### 2013-08-03 Primes Write up.tex
Added the files for the write up -N

\documentclass[12 pt]{article}

\usepackage[parfill]{parskip} 
\begin{document}
\section{The Problem}
In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100. All of these assignments must be graded by someone, and no one can grade their own assignment. Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.

\subsection{Rules}
Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.
\subsection{Assumptions}
These are the assumptions that we have made in creating this model.

1) The objective score is from 0 to 100

2) Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort

3) Everyone, including the professor, has the ability to get the correct objective score

4) Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment

5) Students want good grades

6) People don't like doing work

7) Students are selfish and don't care about their friends

8) Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$

9) Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used

10) Everyone is risk neutral with respect to happiness

11) \emph{Students cannot communicate with each other}

\section{The First Model}
This model is quite unrealistic, but not by such a degree that it is unimaginable. We were, however, able to create a perfect solution if the problem took place in this situation.
\subsection{The Mechanism}
In our model, we have the professor grade one paper, called \emph{X}. The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper. Every student is also given a copy of \emph{X}.

The professor then tells the students that "Out of the two papers you were given, one of them has been graded by me, and the other hasn't. If you fail to give the correct grade for the one I graded, then you will receive a 0." The students then go about their business grading the papers, and individually report the grades they gave out to the professor. Then, just like the professor promised, if the graders graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment. If they graded correctly, the get the maximum of {some minimum value, the assigned grade}.
\subsection{Why it works}
G is the maximum of {some minimum value, the assigned grade}.

The happiness of one student grading one paper is equivalent to $$\frac{H(G)+H(0)}{2}-1$$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.

If they grade both papers, their happiness will be equal to $$H(G)-2$$Because they spent two units of energy, and are guaranteed to get G.

If they grade neither then the happiness will be $$H(0)$$ Because they automatically get a 0, but spend no energy.

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
\subsection{The result}
The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, we get a value of 2.
The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.
\section{The Next Step}
We now have a model that works very well in an unrealistic scenario, so we decided that this solution was fine, and moved on to a new model. The goal for this models was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.

The major change we made in this model was one to assumption number 11. We changed it to:

\emph{All students are able to communicate with each other}

This provides a very different scenario than our original model, because now students will be able to figure out which papers are calibrated. However, we still wanted to try and generalize our previous solution and apply it to the new model, so we came up with the following scheme.
\subsection{The New Mechanism}
Our first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
We arrange the class in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them. The proffesor also grades every \emph{kth} paper starting from some random point in the circle. If a student misgrades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from our previous mechanism.
\subsection{Why it Works and Problems}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students.

1) They can grade 0 papers, giving them a happiness of $H(0) = 0$

2) They can grade all the papers they are assigned, giving them a happiness of $H(g) - k$

3) They can grade i papers giving them a happiness of $(k-i)\div k \cdot H(G)-i$. This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.

The major problem with this method is the amount of work. The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students. For this reason we tried to come up with a different mechanism.
\section{A better mechanism}
In our new mechanism, we went with a completely different strategy, that we wanted to work better than our previous one. It works like this:

For each assignment, a new assignment is created to evaluate the performance of the graders. Every student receives 2 papers from different people, so that each paper overlaps with one other person, and every paper is distributed twice. The student then chooses how many points to subtract, and writes a justification for each one of these points. Graders are then given a contribution score from 1 to -1. From each of the 2 assignments they grade, they get their points deducted/total points deducted-0.5. Then, if the original writers of the papers can appeal their grade if they are unhappy with it. The professor will grade the paper, and if any of the graders were wrong, they get a 0. To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(your assigned grade). (Then your grade is converted from Happiness to an actual score). 
\subsection{Why it works}
The grader's have two choices, they can either grade the papers, or not grade them.

If the grader does not grade the paper, what score should he give it?

If they take off any points, the points will surely be refuted by the professor during the regrade.
So if they take off any points, they will get a 0 on the grading assignment.
If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.
$$$$
If the grader does grade the paper, what score should he give it?

If he gives it a lower score, they throw away free points, and if they give it a lower score there is a risk of them getting a 0 because the scores could be refuted. So, giving it the correct score is the best because it guarantees at least a 50.

So assuming that your partner gives the paper a 100, which is the best thing they could do if they don't grade, then
	If you don’t grade the paper, you don’t use any effort. So your happiness will H(your grade on the original assignment). Contribution score = 0
	If you do grade, you use 1 unit of effort by default. But, your happiness will be H(your grade on the original assignment) + 3. Contribution score = 1

If your partner gives the paper its true grade:
	If you don’t grade the assignment, you will give it a 100 and so your contribution score is -1. So your happiness is H(your original grade) - 4.
	If you do grade the assignment, you and your partner gave the same grades, so get a contribution score of 0. This means that your happiness is H(your original grade).

Therefore, it is in everyone's best interest to honestly grade the paper. 
\subsection{The Result}
Assuming that everyone acts in the dominant strategy behavior, the maximum work for teacher is 0, the maximum work done for students is 2. 
Because everyone honestly grades the papers, the maximum deviation is 0.
So, the objective function is 2, which is even better than our first mechanism.
\section{The Next Step}
\subsection{What is wrong?}
Although the result that we produced for our previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative. This means that we need to find a different solution to the same problem which encourages a kind of positive competition, instead of the negatives formed by trying to find the most mistakes
\subsection{The next mechanism}
For the next mechanism, we kept all of our assumptions the same, and simply tried to find a way to better the feeling of negative competition. To do this, we start by having each paper get graded by two people. Then, the original writer of this paper chooses which of the two grades he/she would like to have, and looks over the justifications for losing any points on both papers. If they see that any of these justifications are incorrect, they flag the paper and send it to the professor. Following this, the paper they chose to have is sent to a third party, who grades the paper, and checks if their grade is close to the one that was given to the paper. If it isn't, the paper is sent to the professor. After everything that needs to be flagged has been, the professor grades all the flagged papers, and rewards people who were correct with a 2 point bonus. If no papers from any group were flagged, every grader in that group gets two points. Final grades are whatever the person chose if there was no flagging, or whatever the professor gave them if there was.
\subsection{Does it work?}
To find out how efficient this mechanism is, we need to analyze two things:
1) Is everyone an honest flagger?
$$$$
2) Do the graders grade honestly
\subsubsection{Flagging}
There are two cases for this:

1) They guess a random score and try to flag everything

-In this case, the chance of gaining points is so low that its disregardable

2) They take the time to flag correctly

-In this case they could get 2 points back, so it is the most beneficial
\subsubsection{Grading}
Once again, there are two cases here: People grading, and people not grading

If people don't bother grading anything, what score should they give the paper?

-100 because anything lower than the actual score will be flagged by the writer, and because of useless justifications, they will lose points. 100 is the only score guaranteed to be greater than or equal to the correct score

Their happiness in this case will be 0, because they use no effort, but also have no chance of gaining points since their paper will definitely get flagged

The happiness of people who honestly grade, on the other hand, will be a +1 gain, because they use 1 unit of effort to grade and they get 2 units back guaranteed. This higher gain means that it is beneficial to grade honestly.

\subsection{The result}
Because everyone is honest, we can now analyze the score of the mechanism:

Maximum work done by one person: 3 (student who flags one paper and grades 2 others)

Maximum deviation: 1 (1 point gain for being a good grader)

Final score: 4

Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve
\end{document}

### 2013-08-03 js/main.js
Login screen looks decent/works

@@ -5,7 +5,7 @@ function MainCtrl($scope) {
 	});
 	io.connect();*/
 	$scope.state = {
-		loggedin:true,
+		loggedin:false,
 		selectedclass : 0,//-1
 		selectedassignment : -1
 	};
@@ -56,6 +56,6 @@ function MainCtrl($scope) {
 		]
 	};
 	$scope.login=function(){
-		this.state.view='main'
+	    this.state.loggedin=true
 	};
 }

### 2013-08-03 js/main.js
Minor modifications

@@ -1,61 +1,46 @@
 function MainCtrl($scope) {
 	/*io.configure(function() {
-		io.set("transports", ["xhr-polling"]);
-		io.set("polling duration", 10);
-	});
-	io.connect();*/
+	 io.set("transports", ["xhr-polling"]);
+	 io.set("polling duration", 10);
+	 });
+	 io.connect();*/
 	$scope.state = {
-		loggedin:false,
-		selectedclass : 0,//-1
+		loggedin : false,
+		selectedclass : 0, //-1
 		selectedassignment : -1
 	};
-	$scope.user={
-		username:"",
-		password:"",
-		data:[
-			{
-				name:"Calculus",
-				assignments:[
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Handout"
-					},
-					{
-						name:"4-3 Homework"
-					}
-				]
-			},
-			{
-				name:"Physics",
-				assignments:[
-					{
-						name:"2-1 Review"
-					},
-					{
-						name:"2-1 Handout"
-					}
-				]
-			}
-		]
+	$scope.user = {
+		username : "",
+		password : "",
+		data : [{
+			name : "Calculus",
+			assignments : [{
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Handout"
+			}, {
+				name : "4-3 Homework"
+			}]
+		}, {
+			name : "Physics",
+			assignments : [{
+				name : "2-1 Review"
+			}, {
+				name : "2-1 Handout"
+			}]
+		}]
 	};
-	$scope.login=function(){
-	    this.state.loggedin=true
+	$scope.login = function() {
+		this.state.loggedin = true
 	};
 }

### 2013-08-04 js/main.js
Added down button and touched up styling

@@ -1,46 +1,50 @@
 function MainCtrl($scope) {
-	/*io.configure(function() {
-	 io.set("transports", ["xhr-polling"]);
-	 io.set("polling duration", 10);
-	 });
-	 io.connect();*/
-	$scope.state = {
-		loggedin : false,
-		selectedclass : 0, //-1
-		selectedassignment : -1
-	};
-	$scope.user = {
-		username : "",
-		password : "",
-		data : [{
-			name : "Calculus",
-			assignments : [{
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Handout"
-			}, {
-				name : "4-3 Homework"
-			}]
-		}, {
-			name : "Physics",
-			assignments : [{
-				name : "2-1 Review"
-			}, {
-				name : "2-1 Handout"
-			}]
-		}]
-	};
-	$scope.login = function() {
-		this.state.loggedin = true
-	};
+  /*io.configure(function() {
+   io.set("transports", ["xhr-polling"]);
+   io.set("polling duration", 10);
+   });
+   io.connect();*/
+  $scope.state = {
+    loggedin : false,
+    selectedclass : 0, //-1
+    selectedassignment : -1,
+    menuvisible : false
+  };
+  $scope.user = {
+    username : "",
+    password : "",
+    data : [{
+      name : "Calculus",
+      assignments : [{
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Handout"
+      }, {
+        name : "4-3 Homework"
+      }]
+    }, {
+      name : "Physics",
+      assignments : [{
+        name : "2-1 Review"
+      }, {
+        name : "2-1 Handout"
+      }]
+    }]
+  };
+  $scope.login = function() {
+    this.state.loggedin = true
+  };
+  $scope.logout = function() {
+    this.state.loggedin = false
+  };
 }

### 2013-08-04 js/main.js
Click-away menu close, reduced lag,  updated css

@@ -47,4 +47,11 @@ function MainCtrl($scope) {
   $scope.logout = function() {
     this.state.loggedin = false
   };
+  $scope.hidemenu = function($event) {
+    console.log($event.target)
+    if (this.state.menuvisible && ($event.target.parentElement && $event.target.parentElement.parentElement && !$event.target.parentElement.parentElement.classList.contains('down'))) {
+      console.log($event.target)
+      this.state.menuvisible = false
+    }
+  };
 }

### 2013-09-01 Primes Write up.tex
Updated gitignore, merged introduction
Now, Latex auxiliary files don't clutter the repo.

@@
-\documentclass[12 pt]{article}
+\documentclass[12pt, Helvetica]{article}   	
+\title{Primes Paper}
+\author{Nick Kaashoek and William Wu}
+\usepackage[margin=1in]{geometry}
+\usepackage{parskip}
+\setlength{\parindent}{15pt}
+\begin{document}
+\maketitle
+\section{Introduction}
+Over the past few years, there has been a tremendous increase in the popularity of MOOCS, also known as massive open online courses, leading to a rise in their importance for educating students around the world as well as a tremendous amount of funding for these courses.
+Both the MOOCS systems coursera and edX; 370,000 in edX and 1.7 million in coursera, these enormous numbers show that MOOCS are extremely important to the education system.
+The amount of money poured into them also reveals this, with 60 million dollars put into edX.
+The huge number of students in these courses also lead to a very high student to professor ratio, 150,000:1 in some courses.
 
-\usepackage[parfill]{parskip} 
-\begin{document}
+The increase in the number of students assigned to a single proffesor in such courses leads to many problems, not the least of which is the inability of a single professor to grade all the assignments they give out, which can sometimes number in the thousands.
+To solve this problem, there are two man solutions in use today; automated grading and peer grading.
+Automated grading relys on having machines grade papers; this is fast, but it may not always be fair to students because machines can only handle a certain number of answers, limiting the types of questions that may be asked.
+Peer grading, however, has no limit on grading, but a system utilizing it could be "hacked" by the students.
+In practice, though, both of these systems are unpolished and rather inefficient.
+
+The problem that we have located is important to solve, because without it the MOOCS cannot provide efficient feedback for their students.
+Without his feedback, students are unable to effectively evaluate what they know and do not know, limiting their learning abilities.
+As such, it is imperitive that an efficient system is created to allow these students to learn and grow efficiently.
+This is our goal.
+
+With the importance of such a problem, there have been many attempts at solving it; however all these attempts lack one thing, which we hope to introduce into our solution.
+In all previous attempts and current designs for grading the papers of students, there is something lacking; a rigourous mathematical proof and analysis of the system.
+With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions.
+Introducing this to the problem will help to create a concrete system of grading that will consistently and universally produce positive results, both in terms of efficiency, and fairness for the students.
+
+To efficiently prove a mathematical system such as we proposed, we need to lay out some tools first, chief among them being mechanism design and game theory.
+Without the correct tools, it is impossible to do the neccesary mathematical analysis on human behavior in these systems, so we turn to game theory.
+Game theory allows us to create a system of rules that have to be followed by everyone in the system.
+By manipulating these rules, we are able to change the behavior of everyone in the system.
+By adding basic assumptions about human nature, we are able to predict what will happen with a specific set of rules, and prove it; this will be how we prove and create our mechanism.
+
+Our end goal with this project is to develop a mathematically provable and efficient mechanism to incentivize selfish people to accurately grade the assignments of others.
+By assuming that all the students in the system care about themselves, we assume that they are selfish.
+With this in mind, the problem becomes an issue of incentivization; how do we make these selfish people care about others?
+As such, our goal is to find the perfect incentive for these people.
+If we are succesful, this will make them grade the papers of others efficienly because they care, and fairly because they are human: this strikes the perfect balance between the two current solutions.
+
+Mathematically provable systems like the one that we are trying to create always lead to good results. For example...
+
+Some people might think that this is a rather simple problem to solve, and could come up with a variety of simple solutions that appear to be correct.
+Incentivizing people often seems simple at first; for example, why not just say "here, take this paper and grade it.
+I'll give you bonus points if you do it." Obviously, this will just return garbage because the students will just take the points and not care about the grading.
+The next step would be to implement some kind of simple checking: "here, you two students, take this paper and grade it.
+If you match, I'll give you bonus points." This case may seem like it works if the students are isolated, but smart students will just give the paper 100, not grade, match and get the points.
+Clearly, simple solutions aren't really that effective
+
+As demonstrated by the above examples, this problem's complexity lies in the complex behavior of selfish human beings; as such, there is no simple way to solve it.
+Because human nature dictates that people will do whatever is in their best interests and will always try to outsmart the system, it quickly becomes apparent that a strict set of rules and assumptions is neccesary to dictate thier behavior.
+The rules, however, can never be to simple, because they need to anticipate every possible way the players (students) will attempt to outsmart them.
+This means that although we will try to create a relatively simple solution, it can never be to straightforward.
+
+The complexity of human nature is what makes the problem interesting; this combined with its relevance makes it an interesting research oppurtunity.
+Although there may not be a simple and beautiful solution to this problem, our use of game theory to predict human nature provides tremendous grounds for interesting research.
+Not only does predicting human nature make this interesting, but the problem's relevance to modern times also means that this is a neccesary problem to solve, giving us good basis to design our solution on.
+
 \section{The Problem}

### 2013-09-02 Primes Write up.tex

@@
 \section{Introduction}
-Over the past few years, there has been a tremendous increase in the popularity of MOOCS, also known as massive open online courses, leading to a rise in their importance for educating students around the world as well as a tremendous amount of funding for these courses.
-Both the MOOCS systems coursera and edX; 370,000 in edX and 1.7 million in coursera, these enormous numbers show that MOOCS are extremely important to the education system.
-The amount of money poured into them also reveals this, with 60 million dollars put into edX.
-The huge number of students in these courses also lead to a very high student to professor ratio, 150,000:1 in some courses.
+Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole.
+Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars\cite{canmoocsreducecc}.
+However, the MOOC's main importance comes from it's scalability.
+Moocs are able to educate massive numbers of students from anywhere in the world\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students\cite{swotanalysisofmoocs}.
+The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.
 
-The increase in the number of students assigned to a single proffesor in such courses leads to many problems, not the least of which is the inability of a single professor to grade all the assignments they give out, which can sometimes number in the thousands.
-To solve this problem, there are two man solutions in use today; automated grading and peer grading.
-Automated grading relys on having machines grade papers; this is fast, but it may not always be fair to students because machines can only handle a certain number of answers, limiting the types of questions that may be asked.
-Peer grading, however, has no limit on grading, but a system utilizing it could be "hacked" by the students.
-In practice, though, both of these systems are unpolished and rather inefficient.
+High student-professor ratios lead to problems for professors.
+Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem.
+Currently, there are two ways to remedy the problem: automated grading and peer grading.
+Automated grading relies on machines to grade assignments.
+However, machines can only check certain types of answers, severly limiting the depth of the questions asked\cite{rightandwrongmoocs}.
+On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students \cite{makingsenseofmoocs}.
+Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.
 
-The problem that we have located is important to solve, because without it the MOOCS cannot provide efficient feedback for their students.
-Without his feedback, students are unable to effectively evaluate what they know and do not know, limiting their learning abilities.
-As such, it is imperitive that an efficient system is created to allow these students to learn and grow efficiently.
+The problem that we have located is important to solve.
+Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge.
+Because this limits their learning abilities, it is imperitive to create an efficient system that enables students to learn efficiently and grow.
 This is our goal.
 
-With the importance of such a problem, there have been many attempts at solving it; however all these attempts lack one thing, which we hope to introduce into our solution.
-In all previous attempts and current designs for grading the papers of students, there is something lacking; a rigourous mathematical proof and analysis of the system.
+There have been many attempts at solving such an important problem.
+However, we hope to introduce what all previous attempts lack: a rigourous mathematical proof and analysis of the system.
 With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions.
@@
 Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve
+
+\begin{thebibliography}
+
+\bibitem{canmoocsreducecc}
+  http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+  Ruth, S. (2012). Can MOOCís and existing e-learning paradigms help reduce college costs? International Journal of Technology in Teaching and Learning, 8(1), 21-32.
+
+\bibitem{makingsenseofmoocs}
+  http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{swotanalysisofmoocs}
+  http://www.editlib.org/p/112020
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{rightandwrongmoocs}
+  http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{test}
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\end{thebibliography}
 \end{document}

### 2013-09-02 Primes Write up.tex
Some edits

--- 2013-08-03 Primes Write up.tex
@@
-\documentclass[12 pt]{article}
+\documentclass[12pt, Helvetica]{article}   	
+\title{Teaching a Class to Grade Itself}
+\author{Nick Kaashoek and William Wu}
+\date{\today}
+\usepackage[margin=1in]{geometry}
+\usepackage{parskip}
+\setlength{\parindent}{15pt}
+\begin{document}
+\maketitle
+\section{Introduction}
+Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole.
+Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars~\cite{canmoocsreducecc}.
+However, the MOOC's main importance comes from it's scalability.
+Moocs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students~\cite{swotanalysisofmoocs}.
+The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.
 
-\usepackage[parfill]{parskip} 
-\begin{document}
+High student-professor ratios lead to problems for professors.
+Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem.
+Currently, there are two ways to remedy the problem: automated grading and peer grading.
+Automated grading relies on machines to grade assignments.
+However, machines can only check certain types of answers, severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}.
+On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students ~\cite{makingsenseofmoocs}.
+Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.
+
+The problem that we have located is important to solve.
+Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge.
+Because this limits their learning abilities, it is imperative to create an efficient system that enables students to learn efficiently and grow.
+This is our goal.
+
+There have been many attempts at solving such an important problem.
+However, we hope to introduce what all previous attempts lack: a rigourous mathematical proof and analysis of the system.
+With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions.
+Introducing this to the problem will help to create a concrete system of grading that will consistently and universally produce positive results, both in terms of efficiency, and fairness for the students.
+
+Without the correct tools, however, it is impossible to do the necessary mathematical analysis on such a system, so we first need to lay out our tools: game theory and mechanism design.
+Game theory allows us to create a unified system of assumptions that simulate a real classroom; this will tell us how the students behave.
+Then, we can use mechanism design to create a set of "rules" that the "players", the students, will have to follow; this is known as the mechanism.
+Using these assumptions and the rules we create, we can predict exactly how students will behave when they play our "game".
+Being able to predict what students will do allow us to prove the efficiency and effectiveness of our mechanism, allowing us to accomplish our goal.
+
+Our end goal with this project is to develop a mathematically provable and efficient mechanism wherein people accurately grade the assignments of others.
+By assuming that all students in the system care about themselves, we assume that they are selfish.
+With this in mind, the problem becomes an issue of finding the right incentive; how do we make these selfish people care about others?
+As such, our goal is to find the perfect incentive for these people.
+If we are successful, this will make them grade the papers of others efficiently because they care, and fairly because they are human: this strikes the perfect balance between the two current solutions.
+
+Some people might think that this is a rather simple problem to solve, and could come up with a variety of simple solutions that appear correct.
+Incentivizing people often seems simple at first; for example, why not just say "here, take this paper and grade it.
+I'll give you bonus points if you do it." Obviously, this will not return anything useful because the students will just take the points and not care about the grading.
+The next step would be to implement some kind of simple checking: "here, you two students, take this paper and grade it.
+If you match, I'll give you bonus points." This case may seem like it works if the students are isolated, but smart students will just give the paper 100, not grade, match and get the points.
+Clearly, simple solutions aren't really that effective.
+
+As demonstrated by the above examples, this problem's complexity lies in the complex behavior of selfish human beings; as such, there is no simple way to solve it.
+Because human nature dictates that people will do whatever is in their best interests and will always try to outsmart the system, it quickly becomes apparent that a strict set of rules and assumptions are necessary to dictate their behavior.
+These rules, however, can never be too simple, because they need to anticipate every possible way the players (students) will attempt to outsmart them.
+This means that although we will try to create a relatively simple solution, it can never be too straightforward.
+
+The complexity of human nature and the relevance that this problem has makes this an interesting research opportunity.
+Because it is so hard to predict human nature, our strategy for creating a solution provides an extremely interesting research opportunity, especially because it is something that no one else has attempted before.
+Also, the relevance of the problem we have located also makes this necessary research; thus making our solution even more interesting because it could actually be used in practice.
+
 \section{The Problem}
@@
 Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve
+
+\begin{thebibliography}
+
+\bibitem{canmoocsreducecc}
+  http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+  Ruth, S. (2012). Can MOOCs and existing e-learning paradigms help reduce college costs? International Journal of Technology in Teaching and Learning, 8(1), 21-32.
+
+\bibitem{makingsenseofmoocs}
+  http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{swotanalysisofmoocs}
+  http://www.editlib.org/p/112020
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{rightandwrongmoocs}
+  http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{test}
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\end{thebibliography}
 \end{document}

### 2013-09-05 Primes Write up.tex
Revised Paper

@@
-\documentclass[12pt, Helvetica]{article}   	
-\title{Teaching a Class to Grade Itself}
+\documentclass[12pt, Arial]{article}   	
+\title{Teaching a Class to Grade Itself using Game Theory}
 \author{Nick Kaashoek and William Wu}
@@
 Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole.
-Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars~\cite{canmoocsreducecc}.
-However, the MOOC's main importance comes from it's scalability.
-Moocs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students~\cite{swotanalysisofmoocs}.
+Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started~\cite{canmoocsreducecc}.
+However, the MOOC's main importance comes from its scalability.
+MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}.
 The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.
@@
 High student-professor ratios lead to problems for professors.
-Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem.
-Currently, there are two ways to remedy the problem: automated grading and peer grading.
+Professors are simply unable to grade hundreds of thousands of submissions.
+Currently, two types of solutions are used to remedy the problem: automated grading and peer grading.
 Automated grading relies on machines to grade assignments.
-However, machines can only check certain types of answers, severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}.
-On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students ~\cite{makingsenseofmoocs}.
-Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.
+However, machines can only check certain types of answers (i.e.
+multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}.
+Even though automated grading for written essays is an active area of research with much recent progress, a usable solution does not yet exist~\cite{automatedsystemssuck}.
+On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}.
+Although both of these systems are interesting concepts, they are limiting or inaccurate in practice~\cite{howaccurateispeergrading}.
 
-The problem that we have located is important to solve.
+The problem of grading large numbers of submissions is important to solve.
 Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge.
-Because this limits their learning abilities, it is imperative to create an efficient system that enables students to learn efficiently and grow.
-This is our goal.
+Because this limits their learning abilities, it is imperative to create an efficient system that enables students to receive feedback to learn efficiently.
 
-There have been many attempts at solving such an important problem.
-However, we hope to introduce what all previous attempts lack: a rigourous mathematical proof and analysis of the system.
-With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions.
-Introducing this to the problem will help to create a concrete system of grading that will consistently and universally produce positive results, both in terms of efficiency, and fairness for the students.
+There have been many attempts at solving such an important problem~\cite{autograding}~\cite{edxsoftware}.
+However, this work introduces what previous attempts lack: a rigorous mathematical analysis of the system using tools from game theory and mechanism design.
+This work sets a concrete set of constraints that a grading system must satisfy to mitigate student incentive to cheat, as well as a concrete benchmark to analyze the efficiency of various systems.
+Together, these create a concrete measure for evaluating peer grading systems in terms of efficiency (how much time the professor and students spend grading) and fairness for the students (how accurate their final scores are).
+Having this measurement model is a large contribution in itself, because it allows comparison between different systems.
+Although a theoretical model cannot predict exactly what will happen in practice, game theory and mechanism design have a history of generally determining mechanisms that work in practice from ones that do not.
+Mechanisms that do not follow game theoretic constraints may work in the short-term, but they will be exploited if possible in the long term~\cite{boycottfinal}.
+%[Note from Matt and Christos: 1) mention that coming up with a model is itself a big contribution, because now we can compare the quality of two different mechanisms.
+2) Mention that certainly theory is not a perfect predictor of what will happen in practice, but that game theory and mechanism design (and all the assumptions used in this work) have a history of ``calling good mechanisms good and bad mechanisms bad''.
+Also, solutions that do not satisfy game theoretic constraints may work for a while, but in the long run if a system can be exploited, eventually it will be.
+See here for an interesting example of this: http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get]
 
-Without the correct tools, however, it is impossible to do the necessary mathematical analysis on such a system, so we first need to lay out our tools: game theory and mechanism design.
-Game theory allows us to create a unified system of assumptions that simulate a real classroom; this will tell us how the students behave.
-Then, we can use mechanism design to create a set of "rules" that the "players", the students, will have to follow; this is known as the mechanism.
-Using these assumptions and the rules we create, we can predict exactly how students will behave when they play our "game".
-Being able to predict what students will do allow us to prove the efficiency and effectiveness of our mechanism, allowing us to accomplish our goal.
+Game theory allows the creation of a unified system of assumptions that simulate student behavior in a class.
+The grading system can be viewed as a ``game'' where the set of ``rules'' are known to everyone and the ``players'' --- the students --- ``play'' the game in order to get the best possible result.
+Using the assumptions and rules, game theory can predict how students will behave when they ``play''.
+This way, mechanism efficiency and effectiveness cam be proved, allowing the evaluation of different sets of rules.
 
-Our end goal with this project is to develop a mathematically provable and efficient mechanism wherein people accurately grade the assignments of others.
-By assuming that all students in the system care about themselves, we assume that they are selfish.
-With this in mind, the problem becomes an issue of finding the right incentive; how do we make these selfish people care about others?
-As such, our goal is to find the perfect incentive for these people.
-If we are successful, this will make them grade the papers of others efficiently because they care, and fairly because they are human: this strikes the perfect balance between the two current solutions.
+In addition to modeling grading systems, this project develops a mechanism in which students accurately grade the assignments of other students.
+Students are assumed to be self-interested; they care about their own grades, not the grades of their peers.
+With this, the problem becomes how to find the perfect incentive for students to spend time to grade assignments of others.
+Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
+However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e.
+they will just give every assignment a 100).
+The next step would be to implement simple checking: e.g.
+have each paper be graded by two students who both receive bonus points if their grades match.
+This case may work if the students are isolated, but clever students will still just give all papers 100.
+This way, their papers will match those of other clever students, giving them points without grading.
+These examples show that properly incentivizing graders can be a difficult task.
 
-Some people might think that this is a rather simple problem to solve, and could come up with a variety of simple solutions that appear correct.
-Incentivizing people often seems simple at first; for example, why not just say "here, take this paper and grade it.
-I'll give you bonus points if you do it." Obviously, this will not return anything useful because the students will just take the points and not care about the grading.
-The next step would be to implement some kind of simple checking: "here, you two students, take this paper and grade it.
-If you match, I'll give you bonus points." This case may seem like it works if the students are isolated, but smart students will just give the paper 100, not grade, match and get the points.
-Clearly, simple solutions aren't really that effective.
+As demonstrated by the above examples, the complexity of the problem lies in the complex behavior of selfish human beings.
+Because human nature dictates that people will do whatever is in their best interest and may try to outsmart the system, coming up with a strict set of rules to encourage the desired behavior can be quite challenging.
+A mechanism should be made as simple as possible, but the above examples show that a small amount of simplicity must be sacrificed to obtain a system that can't be manipulated.
 
-As demonstrated by the above examples, this problem's complexity lies in the complex behavior of selfish human beings; as such, there is no simple way to solve it.
-Because human nature dictates that people will do whatever is in their best interests and will always try to outsmart the system, it quickly becomes apparent that a strict set of rules and assumptions are necessary to dictate their behavior.
-These rules, however, can never be too simple, because they need to anticipate every possible way the players (students) will attempt to outsmart them.
-This means that although we will try to create a relatively simple solution, it can never be too straightforward.
-
-The complexity of human nature and the relevance that this problem has makes this an interesting research opportunity.
-Because it is so hard to predict human nature, our strategy for creating a solution provides an extremely interesting research opportunity, especially because it is something that no one else has attempted before.
-Also, the relevance of the problem we have located also makes this necessary research; thus making our solution even more interesting because it could actually be used in practice.
+This research opportunity is made interesting by the complexity of human nature as well as its necessity for practical use.
+This paper will cover the thought process of models leading up to the final model of grading, as well as explain the final model and its implications.
+All models and related calculations will be presented.
+Section 2 describes the mathematical definition of the problem as well as its rules and assumptions.
+Section 3
 
@@
 Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.
+
+[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload?
+Why do you care about accurate grades?
+If you just care about workload, give everyone 100.
+If you just care about grades, have the professor grade everything.
+Need to consider both to properly model the problem.]
 
@@
 
-\section{The First Model}
+\section{The Calibration Model}
+
 This model is quite unrealistic, but not by such a degree that it is unimaginable. We were, however, able to create a perfect solution if the problem took place in this situation.
-\subsection{The Mechanism}
+
+\subsection{Mechanism}
 In our model, we have the professor grade one paper, called \emph{X}.
@@
 
-The professor then tells the students that "Out of the two papers you were given, one of them has been graded by me, and the other hasn't.
-If you fail to give the correct grade for the one I graded, then you will receive a 0." The students then go about their business grading the papers, and individually report the grades they gave out to the professor.
-Then, just like the professor promised, if the graders graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment.
-If they graded correctly, the get the maximum of {some minimum value, the assigned grade}.
-\subsection{Why it works}
-G is the maximum of {some minimum value, the assigned grade}.
+The professor then tells the students that ``Out of the two papers you were given, one of them has been graded by me, and the other hasn't.
+If you fail to give the correct grade for the one I graded, then you will receive a 0.'' The students then go about their business grading the papers, and individually report the grades they gave out to the professor.
+Then, just like the professor promised, if the students graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment.
+If they graded correctly, their assigned grade is guaranteed to be at least some minimum value.
+
+\subsection{Why it Works}
+G is the maximum of \{ some minimum value, the assigned grade \}.
 
@@
 So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
-\subsection{The result}
+\subsection{Results}
 The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
@@
 The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.
-\section{The Next Step}
+
+\subsection{Problems}
+The goal for this model was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
 We now have a model that works very well in an unrealistic scenario, so we decided that this solution was fine, and moved on to a new model.
-The goal for this models was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
 
-The major change we made in this model was one to assumption number 11. We changed it to:
-
+\section{Improved Verification Model}
+The major change made in this model was one to assumption number 11. Now assumption 11 reads as follows:
 \emph{All students are able to communicate with each other}
@@
 However, we still wanted to try and generalize our previous solution and apply it to the new model, so we came up with the following scheme.
-\subsection{The New Mechanism}
+
+\subsection{Mechanism}
 Our first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
-We arrange the class in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them.
-The proffesor also grades every \emph{kth} paper starting from some random point in the circle.
-If a student misgrades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from our previous mechanism.
-\subsection{Why it Works and Problems}
+The class is arranged in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them.
+The professor also grades every \emph{kth} paper starting from some random point in the circle.
+If a student mis-grades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from our previous mechanism.
+
+\subsection{Why it Works}
 In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other.
@@
 
+\subsection{Results}
+Even though the students can communicate with one another, they will have no way to determine which paper is calibrated, and are thus best off grading all the papers.
+
+\subsection{Problems}
 The major problem with this method is the amount of work.
@@
 For this reason we tried to come up with a different mechanism.
-\section{A better mechanism}
-In our new mechanism, we went with a completely different strategy, that we wanted to work better than our previous one. It works like this:
 
+\section{The Deduction Model}
+In our new mechanism, we went with a completely different strategy, that we wanted to work better than our previous one.
+
+\subsection{Mechanism}
 For each assignment, a new assignment is created to evaluate the performance of the graders.
@@
 Graders are then given a contribution score from 1 to -1.
-From each of the 2 assignments they grade, they get their points deducted/total points deducted-0.5.
+From each of the 2 assignments they grade, they get their points deducted / total points deducted-0.5.
 Then, if the original writers of the papers can appeal their grade if they are unhappy with it.
@@
 (Then your grade is converted from Happiness to an actual score).
-\subsection{Why it works}
+
+\subsection{Why it Works}
 The grader's have two choices, they can either grade the papers, or not grade them.
@@
 So assuming that your partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If you don’t grade the paper, you don’t use any effort. So your happiness will H(your grade on the original assignment). Contribution score = 0
+	If you don't grade the paper, you don't use any effort. So your happiness will H(your grade on the original assignment). Contribution score = 0
 	If you do grade, you use 1 unit of effort by default. But, your happiness will be H(your grade on the original assignment) + 3. Contribution score = 1
@@
 If your partner gives the paper its true grade:
-	If you don’t grade the assignment, you will give it a 100 and so your contribution score is -1. So your happiness is H(your original grade) - 4.
+	If you don't grade the assignment, you will give it a 100 and so your contribution score is -1. So your happiness is H(your original grade) - 4.
 	If you do grade the assignment, you and your partner gave the same grades, so get a contribution score of 0. This means that your happiness is H(your original grade).
@@
 Therefore, it is in everyone's best interest to honestly grade the paper.
-\subsection{The Result}
+
+\subsection{Results}
 Assuming that everyone acts in the dominant strategy behavior, the maximum work for teacher is 0, the maximum work done for students is 2. 
@@
 So, the objective function is 2, which is even better than our first mechanism.
-\section{The Next Step}
-\subsection{What is wrong?}
+
+\subsection{Problems}
 Although the result that we produced for our previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
 This means that we need to find a different solution to the same problem which encourages a kind of positive competition, instead of the negatives formed by trying to find the most mistakes
-\subsection{The next mechanism}
+
+\section{The Flag Model}
 For the next mechanism, we kept all of our assumptions the same, and simply tried to find a way to better the feeling of negative competition.
-To do this, we start by having each paper get graded by two people.
-Then, the original writer of this paper chooses which of the two grades he/she would like to have, and looks over the justifications for losing any points on both papers.
+\subsection{Mechanism}
+Start by having each paper get graded by two people.
+Then, the original writer of this paper chooses which of the two grades he / she would like to have, and looks over the justifications for losing any points on both papers.
 If they see that any of these justifications are incorrect, they flag the paper and send it to the professor.
@@
 Final grades are whatever the person chose if there was no flagging, or whatever the professor gave them if there was.
-\subsection{Does it work?}
+\subsection{Why it Works}
 To find out how efficient this mechanism is, we need to analyze two things:
@@
 
--In this case, the chance of gaining points is so low that its disregardable
+-In this case, the chance of gaining points is so low that it is negligible
 
@@
 
-\subsection{The result}
+\subsection{Results}
 Because everyone is honest, we can now analyze the score of the mechanism:
@@
 
-Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve
+Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negative.
 
-\begin{thebibliography}
+\begin{thebibliography}{9}
 
 \bibitem{canmoocsreducecc}
-  http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-  Ruth, S. (2012). Can MOOCs and existing e-learning paradigms help reduce college costs? International Journal of Technology in Teaching and Learning, 8(1), 21-32.
+  % http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
+  Ruth, S. (2012). \emph{Can MOOCs and existing e-learning paradigms help reduce college costs}? International Journal of Technology in Teaching and Learning, 8(1), 21-32.
 
 \bibitem{makingsenseofmoocs}
-  http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
+  % http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
   Author,
@@
 \bibitem{swotanalysisofmoocs}
-  http://www.editlib.org/p/112020
+  % http://www.editlib.org/p/112020
   Author,
@@
 \bibitem{rightandwrongmoocs}
-  http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
+  % http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
   Author,
@@
 
-\bibitem{test}
+\bibitem{boycottfinal}
+  % http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{autograding}
+  % http://www.ecu.edu/cs-acad/fsonline/customcf/committee/tg/2013proposals/08.pdf
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{edxsoftware}
+  % http://www.bostonmagazine.com/news/blog/2013/04/04/edx-now-has-robots-to-grade-your-essays/
+  Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{automatedsystemssuck}
+  Herrington, A., \& Moran, C.
+(2012).
+\emph{Writing to a machine is not writing at all}.
+In N.
+Elliot \& L.
+Perelman (Eds.), Writing assessment in the 21st century: Essays in honor of Edward M.
+White (pp.
+219-232).
+New York, NY: Hampton Press.
+
+\bibitem{howaccurateispeergrading}
+  % http://educationgroup.mit.edu/HHMIEducationGroup/wp-content/uploads/2011/05/Freeman-et-al-2010.pdf
   Author,

### 2013-09-08 Primes Write up.tex
Removed our

@@
 \subsection{Mechanism}
-In our model, we have the professor grade one paper, called \emph{X}.
+In the model, we have the professor grade one paper, called \emph{X}.
 The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper.
@@
 
-This provides a very different scenario than our original model, because now students will be able to figure out which papers are calibrated.
-However, we still wanted to try and generalize our previous solution and apply it to the new model, so we came up with the following scheme.
+This provides a very different scenario than the original model, because now students will be able to figure out which papers are calibrated.
+However, we still wanted to try and generalize the previous solution and apply it to the new model, so we came up with the following scheme.
 
 \subsection{Mechanism}
-Our first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
+The first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
 The class is arranged in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them.
 The professor also grades every \emph{kth} paper starting from some random point in the circle.
-If a student mis-grades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from our previous mechanism.
+If a student mis-grades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from the previous mechanism.
 
@@
 \section{The Deduction Model}
-In our new mechanism, we went with a completely different strategy, that we wanted to work better than our previous one.
+In the new mechanism, we went with a completely different strategy, that we wanted to work better than the previous one.
 
@@
 The professor will grade the paper, and if any of the graders were wrong, they get a 0.
-To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(your assigned grade).
-(Then your grade is converted from Happiness to an actual score).
+To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(the student's assigned grade).
+(Then the student's grade is converted from Happiness to an actual score).
 
@@
 
-So assuming that your partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If you don't grade the paper, you don't use any effort. So your happiness will H(your grade on the original assignment). Contribution score = 0
-	If you do grade, you use 1 unit of effort by default. But, your happiness will be H(your grade on the original assignment) + 3. Contribution score = 1
+So assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
+	If you don't grade the paper, you don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
+	If you do grade, you use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
 
-If your partner gives the paper its true grade:
-	If you don't grade the assignment, you will give it a 100 and so your contribution score is -1. So your happiness is H(your original grade) - 4.
-	If you do grade the assignment, you and your partner gave the same grades, so get a contribution score of 0. This means that your happiness is H(your original grade).
+If the grader's partner gives the paper its true grade:
+	If the grader doesn't grade the assignment, you will give it a 100 and so the grader's contribution score is -1. So their happiness is H(your original grade) - 4.
+	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
 
@@
 Because everyone honestly grades the papers, the maximum deviation is 0.
-So, the objective function is 2, which is even better than our first mechanism.
+So, the objective function is 2, which is even better than the first mechanism.
 
 \subsection{Problems}
-Although the result that we produced for our previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
+Although the result that we produced for the previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
 This means that we need to find a different solution to the same problem which encourages a kind of positive competition, instead of the negatives formed by trying to find the most mistakes
@@
 \section{The Flag Model}
-For the next mechanism, we kept all of our assumptions the same, and simply tried to find a way to better the feeling of negative competition.
+For the next mechanism, we kept all of the assumptions the same, and simply tried to find a way to better the feeling of negative competition.
 \subsection{Mechanism}
@@
 
-Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negative.
+Although this is not as good as the previous mechanism, it is still an improvement because there is now positive competition instead of negative.
 

### 2013-09-08 Primes Write up.tex
Got rid of you/your

@@
 So assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If you don't grade the paper, you don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
-	If you do grade, you use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
+	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
+	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
 
 If the grader's partner gives the paper its true grade:
-	If the grader doesn't grade the assignment, you will give it a 100 and so the grader's contribution score is -1. So their happiness is H(your original grade) - 4.
+	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
 	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).

### 2013-09-08 Primes Write up.tex
Got rid of we

@@
 \subsection{Assumptions}
-These are the assumptions that we have made in creating this model.
+These are the assumptions that were made in creating this model.
 
@@
 
-This model is quite unrealistic, but not by such a degree that it is unimaginable. We were, however, able to create a perfect solution if the problem took place in this situation.
+This model is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.
 
 \subsection{Mechanism}
-In the model, we have the professor grade one paper, called \emph{X}.
+In the model, the professor grades one paper, called \emph{X}.
 The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper.
@@
 Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
-This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, we get a value of 2.
+This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
 The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.
@@
 The goal for this model was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
-We now have a model that works very well in an unrealistic scenario, so we decided that this solution was fine, and moved on to a new model.
+There is now a model that works very well in an unrealistic scenario, so we moved on to a new model.
 
@@
 This provides a very different scenario than the original model, because now students will be able to figure out which papers are calibrated.
-However, we still wanted to try and generalize the previous solution and apply it to the new model, so we came up with the following scheme.
+However, it would be better to try and generalize the previous solution and apply it to the new model, which leads to the following scheme.
 
@@
 The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students.
-For this reason we tried to come up with a different mechanism.
+For this reason a different mechanism was necessary.
 
 \section{The Deduction Model}
-In the new mechanism, we went with a completely different strategy, that we wanted to work better than the previous one.
+In the new mechanism, a different strategy was created; one that would ideally work better than the previous ones.
 
@@
 \subsection{Problems}
-Although the result that we produced for the previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
-This means that we need to find a different solution to the same problem which encourages a kind of positive competition, instead of the negatives formed by trying to find the most mistakes
+Although the result that was produced for the previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
+This means that finding a different solution to the same problem was necessary, in which students are placed in positive competition, instead of the negative one formed by trying to find the most mistakes
 
 \section{The Flag Model}
-For the next mechanism, we kept all of the assumptions the same, and simply tried to find a way to better the feeling of negative competition.
+For the next mechanism, all of the assumptions were kept the same, and simply tried to find a way to better the feeling of negative competition.
 \subsection{Mechanism}
@@
 \subsection{Why it Works}
-To find out how efficient this mechanism is, we need to analyze two things:
+To find out how efficient this mechanism is, two things needed to be analyzed:
 1) Is everyone an honest flagger?

### 2013-09-08 Primes Write up.tex
Changes to methods and materials

@@
 Section 3
+\section{Materials and Methods}
+To create the models that are used to predict the behavior of the students, a set process was used each time.
+To begin with, a set of assumptions is created.
+These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades.
+This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model.
+The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side.
+To begin with, a simple set of assumptions was created:
+\begin{enumerate}
+  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
+  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+  \item Everyone is risk neutral with respect to happiness
+  \item Students want good grades
+\end{enumerate}
 
+These assumptions, in layman's terms, state that student's are happiest when they do no work, want to be happy, want good grades, and have a function that expresses there happiness.
+Also, they state that students will not avoid nor specifically try and take risks to get happier.
+
+The next step is to create a system that will allow multiple different models to be compared and evaluated side by side; in other words, a benchmark needs to be created.
+To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
+Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done.
+As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism.
+
+Being able to evaluate two mechanisms side by side is key to the success of the problem, because it allows us to definitively determine whether one mechanism is better than the other.
+In the benchmark, the two important factors are both necessary to consider, as  without one or the other, it would become impossible to create an efficient mechanism.
+Without caring about the workload, a model could be considered efficient if it simply asked the professor to grade every paper, because the grades would be very accurate, but a mechanism like this is clearly inefficient.
+Also, without caring about accuracy, not grading the papers becomes an efficient design.
+
+Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ''rules'' of the game.
+To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes.
+This turned the list of assumptions from the simple:
+\begin{enumerate}
+  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
+  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+  \item Everyone is risk neutral with respect to happiness
+  \item Students want good grades
+\end{enumerate}
+into:
+\begin{enumerate}
+\item The objective score of an assignment is from 0 to 100
+\item The objective score assigned by the professor is the correct objective score
+\item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort
+\item Not everyone has the ability to get the correct objective score
+\item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
+\item Students want good grades
+\item People don't like doing work
+\item Students are selfish and don't care about their friends
+\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+\item Everyone is risk neutral with respect to happiness
+\item All students can communicate with all other students
+\end{enumerate}
+These assumptions provide the necessary environment to begin creating a mechanism, as they state everything that is necessary to understand how students behave.
+Simply put, every assignment has a grade from 1-100, and whatever the professor says goes.
+Every student has a different capacity for grading, and as such not everyone will be able to correctly grade very assignment, but they can only choose to either grade or not grade.
+All students are capable of communicating with each other, and will do so, and the rest is from the simple set of assumptions.
+
+Because it would be illogical to start creating a mechanism to encompass all of these assumptions, every mechanism grows in complexity, with the first one being the most simple.
+Throughout the design process, the assumptions were changed to allow for simplicity, which allows for the creation of simpler models.
+The complex set of assumptions were always kept in mind, however.
+
+The next step in creating a mechanism
 \section{The Problem}

### 2013-09-08 Primes Write up.tex
Merged Nick's changes into mine

@@
 
-In addition to modeling grading systems, this project develops a mechanism in which students accurately grade the assignments of other students.
-Students are assumed to be self-interested; they care about their own grades, not the grades of their peers.
-With this, the problem becomes how to find the perfect incentive for students to spend time to grade assignments of others.
+The difficulty of the problem lies in finding an incentive for students to spend time to grade assignments of others who they don't care about.
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
@@
 These examples show that properly incentivizing graders can be a difficult task.
+The main purpose of this work is to devise mechanisms which avoid these problems, allowing for work to be distributed efficiently.
 
-As demonstrated by the above examples, the complexity of the problem lies in the complex behavior of selfish human beings.
+As demonstrated by the above examples, the difficulty of the problem lies in the complex behavior of selfish human beings.
 Because human nature dictates that people will do whatever is in their best interest and may try to outsmart the system, coming up with a strict set of rules to encourage the desired behavior can be quite challenging.
@@
 This research opportunity is made interesting by the complexity of human nature as well as its necessity for practical use.
-This paper will cover the thought process of models leading up to the final model of grading, as well as explain the final model and its implications.
-All models and related calculations will be presented.
+This paper will cover the thought process of mechanisms leading up to the final mechanism of grading, as well as explain the final mechanism and its implications.
+All mechanisms and related calculations will be presented.
 Section 2 describes the mathematical definition of the problem as well as its rules and assumptions.
-Section 3
+
 \section{Materials and Methods}
-To create the models that are used to predict the behavior of the students, a set process was used each time.
+The goal of this research is to find a peer grading system that is as accurate and as efficient as possible. First, the problem must be defined in mathematical terms.
+
 To begin with, a set of assumptions is created.
 These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades.
-This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model.
-The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side.
+This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a mechanism.
+The same set of assumptions can be used for multiple mechanisms, which will allow us to evaluate different mechanisms side by side.
 To begin with, a simple set of assumptions was created:
@@
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$, $W$ is number of work units used
   \item Everyone is risk neutral with respect to happiness
@@
 
-The next step is to create a system that will allow multiple different models to be compared and evaluated side by side; in other words, a benchmark needs to be created.
-To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
+\subsection{Benchmark}
+Once the assumptions are complete, a benchmark can be selected based on the goals of the system.
+A benchmark will allow for a quantitative way to compare mechanisms.
+To define such a benchmark, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
 Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done.
 As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism.
+Mathematically, the goal is to minimize the maximum amount of work done by a single person, as well as minimize maximum deviation between any student's given grade and the grade their assignment deserves.
 
-Being able to evaluate two mechanisms side by side is key to the success of the problem, because it allows us to definitively determine whether one mechanism is better than the other.
-In the benchmark, the two important factors are both necessary to consider, as  without one or the other, it would become impossible to create an efficient mechanism.
-Without caring about the workload, a model could be considered efficient if it simply asked the professor to grade every paper, because the grades would be very accurate, but a mechanism like this is clearly inefficient.
-Also, without caring about accuracy, not grading the papers becomes an efficient design.
+Caring about the workload is just as important as caring about accurate grades.
+If the system was purely based on minimizing only the work done by a single person, everyone could just get 100.
+Likewise, if the system was purely based on maximizing grade accuracy, the professor could grade everything.
+In order to properly model the problem to achieve a solution that is reasonable, both aspects of the problem need to be considered.
 
-Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ''rules'' of the game.
+\subsection{Rules}
+After a simple set of assumptions and a benchmark are created, the assumptions need to be further developed into a true model that will become the ``rules'' of the game.
 To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes.
-This turned the list of assumptions from the simple:
+This added complexity to the previously simple assumptions:
 \begin{enumerate}
@@
 \end{enumerate}
+
+Put simply, in a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 0 to 100.
+All of these assignments must be graded by someone, and no one can grade their own assignment.
+Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.
+
 These assumptions provide the necessary environment to begin creating a mechanism, as they state everything that is necessary to understand how students behave.
@@
 Need to consider both to properly model the problem.]
+Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested.
+This is where mechanism design and game theory comes into play.
+Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose.
+Then, game theory is used to mathematically predict student behavior to benchmark such a system.
+Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months.
+The end result is fairly complete, although there are still questions to be answered in future work.
 
-\subsection{Rules}
-Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.
-\subsection{Assumptions}
-These are the assumptions that were made in creating this model.
+\section{The Calibration Mechanism}
 
-1) The objective score is from 0 to 100
-
-2) Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort
-
-3) Everyone, including the professor, has the ability to get the correct objective score
-
-4) Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
-
-5) Students want good grades
-
-6) People don't like doing work
-
-7) Students are selfish and don't care about their friends
-
-8) Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-
-9) Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-
-10) Everyone is risk neutral with respect to happiness
-
-11) \emph{Students cannot communicate with each other}
-
-\section{The Calibration Model}
-
-This model is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.
+This mechanism is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.
 
 \subsection{Mechanism}
-In the model, the professor grades one paper, called \emph{X}.
+In the mechanism, the professor grades one paper, called \emph{X}.
 The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper.
@@
 \subsection{Problems}
-The goal for this model was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
-There is now a model that works very well in an unrealistic scenario, so we moved on to a new model.
+The goal for this mechanism was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
+There is now a mechanism that works very well in an unrealistic scenario, so we moved on to a new mechanism.
 
-\section{Improved Verification Model}
-The major change made in this model was one to assumption number 11. Now assumption 11 reads as follows:
+\section{Improved Verification Mechanism}
+The major change made in this mechanism was one to assumption number 11. Now assumption 11 reads as follows:
 \emph{All students are able to communicate with each other}
 
-This provides a very different scenario than the original model, because now students will be able to figure out which papers are calibrated.
-However, it would be better to try and generalize the previous solution and apply it to the new model, which leads to the following scheme.
+This provides a very different scenario than the original mechanism, because now students will be able to figure out which papers are calibrated.
+However, it would be better to try and generalize the previous solution and apply it to the new mechanism, which leads to the following scheme.
 
 \subsection{Mechanism}
-The first attempt to apply a solution to this model was a near carbon copy of the previous scheme.
+The first attempt to apply a solution to this mechanism was a near carbon copy of the previous scheme.
 The class is arranged in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them.
@@
 
-\section{The Deduction Model}
+\section{The Deduction Mechanism}
 In the new mechanism, a different strategy was created; one that would ideally work better than the previous ones.
@@
 \subsection{Problems}
-Although the result that was produced for the previous model is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
+Although the result that was produced for the previous mechanism is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
 This means that finding a different solution to the same problem was necessary, in which students are placed in positive competition, instead of the negative one formed by trying to find the most mistakes
 
-\section{The Flag Model}
+\section{The Flag Mechanism}
 For the next mechanism, all of the assumptions were kept the same, and simply tried to find a way to better the feeling of negative competition.

### 2013-09-08 Primes Write up.tex
Christos' changes

--- 2013-09-08 Primes Write up.tex
@@
 To begin with, a simple set of assumptions was created:
+%Note: Specify that the model refers to a single grading round: There are $n$ students and 1 professor.
+Every student comes to us with an ungraded paper (input) define the objective score o_i, we then give those papers grades(output) After a mechanism runs each student receives a grade $g_i$ and after performing $w_i$ units of work.
+Define the professor as index 0.%
 \begin{enumerate}
-  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-  \item Everyone is risk neutral with respect to happiness
-  \item Students want good grades
+  \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
+  \item Students want to maximize their final happiness, expressed as $H(g)-W$
+  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
+  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
 \end{enumerate}
+%add simple list%
 
-These assumptions, in layman's terms, state that student's are happiest when they do no work, want to be happy, want good grades, and have a function that expresses there happiness.
-Also, they state that students will not avoid nor specifically try and take risks to get happier.
+%Explanation of the choice of assumption
+% - We need to talk about happiness because it provides a numerical way to compare different outcomes
+% - Why don't we care about our friends
 
+%First objective%
+No student can deviate from the truthful strategy to improve his happiness.
+In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.
+
+%Efficiency objective%
 The next step is to create a system that will allow multiple different models to be compared and evaluated side by side; in other words, a benchmark needs to be created.
@@
 As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism.
+In mathematical terms we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
 
@@
 
+% We now have a well defined problem that we need to solve. Of course the set of assumptions might not be very realistic as we will so we
+
 Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ''rules'' of the game.
 To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes.
-This turned the list of assumptions from the simple:
+This turned the list of assumptions from the
+simple into:
+%Repeat above corrections%
 \begin{enumerate}
-  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
-  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-  \item Everyone is risk neutral with respect to happiness
-  \item Students want good grades
-\end{enumerate}
-into:
-\begin{enumerate}
-\item The objective score of an assignment is from 0 to 100
-\item The objective score assigned by the professor is the correct objective score
+\item The objective score of an assignment is from 0 to 100%setting%
+\item The objective score assigned by the professor is the correct objective score%setting%
 \item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort
+
 \item Not everyone has the ability to get the correct objective score
+
 \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
@@
 \item Everyone is risk neutral with respect to happiness
+
 \item All students can communicate with all other students
+
 \end{enumerate}

### 2013-09-08 Primes Write up.tex
Resolved merge conflicts

--- 2013-09-08 Primes Write up.tex
@@
 \section{Materials and Methods}
-The goal of this research is to find a peer grading system that is as accurate and as efficient as possible. First, the problem must be defined in mathematical terms.
-
+To create the models that are used to predict the behavior of the students, a set process was used each time.
 To begin with, a set of assumptions is created.
 These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades.
-This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a mechanism.
-The same set of assumptions can be used for multiple mechanisms, which will allow us to evaluate different mechanisms side by side.
+This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model.
+The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side.
 To begin with, a simple set of assumptions was created:
+%Note: Specify that the model refers to a single grading round: There are $n$ students and 1 professor.
+Every student comes to us with an ungraded paper (input) define the objective score o_i, we then give those papers grades(output) After a mechanism runs each student receives a grade $g_i$ and after performing $w_i$ units of work.
+Define the professor as index 0.%
 \begin{enumerate}
-  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$, $W$ is number of work units used
-  \item Everyone is risk neutral with respect to happiness
-  \item Students want good grades
+  \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
+  \item Students want to maximize their final happiness, expressed as $H(g)-W$
+  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
+  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
 \end{enumerate}
+%add simple list%
 
-These assumptions, in layman's terms, state that student's are happiest when they do no work, want to be happy, want good grades, and have a function that expresses there happiness.
-Also, they state that students will not avoid nor specifically try and take risks to get happier.
+%Explanation of the choice of assumption
+% - We need to talk about happiness because it provides a numerical way to compare different outcomes
+% - Why don't we care about our friends
+
+%First objective%
+No student can deviate from the truthful strategy to improve his happiness.
+In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.
 
 \subsection{Benchmark}
-Once the assumptions are complete, a benchmark can be selected based on the goals of the system.
-A benchmark will allow for a quantitative way to compare mechanisms.
-To define such a benchmark, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
+%Efficiency objective%
+The next step is to create a system that will allow multiple different models to be compared and evaluated side by side; in other words, a benchmark needs to be created.
+To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
 Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done.
 As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism.
-Mathematically, the goal is to minimize the maximum amount of work done by a single person, as well as minimize maximum deviation between any student's given grade and the grade their assignment deserves.
+In mathematical terms we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
 
@@
 
-\subsection{Rules}
-After a simple set of assumptions and a benchmark are created, the assumptions need to be further developed into a true model that will become the ``rules'' of the game.
+% We now have a well defined problem that we need to solve. Of course the set of assumptions might not be very realistic as we will so we
+
+Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ``''rules'' of the game.
 To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes.
-This added complexity to the previously simple assumptions:
+This turned the list of assumptions from the
+simple into:
+%Repeat above corrections%
 \begin{enumerate}
-  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
-  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-  \item Everyone is risk neutral with respect to happiness
-  \item Students want good grades
-\end{enumerate}
-into:
-\begin{enumerate}
-\item The objective score of an assignment is from 0 to 100
-\item The objective score assigned by the professor is the correct objective score
+\item The objective score of an assignment is from 0 to 100%setting%
+\item The objective score assigned by the professor is the correct objective score%setting%
 \item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort
+
 \item Not everyone has the ability to get the correct objective score
+
 \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
@@
 
-The next step in creating a mechanism
 \section{The Problem}
@@
 
-[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload?
+%[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload?
 Why do you care about accurate grades?

### 2013-09-14 Primes Write up.tex
Finished up methods and materials

@@
 \section{Materials and Methods}
+\subsection{The Scenario}
+In our trying to find a solution to the professor's problem, we created a scenario in which our solution applies to a single assignment.
+This means that our system will have to be repeated for every assignment, instead of performing on a global scale.
+In such a "round" of grading, there are $n$ students, who each bring one ungraded paper to the professor.
+These ungraded papers are like the input for a function.
+Each of these papers has an objective score $o_i\mid 0<o_i<100$.
+This is the score the professor would give out.
+Our mechanism then grades the paper, and outputs these grades.
+After one "round" each student receives a grade $g_i$ and after performing $w_i$ units of work, where for one paper, $w_i=1$.
+The professor is index 0.
+\subsection{Assumptions}
 To create the models that are used to predict the behavior of the students, a set process was used each time.
@@
 To begin with, a simple set of assumptions was created:
-%Note: Specify that the model refers to a single grading round: There are $n$ students and 1 professor.
-Every student comes to us with an ungraded paper (input) define the objective score o_i, we then give those papers grades(output) After a mechanism runs each student receives a grade $g_i$ and after performing $w_i$ units of work.
-Define the professor as index 0.%
+\begin{enumerate}
+	\item Students want good grades
+ 	\item Doing work makes students unhappy
+  	\item Students want to be happy
+ 	\item Students only care about their final happiness
+  	\item The happiness of a student is only affected by their grade and the amount of work they do
+\end{enumerate}
+However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
 \begin{enumerate}
@@
 \end{enumerate}
-%add simple list%
 
-%Explanation of the choice of assumption
-% - We need to talk about happiness because it provides a numerical way to compare different outcomes
-% - Why don't we care about our friends
-
-%First objective%
+\subsection{Why?}
+There are two questions that need to be addressed, first, why is happiness important, and second, why are the scores of others not important?
+The importance of happiness lies in the fact that it provides a way to compare different outcomes; effectively allowing us to show definitively which of two models is better.
+The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, as well as the incredible complexity the model would have to account for with this considered.
+\subsection{First major objective}
 No student can deviate from the truthful strategy to improve his happiness.
@@
 \begin{enumerate}
-\item The objective score of an assignment is from 0 to 100%setting%
-\item The objective score assigned by the professor is the correct objective score%setting%
-\item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort
-
-\item Not everyone has the ability to get the correct objective score
-
-\item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
+\item When grading, $w_i=0 \oplus w_i=1$
+\item For all students, $g_i \neq o_i$
+\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
+\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
+\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
+\item For a given student in $N$, that student has contact with all other students in $N$.
+\end{enumerate}
+Put simply:
+\begin{enumerate}
+\item Students cannot "half bake" an assignment
+\item Students can't always get the exact objective score
 \item Students want good grades
-\item People don't like doing work
-\item Students are selfish and don't care about their friends
-\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-\item Everyone is risk neutral with respect to happiness
-
-\item All students can communicate with all other students
-
+\item Students don't like grading
+\item Students are selfish
+\item Doing work costs 1 unit of effort
+\item Students are risk neutral with respect to happiness
+\item All students can talk to each other
 \end{enumerate}
-
-Put simply, in a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 0 to 100.
-All of these assignments must be graded by someone, and no one can grade their own assignment.
-Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.
 
@@
 
-\section{The Problem}
+\section{Results}
 In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100.

### 2013-09-14 Primes Write up.tex
Discussion

@@
 
+\section{Discussion}
+With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the "game" the way they were meant to, and to efficiently and effectively grade the assignments of these students.
+Although our mechanisms are not truly realistic, the significance of them cannot be denied.
+The mechanisms created by the end of the research came very close to realism, with only one factor missing, and could still be implemented in a classroom environment where all students are capable of grading others assignments efficiently.
+
+The work done in creating these mechanisms further builds upon that which has been done before to try and answer the same question of grading large numbers of papers.
+Much of the previous work done to address this problem involves creating automated mechanisms that simple spit out machine-assigned grades.
+These solutions, as stated previously, are inefficient and often produce unsatisfactory results.
+By creating these mechanisms using game theory, it has been shown that computers do not need to be relied upon to grade papers, opening the way for others to create game theory driven solutions to this problem.
+
+Also, by taking the happiness of the students into account, it can be almost guaranteed that these mechanisms are better for the students than automated grading, or any other solutions attempted before.
+Many of the complaints that students give out include something along the lines of the fact that they cannot give feedback on their feedback, a problem in the Coursera system~\cite{theproblemswithpeergradingincoursera}.
+This problem is fixed in our mechanism by allowing the students to appeal their grades and to have multiple rounds of grading.
+Other commonly expressed problems such as the variability of feedback are also addressed by these mechanisms, which prevent this from happening by having a rigid set of justifications required.
+This means that students cannot simply pass on a paper with the word "good," they must rather take the time to explain why they took off any points they did, or why they gave the paper a perfect score.
+
+Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students.
+In current peer grading schemes, it is easy for students to just "game" the system and fake their way through a course.
+Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{theproblemswithpeergradingincoursera}.
+This allows students to dishonestly grade the work of others, as well as just give whomever they want a better grade than that person actually deserves.
+In our mechanisms, however, these problems are solved by removing anonymity and adding incentives to make students behave honestly, no matter who they are grading.
+
+Aside from fixing many problems that students have with other peer grading systems, our mechanisms also address the unhappiness and inconsistency caused by the grading given out by machines.
+One key problem that machines have is that they always look at the same thing in a paper, meaning that they can be easily "gamed" and fooled into thinking something is better than it acutely is~\cite{robogradingproblems}.
+Not only does this make the system inconsistent, but any student who is lacking something that is in the list of requirements the machine checks for can be unfairly given a poor grade, making them unhappy.
+By solving both of these problems with the mechanisms that were created, it has been demonstrated the peer grading, at least for the moment, is all in all better for education that automated grading.
+
+Not only do the mechanisms developed in this research improve upon the efficiency of automated grading systems, but they also help to remove the dominance that automated grading has placed on grading large courses.
+By providing a system that fixes many of the problems with current automated grading systems, these mechanisms help to show that automated grading is not the only way to solve the problem of grading online courses.
+Because automated grading, at the moment, is not as efficient and robust as it needs to be to prevent students from creating unfair situations, this is something that is necessary to show because automated grading is simply not good enough with today's technology.
+
+By creating a mechanism that is, in theory, more efficient than both current peer grading systems and automated grading systems, it has been shown that there is still room for improvement in the grading of online courses.
+By showing this, a renewed interest in the field can be created, which could lead to others developing more mechanisms that will improve the general education of students in these courses.
+As the ultimate goal of this research is to accomplish this, the idea that the mechanisms not only accomplish this, but also open the road for others to do so is a marked success.
+
+All in all, with the final mechanism, all of the goals that were set up were accomplished, with only total realism absent from the design.
+With this final mechanism, it has been shown that it is possible to create a mathematically driven and effective design that can solve a problem that needs to be solved.
+Not only is this something that has not been done before, but it opens the way for others to build upon this work, something that could eventually lead to the creation of a perfect solution.
+
+However important the creation of these mechanisms is, arguably more important to the future development of further solutions is the creation of a realistic and robust model.
+Without a model, many of the mechanisms mentioned would have been impossible to create, and would certainly not work as well as they do.
+The creation of a model is essential in game theory as it provides the outline for how the "players" of a given game will act under any set of circumstances.
+As such, by creating a good model, this research has undergone the trouble of providing a way for anyone to predict how students will behave.
+
+Not only did this research lead to the creation of a good model, but it also led to the creation of a benchmark.
+The creation of a benchmark is important because it allows two or mechanisms to be compared side by side, and it allows theorists to definitively determine which of these mechanisms is superior.
+With this, it becomes possible to compare the results of this research to the results of others, and also allows future work to be done by others.
+Not only does a benchmark allow the research done here to be compared to that of others, but it allows two totally independent mechanisms not derived from this research to be compared, which could lead to a universal system of evaluating peer grading systems.
+
+Both of these are major contributions towards further developments in the field of research this problem takes place in, primarily game theory.
+By doing so, grading mechanisms across online courses will constantly be able to evolve and improve with contributions from anyone.
+By creating the benchmark and model, all mechanisms will undergo a uniform set of evaluations that will allow online course systems to determine which system is the best out of any proposals.
+By doing so, this research has opened up a road for many game theorists to develop and analyze new ideas that will lead to improvements in student happiness and results from online courses.
+
+Due to the numerous possibilities the creation of a model and benchmark can lead to for future research, it is clear that they are the most important results gained from this research.
+Without them, nothing else could have been done, and no future mechanisms could be created that would be able to be analyzed in the same way that these were.
+Due to the importance of future research in this field, it was imperative that this research led to more solutions in the future, so that the problem that was identified would be quickly and efficiently solved.
+
+Although the models presented by this research are not completely realistic, they do show that there is much room for improvement in the area of grading online courses, and that it is possible to take a strictly mathematical approach at designing a mechanism, and then implementing it using computer science.
+By showing that this is possible, a huge amount of potential for future research has been opened, primarily due to the creation of a benchmark and model.
+With these tools, other game theorists can create their own mechanisms, and compare them to those of others around the world.
+
+Aside from improving previous research done in this field, this research also supports the idea that many others have proposed: that peer grading is more efficient than automated grading.
+When EdX first introduced its automated grading system, many were skeptical of the idea, and had right to be.
+For this reason, systems such as coursera have yet to adopt this, and instead default to peer grading.
+As many people suspected, and as this research confirms, peer grading can indeed be more efficient than automated grading when implemented correctly, simply because the A.I.
+of current machines cannot handle the many different ways a student can answer an open ended question.
+
+Human judgement has always been superior to that of a machine, and this research continues to support that idea.
+As powerful as automated grading can be in practice, when it comes to theory, peer grading is simply more efficient.
+This means that with the right mechanism, such as the ones proposed by this research, so, in practice peer grading should be superior to automated grading.
+All in all, this research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.
 \section{Results}
-In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100.
-All of these assignments must be graded by someone, and no one can grade their own assignment.
-Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.
-
 %[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload?
@@
 
+\bibitem{theproblemswithpeergradingincoursera}
+%http://www.insidehighered.com/blogs/hack-higher-education/problems-peer-grading-coursera
+Author,
+  \emph{Title}.
+  Source,
+  Year.
+
+\bibitem{robogradingproblems}
+%http://bltnotjustasandwich.com/2013/04/05/the-problems-with-moocs-1-robo-essay-grading/
+Author,
+  \emph{Title}.
+  Source,
+  Year.
+
 \end{thebibliography}

### 2013-09-17 Primes Write up.tex
Added chart
Changed bibliography to bibtex and added all the neccesary information, might change format later

@@
 \usepackage{parskip}
+\usepackage{cite}
+\usepackage{graphicx}
 \setlength{\parindent}{15pt}
@@
 \section{Introduction}
+\cite{m85}
 Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole.
@@
 
-\section{Improved Verification Mechanism}
+\section{Improved Calibration Mechanism}
 The major change made in this mechanism was one to assumption number 11. Now assumption 11 reads as follows:
@@
 
-\begin{thebibliography}{9}
-
-\bibitem{canmoocsreducecc}
-  % http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
-  Ruth, S. (2012). \emph{Can MOOCs and existing e-learning paradigms help reduce college costs}? International Journal of Technology in Teaching and Learning, 8(1), 21-32.
-
-\bibitem{makingsenseofmoocs}
-  % http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{swotanalysisofmoocs}
-  % http://www.editlib.org/p/112020
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{rightandwrongmoocs}
-  % http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{boycottfinal}
-  % http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{autograding}
-  % http://www.ecu.edu/cs-acad/fsonline/customcf/committee/tg/2013proposals/08.pdf
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{edxsoftware}
-  % http://www.bostonmagazine.com/news/blog/2013/04/04/edx-now-has-robots-to-grade-your-essays/
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{automatedsystemssuck}
-  Herrington, A., \& Moran, C.
-(2012).
-\emph{Writing to a machine is not writing at all}.
-In N.
-Elliot \& L.
-Perelman (Eds.), Writing assessment in the 21st century: Essays in honor of Edward M.
-White (pp.
-219-232).
-New York, NY: Hampton Press.
-
-\bibitem{howaccurateispeergrading}
-  % http://educationgroup.mit.edu/HHMIEducationGroup/wp-content/uploads/2011/05/Freeman-et-al-2010.pdf
-  Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{theproblemswithpeergradingincoursera}
-%http://www.insidehighered.com/blogs/hack-higher-education/problems-peer-grading-coursera
-Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\bibitem{robogradingproblems}
-%http://bltnotjustasandwich.com/2013/04/05/the-problems-with-moocs-1-robo-essay-grading/
-Author,
-  \emph{Title}.
-  Source,
-  Year.
-
-\end{thebibliography}
+\section{Illustrations}
+{
+\noindent
+\includegraphics[width=\textwidth]{Chart.eps}
+}
+\bibliography{bibliography}{}
+\bibliographystyle{plain}
 \end{document}

### 2013-09-19 Primes Write up.tex
Added conclusion and project abstract, all thats left are illustrations and edits

@@
 }
+\section{Conclusion}
+In this research, we learned and established the validity of game theory and matematically based models when solving complex problems involving human nature.
+Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs
+
+Theoretically, all of our results are perfectly valid, however one must acknowledge that theory is not practice.
+Because of this, it becomes hard to say how valid our results are, since they have not been tested in the real world.
+In the real world, there is always the chance that theory falls apart; this is the main flaw in the validity of our results.
+
+Also, the only other flaw, which is minor in comparison, is that the mechanisms do not account for a perfectly realistic world.
+Even though we completed a model which can be built upon, and applies to the real world, the mechansims designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.
+
+Although there are some errors in the validity of our results, all of them were established and created independant of any prior literature.
+One of the main advantages of this research is that it has not been done before; this is what makes it an interesting idea to explore and develop upon.
+Because of this, there is no prior literature that addresses the problem at hand in the same way that we do.
+
+In the future, one of the experiments that would truly confirm the validity of our results would be to test them in the real world.
+With real world testing in a system where assignments need to be graded, it would quickly become apparent whether the theory behind our mechanisms actually works, and how well it works in the real world.
+This would fix the first of the validity errors that the mechanisms have.
+
+To address the second of these validity errors, more work would need to be done to make the models realistic.
+If we had more time, this would be the first thing that we would do; creating a mechanism that applies to a more realistic world would ready the theory for real testing, and would also patch the second hole in the validity of the mechanisms.
+
+After finalizing the mechanisms, our preffered next step would be to implement software in an existing course system, and use it to test out our ideas.
+By implementing this, it would allow us to use what already exists and build upon it.
+This means that not much would have to be done to encourage people to use it, since they would already be using whatever we implemented it on.
+Also, this would allow us to receive real data for the theory, and using this we could continue the improvement cycle.
+
+Even though the mechansims are not truly valid, only one true question remains unanswered.
+This question being the question of what happens when our theory is introduced into the real world.
+As stated previously, to solve this question, we would prefer to create a system of implementation that would allows us to test our mechanisms.
 \bibliography{bibliography}{}

### 2013-09-19 Primes Write up.tex
Added edits to materials and methods/introduction

@@
 \section{Introduction}
-\cite{m85}
 Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole.
-Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started~\cite{canmoocsreducecc}.
+Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}.
 However, the MOOC's main importance comes from its scalability.
@@
 However, this work introduces what previous attempts lack: a rigorous mathematical analysis of the system using tools from game theory and mechanism design.
-This work sets a concrete set of constraints that a grading system must satisfy to mitigate student incentive to cheat, as well as a concrete benchmark to analyze the efficiency of various systems.
+This work sets a concrete set of constraints that a grading system must satisfy to mitigate students' incentive to cheat, as well as a concrete benchmark to analyze the efficiency of various systems.
 Together, these create a concrete measure for evaluating peer grading systems in terms of efficiency (how much time the professor and students spend grading) and fairness for the students (how accurate their final scores are).
@@
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
-However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e.
-they will just give every assignment a 100).
+However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e how can the professor tell the difference between an acurately assigned hundred and randomly awarded 100).
 The next step would be to implement simple checking: e.g.
 have each paper be graded by two students who both receive bonus points if their grades match.
-This case may work if the students are isolated, but clever students will still just give all papers 100.
+This case may work if the students are isolated, but the professor still can't tell the difference betweena randomly or sincerely awarded grade.
 This way, their papers will match those of other clever students, giving them points without grading.
@@
 \subsection{The Scenario}
-In our trying to find a solution to the professor's problem, we created a scenario in which our solution applies to a single assignment.
-This means that our system will have to be repeated for every assignment, instead of performing on a global scale.
+In our trying to find a solution to the professor's problem, we consider the case of a single assingment.
+To apply them to an entire class, simply apply them to each assignment.
 In such a "round" of grading, there are $n$ students, who each bring one ungraded paper to the professor.
 These ungraded papers are like the input for a function.
-Each of these papers has an objective score $o_i\mid 0<o_i<100$.
+Each of these papers, $i$ has an objective score $o_i\mid 0<o_i<100$.
 This is the score the professor would give out.
-Our mechanism then grades the paper, and outputs these grades.
-After one "round" each student receives a grade $g_i$ and after performing $w_i$ units of work, where for one paper, $w_i=1$.
-The professor is index 0.
+Our mechanism then has the students grade the papers in a clever way and output the grades.
+We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
 \subsection{Assumptions}
-To create the models that are used to predict the behavior of the students, a set process was used each time.
-To begin with, a set of assumptions is created.
+To create the models that are used to predict the behavior of the students, we use a set process every each time.
+To begin with, we create a set of assumptions.
 These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades.
@@
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
+  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness.
+Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
   \item Students want to maximize their final happiness, expressed as $H(g)-W$
@@
 
-\subsection{Why?}
+\paragraph{Why?}
 There are two questions that need to be addressed, first, why is happiness important, and second, why are the scores of others not important?
-The importance of happiness lies in the fact that it provides a way to compare different outcomes; effectively allowing us to show definitively which of two models is better.
-The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, as well as the incredible complexity the model would have to account for with this considered.
+Happiness is important because it provides a measure of the combination of the work performed and grade received.
+The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a coursera course with 150,000 students, it is extremely unlikely that any tudent will ever be able to have any effect on the grade of another student.
+So, for simplicity, we ignore the "friendship" effect.
 \subsection{First major objective}
-No student can deviate from the truthful strategy to improve his happiness.
+The first goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment that the professor asks them to.
+If a system has this property, then it is reasonable to assume that students will always choose to grade every assignment the professor asks them to.
+Without this property, a system becomes extremely unpredictable.
+So, in other words, no student can deviate from the truthful strategy to improve his happiness.
 In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.
@@
 %Efficiency objective%
-The next step is to create a system that will allow multiple different models to be compared and evaluated side by side; in other words, a benchmark needs to be created.
+The next step is to create a system that will allow multiple different mechanisms to be compared and evaluated side by side; in other words, a benchmark needs to be created.
 To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
@@
 
-Caring about the workload is just as important as caring about accurate grades.
-If the system was purely based on minimizing only the work done by a single person, everyone could just get 100.
-Likewise, if the system was purely based on maximizing grade accuracy, the professor could grade everything.
-In order to properly model the problem to achieve a solution that is reasonable, both aspects of the problem need to be considered.
+When creating this benchmark, there are 2 things that need to be considered.
+First of all, caring about accuracy.
+This is important because if we don't care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
+Secondly, caring about work done.
+If we don't care about the amount of work doen, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.
+
+Also, we need to address why we use maximum for these two things, and not sum.
+Caring about the maximum difference in grades and not the sum.
+Consider these two outcomes: each student's real grade should be 90 but they get a 91 and each student's real grade should be a 90, but all of them get a 90 except for 1 who gets a 0.
+In this case, the first case is clearly better, something that is only caputured by a maximum.
+To address caring about the maximum work done, consider these two outcomes: one where a professor grades all $n$ papers, and another where each student grades $2$ papers.
+In this case, the first scenario is far worse, even though the total work performed is less than the second.
+For this reason, we use a maximum.
 
@@
 
-Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ``''rules'' of the game.
-To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes.
-This turned the list of assumptions from the
-simple into:
+Now that a simple set of assumptions and a benchmark have been created, it becomes possible to create simple mechanisms, and improve upon them until we get to a final, satisfactory mechanism.
+
+To improve upon our mechanisms, we need to often change our assumptions.
+This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex situations.
+
+One advantage of this is that we can now address the fact that the above set of assumptions is rather simple and unrealistic, for instance assuming that every student is a perfect grader.
 %Repeat above corrections%
-\begin{enumerate}
-\item When grading, $w_i=0 \oplus w_i=1$
-\item For all students, $g_i \neq o_i$
-\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
-\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
-\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
-\item For a given student in $N$, that student has contact with all other students in $N$.
-\end{enumerate}
-Put simply:
-\begin{enumerate}
-\item Students cannot "half bake" an assignment
-\item Students can't always get the exact objective score
-\item Students want good grades
-\item Students don't like grading
-\item Students are selfish
-\item Doing work costs 1 unit of effort
-\item Students are risk neutral with respect to happiness
-\item All students can talk to each other
-\end{enumerate}
-
-These assumptions provide the necessary environment to begin creating a mechanism, as they state everything that is necessary to understand how students behave.
-Simply put, every assignment has a grade from 1-100, and whatever the professor says goes.
-Every student has a different capacity for grading, and as such not everyone will be able to correctly grade very assignment, but they can only choose to either grade or not grade.
-All students are capable of communicating with each other, and will do so, and the rest is from the simple set of assumptions.
-
-Because it would be illogical to start creating a mechanism to encompass all of these assumptions, every mechanism grows in complexity, with the first one being the most simple.
-Throughout the design process, the assumptions were changed to allow for simplicity, which allows for the creation of simpler models.
-The complex set of assumptions were always kept in mind, however.
 
@@
 Although this is not as good as the previous mechanism, it is still an improvement because there is now positive competition instead of negative.
+\subsection{Final Assumptions}
+Now that we have reached a point far into the research, we are able to propose a model that accounts for a much more realistic and complex world:
 
+\begin{enumerate}
+\item When grading, $w_i=0 \oplus w_i=1$
+\item For all students, $g_i \neq o_i$
+\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
+\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
+\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
+\item For a given student in $N$, that student has contact with all other students in $N$.
+\end{enumerate}
+Put simply:
+\begin{enumerate}
+\item Students cannot "half bake" an assignment
+\item Students can't always get the exact objective score
+\item Students want good grades
+\item Students don't like grading
+\item Students are selfish
+\item Doing work costs 1 unit of effort
+\item Students are risk neutral with respect to happiness
+\item All students can talk to each other
+\end{enumerate}
 \section{Illustrations}

### 2013-09-19 Primes Write up.tex
Added more illustrations, edits.

@@
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
-However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e how can the professor tell the difference between an acurately assigned hundred and randomly awarded 100).
+However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e how can the professor tell the difference between an accurately assigned hundred and randomly awarded 100).
 The next step would be to implement simple checking: e.g.
 have each paper be graded by two students who both receive bonus points if their grades match.
-This case may work if the students are isolated, but the professor still can't tell the difference betweena randomly or sincerely awarded grade.
+This case may work if the students are isolated, but the professor still can't tell the difference between a randomly or sincerely awarded grade.
 This way, their papers will match those of other clever students, giving them points without grading.
@@
 \subsection{The Scenario}
-In our trying to find a solution to the professor's problem, we consider the case of a single assingment.
+In our trying to find a solution to the professor's problem, we consider the case of a single assignment.
 To apply them to an entire class, simply apply them to each assignment.
-In such a "round" of grading, there are $n$ students, who each bring one ungraded paper to the professor.
+In such a ``round''of grading, there are $n$ students, who each bring one ungraded paper to the professor.
 These ungraded papers are like the input for a function.
@@
 Happiness is important because it provides a measure of the combination of the work performed and grade received.
-The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a coursera course with 150,000 students, it is extremely unlikely that any tudent will ever be able to have any effect on the grade of another student.
-So, for simplicity, we ignore the "friendship" effect.
+The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a coursera course with 150,000 students, it is extremely unlikely that any student will ever be able to have any effect on the grade of another student.
+So, for simplicity, we ignore the ``friendship''effect.
 \subsection{First major objective}
@@
 Secondly, caring about work done.
-If we don't care about the amount of work doen, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.
+If we don't care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.
 
@@
 Consider these two outcomes: each student's real grade should be 90 but they get a 91 and each student's real grade should be a 90, but all of them get a 90 except for 1 who gets a 0.
-In this case, the first case is clearly better, something that is only caputured by a maximum.
+In this case, the first case is clearly better, something that is only captured by a maximum.
 To address caring about the maximum work done, consider these two outcomes: one where a professor grades all $n$ papers, and another where each student grades $2$ papers.
@@
 \section{Discussion}
-With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the "game" the way they were meant to, and to efficiently and effectively grade the assignments of these students.
+With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game''the way they were meant to, and to efficiently and effectively grade the assignments of these students.
 Although our mechanisms are not truly realistic, the significance of them cannot be denied.
@@
 Other commonly expressed problems such as the variability of feedback are also addressed by these mechanisms, which prevent this from happening by having a rigid set of justifications required.
-This means that students cannot simply pass on a paper with the word "good," they must rather take the time to explain why they took off any points they did, or why they gave the paper a perfect score.
+This means that students cannot simply pass on a paper with the word ``good,''they must rather take the time to explain why they took off any points they did, or why they gave the paper a perfect score.
 
 Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students.
-In current peer grading schemes, it is easy for students to just "game" the system and fake their way through a course.
+In current peer grading schemes, it is easy for students to just ``game''the system and fake their way through a course.
 Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{theproblemswithpeergradingincoursera}.
@@
 Aside from fixing many problems that students have with other peer grading systems, our mechanisms also address the unhappiness and inconsistency caused by the grading given out by machines.
-One key problem that machines have is that they always look at the same thing in a paper, meaning that they can be easily "gamed" and fooled into thinking something is better than it acutely is~\cite{robogradingproblems}.
+One key problem that machines have is that they always look at the same thing in a paper, meaning that they can be easily ``gamed''and fooled into thinking something is better than it acutely is~\cite{robogradingproblems}.
 Not only does this make the system inconsistent, but any student who is lacking something that is in the list of requirements the machine checks for can be unfairly given a poor grade, making them unhappy.
@@
 Without a model, many of the mechanisms mentioned would have been impossible to create, and would certainly not work as well as they do.
-The creation of a model is essential in game theory as it provides the outline for how the "players" of a given game will act under any set of circumstances.
+The creation of a model is essential in game theory as it provides the outline for how the ``players''of a given game will act under any set of circumstances.
 As such, by creating a good model, this research has undergone the trouble of providing a way for anyone to predict how students will behave.
@@
 When EdX first introduced its automated grading system, many were skeptical of the idea, and had right to be.
-For this reason, systems such as coursera have yet to adopt this, and instead default to peer grading.
+For this reason, systems such as Coursera have yet to adopt this, and instead default to peer grading.
 As many people suspected, and as this research confirms, peer grading can indeed be more efficient than automated grading when implemented correctly, simply because the A.I.
@@
 
-Human judgement has always been superior to that of a machine, and this research continues to support that idea.
+Human judgment has always been superior to that of a machine, and this research continues to support that idea.
 As powerful as automated grading can be in practice, when it comes to theory, peer grading is simply more efficient.
@@
 \section{The Calibration Mechanism}
+\label{sec:calibration}
 
@@
 If they graded correctly, their assigned grade is guaranteed to be at least some minimum value.
+
+See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.
 
@@
 \section{The Deduction Mechanism}
+\label{sec:deduction}
 In the new mechanism, a different strategy was created; one that would ideally work better than the previous ones.
@@
 
+See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.
+
 \subsection{Why it Works}
-The grader's have two choices, they can either grade the papers, or not grade them.
+The graders have two choices, they can either grade the papers, or not grade them.
 
-If the grader does not grade the paper, what score should he give it?
+If the grader does not grade the paper, what score should he or she give it?
 
-If they take off any points, the points will surely be refuted by the professor during the regrade.
-So if they take off any points, they will get a 0 on the grading assignment.
-If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.
+If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
+If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.
 $$$$
-If the grader does grade the paper, what score should he give it?
+If the grader does grade the paper, what score should he or she give it?
 
-If he gives it a lower score, they throw away free points, and if they give it a lower score there is a risk of them getting a 0 because the scores could be refuted.
-So, giving it the correct score is the best because it guarantees at least a 50.
+If the grader takes off fewer points than the true score of the assignment, he or she is throwing away free points.
+If the grader deducts too aggressively, there is a risk for him or her to get a 0 because the score could be refuted.
+Therefore, assigning the correct score is the best because it guarantees at least a 50.
 
-So assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
+Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
 	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
@@
 
-If the grader's partner gives the paper its true grade:
+If the partner gives the paper its true grade:
 	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
@@
 \begin{enumerate}
-\item Students cannot "half bake" an assignment
+\item Students cannot ``half bake''an assignment
 \item Students can't always get the exact objective score
@@
 \noindent
-\includegraphics[width=\textwidth]{Chart.eps}
+\begin{figure}
+	\centering
+		\label{fig:comparison}
+		\includegraphics[width=\textwidth]{Comparison.eps}
+		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
+		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
+		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
+\end{figure}
 }
 \section{Conclusion}
-In this research, we learned and established the validity of game theory and matematically based models when solving complex problems involving human nature.
+In this research, we learned and established the validity of game theory and mathematically based models when solving complex problems involving human nature.
 Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs
@@
 Also, the only other flaw, which is minor in comparison, is that the mechanisms do not account for a perfectly realistic world.
-Even though we completed a model which can be built upon, and applies to the real world, the mechansims designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.
+Even though we completed a model which can be built upon, and applies to the real world, the mechanisms designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.
 
-Although there are some errors in the validity of our results, all of them were established and created independant of any prior literature.
+Although there are some errors in the validity of our results, all of them were established and created independent of any prior literature.
 One of the main advantages of this research is that it has not been done before; this is what makes it an interesting idea to explore and develop upon.
@@
 
-After finalizing the mechanisms, our preffered next step would be to implement software in an existing course system, and use it to test out our ideas.
+After finalizing the mechanisms, our preferred next step would be to implement software in an existing course system, and use it to test out our ideas.
 By implementing this, it would allow us to use what already exists and build upon it.
@@
 
-Even though the mechansims are not truly valid, only one true question remains unanswered.
+Even though the mechanisms are not truly valid, only one true question remains unanswered.
 This question being the question of what happens when our theory is introduced into the real world.

### 2013-09-19 Primes Write up.tex
For merge

--- 2013-09-19 Primes Write up.tex
@@
 \usepackage{graphicx}
+\usepackage{amsthm}
 \setlength{\parindent}{15pt}
+\newtheorem{theorem}{Theorem}
 \begin{document}
@@
 Having this measurement model is a large contribution in itself, because it allows comparison between different systems.
-Although a theoretical model cannot predict exactly what will happen in practice, game theory and mechanism design have a history of generally determining mechanisms that work in practice from ones that do not.
+Although a theoretical model cannot predict exactly what will happen in practice, game theory and mechanism design have a history of generally determining mechanisms that work in practice from ones that do not~\cite{AGTbook}.
 Mechanisms that do not follow game theoretic constraints may work in the short-term, but they will be exploited if possible in the long term~\cite{boycottfinal}.
@@
 \section{Results}
-%[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload?
-Why do you care about accurate grades?
-If you just care about workload, give everyone 100.
-If you just care about grades, have the professor grade everything.
-Need to consider both to properly model the problem.]
 Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested.
@@
 
-\section{The Calibration Mechanism}
+\subsection{The Calibration Mechanism}
 
-This mechanism is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.
+First we design a mechansim that does extremely well in the simple model we defined above.
 
-\subsection{Mechanism}
+\subsubsection{Mechanism}
 In the mechanism, the professor grades one paper, called \emph{X}.
-The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper.
+The professor then distributes all the students' papers randomly among the students, while making sure that no student receives his or her own paper.
 Every student is also given a copy of \emph{X}.
-
+\begin{theorem}
 The professor then tells the students that ``Out of the two papers you were given, one of them has been graded by me, and the other hasn't.
-If you fail to give the correct grade for the one I graded, then you will receive a 0.'' The students then go about their business grading the papers, and individually report the grades they gave out to the professor.
+If you fail to give the correct grade for the one I graded, then you will receive a 0.'' The students then grade the papers, and individually report the grades they gave out to the professor.
 Then, just like the professor promised, if the students graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment.
 If they graded correctly, their assigned grade is guaranteed to be at least some minimum value.
+\end{theorem}
+\begin{proof}
+G is the maximum of \{ some minimum value, the assigned grade \}.
+The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
 
-\subsection{Why it Works}
-G is the maximum of \{ some minimum value, the assigned grade \}.
+If they grade both papers, their happiness will be equal to $H(G)-2$Because they spent two units of energy, and are guaranteed to get G.
 
-The happiness of one student grading one paper is equivalent to $$\frac{H(G)+H(0)}{2}-1$$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
-
-If they grade both papers, their happiness will be equal to $$H(G)-2$$Because they spent two units of energy, and are guaranteed to get G.
-
-If they grade neither then the happiness will be $$H(0)$$ Because they automatically get a 0, but spend no energy.
+If they grade neither then the happiness will be $H(0)$ Because they automatically get a 0, but spend no energy.
 
@@
 So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
-\subsection{Results}
-The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
+The teacher expends one unit of effort, students each spend 2, as long as the teacher set the minimum value high enough.
 Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
-This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
+So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
+\end{proof}
+\subsection{Benchmark}
 The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.
 
-\subsection{Problems}
+\subsubsection{Problems}
 The goal for this mechanism was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
@@
 So if they take off any points, they will get a 0 on the grading assignment.
-If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.
-$$$$
+If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.\\
 If the grader does grade the paper, what score should he give it?
@@
 To find out how efficient this mechanism is, two things needed to be analyzed:
-1) Is everyone an honest flagger?
-$$$$
+1) Is everyone an honest flagger?\\
 2) Do the graders grade honestly

### 2013-09-20 Primes Write up.tex
Finished up my edits to results and such. Not much left

--- 2013-09-19 Primes Write up.tex
@@
 \usepackage{graphicx}
+\usepackage{amsthm}
+\usepackage{wrapfig}
+\usepackage[section]{placeins}
+\usepackage{enumitem}
 \setlength{\parindent}{15pt}
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
 \begin{document}
@@
 To begin with, a simple set of assumptions was created:
-\begin{enumerate}
+\begin{enumerate}[itemsep=0pt, parsep=0pt]
 	\item Students want good grades
@@
 However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
-\begin{enumerate}
+\begin{enumerate}[itemsep=0pt, parsep=0pt]
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
@@
 %Repeat above corrections%
+\section{Results}
+Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested.
+This is where mechanism design and game theory comes into play.
+Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose.
+Then, game theory is used to mathematically predict student behavior to benchmark such a system.
+Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months.
+The end result is fairly complete, although there are still questions to be answered in future work.
 
+\subsection{The Calibration Mechanism}
+
+\subsubsection{Mechanism}
+First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
+\begin{definition}(Calibration Mechanism)
+In this mechanism, the professor chooses one paper to grade, which he gives to every student, along with a second, ungraded paper.
+If the students fail to grade the paper the professor graded correctly, they get a 0.
+Otherwise they get the minimum of an arbitrary number $???$ and the grade their assigned grade.
+\end{definition}
+\begin{theorem}
+With this mechanism, all students should behave honestly and the mechanism shoul output accurate grades while maintaining a low amount of per-person work.
+\end{theorem}
+\begin{proof}[Why this works]
+See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.
+
+G is the maximum of \{ some minimum value, the assigned grade \}.
+The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
+
+If they grade both papers, their happiness will be equal to $H(G)-2$Because they spent two units of energy, and are guaranteed to get G.
+
+If they grade neither then the happiness will be $H(0)$ Because they automatically get a 0, but spend no energy.
+
+This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(???) > H(0) + 2$.
+The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value high enough.
+Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
+So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
+\end{proof}
+\subsubsection{Benchmark}
+The means that the value of the objective function in this case is 4, a very low value, because it is exactly the same as if we convinced every student to grade accurately grade 4 papers.
+
+\subsubsection{Problems}
+This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other.
+If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.
+
+\subsection{Improved Calibration Mechanism}
+\subsubsection{The Mechanism}
+In the calibration mechanism, we assumed that students couldn't communicate with each other.
+For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
+\begin{definition}(Improved Calibration Mechanism)
+In this mechanism, we apply the calibration mechanism on a larger scale.
+Every student grades the papers of \emph{k} other students.
+The professor also grades every \emph{kth} paper, these are the calibrated papers.
+The same system for assigning grades is used as in the calibration mechanism.
+\end{definition}
+\begin{theorem}
+In this mechanism, students will return accurate grades, even though they can communicate with each other.
+\end{theorem}
+\begin{proof}
+In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other.
+As such, there are 3 options for the students.
+They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$.
+This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.
+
+Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers.
+As long as the minimum value is high enough, the papers will be accurately graded, as before.
+\end{proof}
+\subsubsection{Benchmark and Problems}
+The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before.
+The huge problem with this is the high amount of work being done.
+
+\subsection{The Deduction Mechanism}
+With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions.
+Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
+\subsubsection{Mechanism}
+See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.
+\begin{definition}(Deduction Mechanism)
+In this mechanism, each paper is randomly assigned to 2 students.
+Students deduct as many points as they want, and write a justification for each of them.
+For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$.
+Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0.
+To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$.
+(Then the student’s grade is converted from Happiness to an actual score).
+\end{definition}
+\begin{theorem}
+The addition of the contribution score being added or subtraced should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
+\end{theorem}
+\begin{proof}
+The graders have two choices, they can either grade the papers, or not grade them.
+
+If the grader does not grade the paper, what score should he or she give it?
+
+If they take off any points, the points will surely be refuted by the professor during the regrade.
+So if they take off any points, they will get a 0 on the grading assignment.
+If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.\\
+If the grader does grade the paper, what score should he give it?
+
+If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
+If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.\\
+If the grader does grade the paper, what score should he or she give it?
+
+If the grader takes off fewer points than the true score of the assignment, he or she is throwing away free points.
+If the grader deducts too aggressively, there is a risk for him or her to get a 0 because the score could be refuted.
+Therefore, assigning the correct score is the best because it guarantees at least a 50.
+
+Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
+	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
+	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
+
+If the partner gives the paper its true grade:
+	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
+	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
+
+Therefore, it is in everyone's best interest to honestly grade the paper.
+\end{proof}
+\subsection{Final Assumptions}
+Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inablitity to deal with students who are incompetent graders.
+With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.
+
+\begin{enumerate}[itemsep=0pt, parsep=0pt]
+\item When grading, $w_i=0 \oplus w_i=1$
+\item For all students, $g_i \neq o_i$
+\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
+\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
+\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
+\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
+\item For a given student in $N$, that student has contact with all other students in $N$.
+\end{enumerate}
+% Put simply:
+% \begin{enumerate}[itemsep=0pt, parsep=0pt]
+% \item Students cannot ``half bake''an assignment
+% \item Students can't always get the exact objective score
+% \item Students want good grades
+% \item Students don't like grading
+% \item Students are selfish
+% \item Doing work costs 1 unit of effort
+% \item Students are risk neutral with respect to happiness
+% \item All students can talk to each other
+% \end{enumerate}
+\newpage
+\section{Illustrations}
+\begin{figure}[!ht]
+	\centering
+		\includegraphics[width=0.9\textwidth]{Comparison.eps}
+		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
+		\vspace{-100pt}
+		\label{fig:Comparisongraph}
+\end{figure}
+\begin{figure}[!ht]
+	\centering
+		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
+		\caption {A flowchart of the Calibration Mechanism from the student perspective.}
+		\label{fig:calibration}
+\end{figure}
+\begin{figure}[!ht]
+	\centering
+		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
+		\caption {A flowchart of the Deduction Mechanism from the student perspective.}
+		\label{fig:deduction}
+\end{figure}
 \section{Discussion}
@@
 All in all, this research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.
-\section{Results}
-%[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload?
-Why do you care about accurate grades?
-If you just care about workload, give everyone 100.
-If you just care about grades, have the professor grade everything.
-Need to consider both to properly model the problem.]
-Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested.
-This is where mechanism design and game theory comes into play.
-Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose.
-Then, game theory is used to mathematically predict student behavior to benchmark such a system.
-Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months.
-The end result is fairly complete, although there are still questions to be answered in future work.
 
-\section{The Calibration Mechanism}
-\label{sec:calibration}
-
-This mechanism is quite unrealistic, but not by such a degree that it is unimaginable. Because of this, it was possible to create a perfect solution if the problem took place in this situation.
-
-\subsection{Mechanism}
-In the mechanism, the professor grades one paper, called \emph{X}.
-The professor then distributes all the student's papers randomly among the students, while making sure that no student receives his or her own paper.
-Every student is also given a copy of \emph{X}.
-
-The professor then tells the students that ``Out of the two papers you were given, one of them has been graded by me, and the other hasn't.
-If you fail to give the correct grade for the one I graded, then you will receive a 0.'' The students then go about their business grading the papers, and individually report the grades they gave out to the professor.
-Then, just like the professor promised, if the students graded the pre-graded, or \emph{calibrated} paper incorrectly, then that grader gets a 0 on the assignment.
-If they graded correctly, their assigned grade is guaranteed to be at least some minimum value.
-
-See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.
-
-\subsection{Why it Works}
-G is the maximum of \{ some minimum value, the assigned grade \}.
-
-The happiness of one student grading one paper is equivalent to $$\frac{H(G)+H(0)}{2}-1$$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
-
-If they grade both papers, their happiness will be equal to $$H(G)-2$$Because they spent two units of energy, and are guaranteed to get G.
-
-If they grade neither then the happiness will be $$H(0)$$ Because they automatically get a 0, but spend no energy.
-
-This means that if $H(G) - 2 > H(0)$, then student will grade both papers.
-So, for the professor to guarantee that the students use effort and obtain the correct grades, he or she would choose a minimum value such that $H(G) > H(0) + 2$.
-\subsection{Results}
-The teacher expends one unit of effort, and the students each spend 2, as long as the teacher set the minimum value high enough.
-Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
-This means that the maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
-The means that the value of the objective function in this case is 4, a very low value, which shows how effective this solution is.
-
-\subsection{Problems}
-The goal for this mechanism was to make it more realistic while still making it simple to understand, and have a simply solution that would be easy for students to understand.
-There is now a mechanism that works very well in an unrealistic scenario, so we moved on to a new mechanism.
-
-\section{Improved Calibration Mechanism}
-The major change made in this mechanism was one to assumption number 11. Now assumption 11 reads as follows:
-\emph{All students are able to communicate with each other}
-
-This provides a very different scenario than the original mechanism, because now students will be able to figure out which papers are calibrated.
-However, it would be better to try and generalize the previous solution and apply it to the new mechanism, which leads to the following scheme.
-
-\subsection{Mechanism}
-The first attempt to apply a solution to this mechanism was a near carbon copy of the previous scheme.
-The class is arranged in a virtual circle, where every student grades the papers of the \emph{k} students to the right of them.
-The professor also grades every \emph{kth} paper starting from some random point in the circle.
-If a student mis-grades the calibrated paper, they get a 0, otherwise they get the maximum of their objective score and the minimum value from the previous mechanism.
-
-\subsection{Why it Works}
-In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other.
-As such, there are 3 options for the students.
-
-1) They can grade 0 papers, giving them a happiness of $H(0) = 0$
-
-2) They can grade all the papers they are assigned, giving them a happiness of $H(g) - k$
-
-3) They can grade i papers giving them a happiness of $(k-i)\div k \cdot H(G)-i$.
-This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.
-
-\subsection{Results}
-Even though the students can communicate with one another, they will have no way to determine which paper is calibrated, and are thus best off grading all the papers.
-
-\subsection{Problems}
-The major problem with this method is the amount of work.
-The professor has to grade $\frac{n}{k}$ papers, which can be massive in a class of 1000+ students.
-For this reason a different mechanism was necessary.
-
-\section{The Deduction Mechanism}
-\label{sec:deduction}
-In the new mechanism, a different strategy was created; one that would ideally work better than the previous ones.
-
-\subsection{Mechanism}
-For each assignment, a new assignment is created to evaluate the performance of the graders.
-Every student receives 2 papers from different people, so that each paper overlaps with one other person, and every paper is distributed twice.
-The student then chooses how many points to subtract, and writes a justification for each one of these points.
-Graders are then given a contribution score from 1 to -1.
-From each of the 2 assignments they grade, they get their points deducted / total points deducted-0.5.
-Then, if the original writers of the papers can appeal their grade if they are unhappy with it.
-The professor will grade the paper, and if any of the graders were wrong, they get a 0.
-To compute the final score, the grader's final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to H(the student's assigned grade).
-(Then the student's grade is converted from Happiness to an actual score).
-
-See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.
-
-\subsection{Why it Works}
-The graders have two choices, they can either grade the papers, or not grade them.
-
-If the grader does not grade the paper, what score should he or she give it?
-
-If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
-If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.
-$$$$
-If the grader does grade the paper, what score should he or she give it?
-
-If the grader takes off fewer points than the true score of the assignment, he or she is throwing away free points.
-If the grader deducts too aggressively, there is a risk for him or her to get a 0 because the score could be refuted.
-Therefore, assigning the correct score is the best because it guarantees at least a 50.
-
-Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
-	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
-
-If the partner gives the paper its true grade:
-	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
-	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
-
-Therefore, it is in everyone's best interest to honestly grade the paper.
-
-\subsection{Results}
-Assuming that everyone acts in the dominant strategy behavior, the maximum work for teacher is 0, the maximum work done for students is 2. 
-Because everyone honestly grades the papers, the maximum deviation is 0.
-So, the objective function is 2, which is even better than the first mechanism.
-
-\subsection{Problems}
-Although the result that was produced for the previous mechanism is rather good, it encourages very harsh competition between students, and would make the classroom environment feel very negative.
-This means that finding a different solution to the same problem was necessary, in which students are placed in positive competition, instead of the negative one formed by trying to find the most mistakes
-
-\section{The Flag Mechanism}
-For the next mechanism, all of the assumptions were kept the same, and simply tried to find a way to better the feeling of negative competition.
-\subsection{Mechanism}
-Start by having each paper get graded by two people.
-Then, the original writer of this paper chooses which of the two grades he / she would like to have, and looks over the justifications for losing any points on both papers.
-If they see that any of these justifications are incorrect, they flag the paper and send it to the professor.
-Following this, the paper they chose to have is sent to a third party, who grades the paper, and checks if their grade is close to the one that was given to the paper.
-If it isn't, the paper is sent to the professor.
-After everything that needs to be flagged has been, the professor grades all the flagged papers, and rewards people who were correct with a 2 point bonus.
-If no papers from any group were flagged, every grader in that group gets two points.
-Final grades are whatever the person chose if there was no flagging, or whatever the professor gave them if there was.
-\subsection{Why it Works}
-To find out how efficient this mechanism is, two things needed to be analyzed:
-1) Is everyone an honest flagger?
-$$$$
-2) Do the graders grade honestly
-\subsubsection{Flagging}
-There are two cases for this:
-
-1) They guess a random score and try to flag everything
-
--In this case, the chance of gaining points is so low that it is negligible
-
-2) They take the time to flag correctly
-
--In this case they could get 2 points back, so it is the most beneficial
-\subsubsection{Grading}
-Once again, there are two cases here: People grading, and people not grading
-
-If people don't bother grading anything, what score should they give the paper?
-
--100 because anything lower than the actual score will be flagged by the writer, and because of useless justifications, they will lose points.
-100 is the only score guaranteed to be greater than or equal to the correct score
-
-Their happiness in this case will be 0, because they use no effort, but also have no chance of gaining points since their paper will definitely get flagged
-
-The happiness of people who honestly grade, on the other hand, will be a +1 gain, because they use 1 unit of effort to grade and they get 2 units back guaranteed.
-This higher gain means that it is beneficial to grade honestly.
-
-\subsection{Results}
-Because everyone is honest, we can now analyze the score of the mechanism:
-
-Maximum work done by one person: 3 (student who flags one paper and grades 2 others)
-
-Maximum deviation: 1 (1 point gain for being a good grader)
-
-Final score: 4
-
-Although this is not as good as the previous mechanism, it is still an improvement because there is now positive competition instead of negative.
-\subsection{Final Assumptions}
-Now that we have reached a point far into the research, we are able to propose a model that accounts for a much more realistic and complex world:
-
-\begin{enumerate}
-\item When grading, $w_i=0 \oplus w_i=1$
-\item For all students, $g_i \neq o_i$
-\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
-\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
-\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
-\item For a given student in $N$, that student has contact with all other students in $N$.
-\end{enumerate}
-Put simply:
-\begin{enumerate}
-\item Students cannot ``half bake''an assignment
-\item Students can't always get the exact objective score
-\item Students want good grades
-\item Students don't like grading
-\item Students are selfish
-\item Doing work costs 1 unit of effort
-\item Students are risk neutral with respect to happiness
-\item All students can talk to each other
-\end{enumerate}
-\section{Illustrations}
-{
-\noindent
-\begin{figure}
-	\centering
-		\label{fig:comparison}
-		\includegraphics[width=\textwidth]{Comparison.eps}
-		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
-\end{figure}
-\begin{figure}
-	\centering
-		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
-		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
-\end{figure}
-\begin{figure}
-	\centering
-		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
-		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
-\end{figure}
-}
 \section{Conclusion}
@@
 As stated previously, to solve this question, we would prefer to create a system of implementation that would allows us to test our mechanisms.
+\newpage
 \bibliography{bibliography}{}

### 2013-09-21 Primes Write up.tex
Edited to near perfection

@@
 \title{Teaching a Class to Grade Itself using Game Theory}
-\author{Nick Kaashoek and William Wu}
-\date{\today}
+\author{}%Nick Kaashoek and William Wu
+\date{}
 \usepackage[margin=1in]{geometry}
@@
 multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}.
-Even though automated grading for written essays is an active area of research with much recent progress, a usable solution does not yet exist~\cite{automatedsystemssuck}.
+Even though automated grading for written essays is an active area of research with much recent progress, but the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}.
 On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}.
@@
 The problem of grading large numbers of submissions is important to solve.
-Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge.
-Because this limits their learning abilities, it is imperative to create an efficient system that enables students to receive feedback to learn efficiently.
+Without a solid solution, MOOCs cannot provide efficient feedback for students taking them.
+This renders the students unable to effectively evaluate the mastery of the course material.
+Therefore, it is imperative to create an efficient system that enables students to receive feedback to learn effectively.
 
@@
 Using the assumptions and rules, game theory can predict how students will behave when they ``play''.
-This way, mechanism efficiency and effectiveness cam be proved, allowing the evaluation of different sets of rules.
+This way, mechanism efficiency and effectiveness can be proved, allowing the evaluation of different sets of rules.
 
@@
 
-This research opportunity is made interesting by the complexity of human nature as well as its necessity for practical use.
-This paper will cover the thought process of mechanisms leading up to the final mechanism of grading, as well as explain the final mechanism and its implications.
-All mechanisms and related calculations will be presented.
-Section 2 describes the mathematical definition of the problem as well as its rules and assumptions.
+This research opportunity is made interesting by the complexity of human nature as well as its huge practical value.
+This paper will cover the thought process of mechanisms leading up to the final mechanism and its implications.
+All mechanisms and related calculations will be compared in terms of scalability and effectiveness.
 
@@
 \subsection{The Scenario}
-In our trying to find a solution to the professor's problem, we consider the case of a single assignment.
-To apply them to an entire class, simply apply them to each assignment.
-In such a ``round''of grading, there are $n$ students, who each bring one ungraded paper to the professor.
+The first step to remedy the professor's problem is to follow the grading of a single assignment.
+The assignment is easy enough to consider independently, and can be generalized to multiple assignments.
+In such a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor.
 These ungraded papers are like the input for a function.
@@
 \end{enumerate}
-However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
-\begin{enumerate}[itemsep=0pt, parsep=0pt]
+To re-express the above in mathematics:
+\begin{enumerate}
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
@@
 
-\paragraph{Why?}
-There are two questions that need to be addressed, first, why is happiness important, and second, why are the scores of others not important?
+There are two things that need to be considered: the importance of a student's own happiness and the irrelevance of others' grades.
 Happiness is important because it provides a measure of the combination of the work performed and grade received.
-The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a coursera course with 150,000 students, it is extremely unlikely that any student will ever be able to have any effect on the grade of another student.
+The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a Coursera course with 150,000 students~\cite{swotanalysisofmoocs}, it is extremely unlikely that any student will ever be able to have any effect on the grade of another student.
 So, for simplicity, we ignore the ``friendship''effect.
@@
 %Efficiency objective%
-The next step is to create a system that will allow multiple different mechanisms to be compared and evaluated side by side; in other words, a benchmark needs to be created.
-To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are.
-Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done.
-As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism.
-In mathematical terms we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
+A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development.
+Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced.
+Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desired outcome.
+In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
 
-When creating this benchmark, there are 2 things that need to be considered.
-First of all, caring about accuracy.
-This is important because if we don't care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
+When creating this benchmark, there are 2 things that need to be considered: accuracy and workload.
+Accuracy is important because if we don't care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
 Secondly, caring about work done.
@@
 \subsection{The Calibration Mechanism}
+\label{sec:calibration}
 
-\subsubsection{Mechanism}
+\subsubsection{Process}
 First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
@@
 \end{theorem}
-\begin{proof}[Why this works]
-See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.
 
+\begin{proof}[Analysis]
 G is the maximum of \{ some minimum value, the assigned grade \}.
@@
 \end{proof}
-\subsubsection{Benchmark}
+\emph{This process is summarized in figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}
+
+\subsubsection{Benchmark and Remaining Issues}
 The means that the value of the objective function in this case is 4, a very low value, because it is exactly the same as if we convinced every student to grade accurately grade 4 papers.
 
-\subsubsection{Problems}
+\emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+
 This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other.
@@
 \subsection{Improved Calibration Mechanism}
-\subsubsection{The Mechanism}
+\subsubsection{Process}
 In the calibration mechanism, we assumed that students couldn't communicate with each other.
@@
 \end{theorem}
-\begin{proof}
+\begin{proof}[Analysis]
 In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other.
@@
 \end{proof}
-\subsubsection{Benchmark and Problems}
+\subsubsection{Benchmark and Remaining Issues}
 The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before.
@@
 
+\emph{The benchmark results for The Improved Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+
 \subsection{The Deduction Mechanism}
+\label{sec:deduction}
 With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions.
 Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
-\subsubsection{Mechanism}
-See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.
+\subsubsection{Process}
 \begin{definition}(Deduction Mechanism)
@@
 \end{theorem}
-\begin{proof}
+\begin{proof}[Analysis]
 The graders have two choices, they can either grade the papers, or not grade them.
@@
 Therefore, it is in everyone's best interest to honestly grade the paper.
+
 \end{proof}
+\emph{This process is summarized in figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
+
+\emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+
 \subsection{Final Assumptions}
@@
 \end{enumerate}
-% Put simply:
-% \begin{enumerate}[itemsep=0pt, parsep=0pt]
-% \item Students cannot ``half bake''an assignment
-% \item Students can't always get the exact objective score
-% \item Students want good grades
-% \item Students don't like grading
-% \item Students are selfish
-% \item Doing work costs 1 unit of effort
-% \item Students are risk neutral with respect to happiness
-% \item All students can talk to each other
-% \end{enumerate}
-\newpage
 \section{Illustrations}
-\begin{figure}[!ht]
+{
+\noindent
+\begin{figure}[!h]
 	\centering
-		\includegraphics[width=0.9\textwidth]{Comparison.eps}
-		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
-		\vspace{-100pt}
-		\label{fig:Comparisongraph}
+		\includegraphics[width=\textwidth]{Comparison.eps}
+		\caption {A comparison of mechanisms in terms of effectiveness and scalability.\label{fig:comparison}}
 \end{figure}
-\begin{figure}[!ht]
+\begin{figure}
 	\centering
-		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
-		\caption {A flowchart of the Calibration Mechanism from the student perspective.}
-		\label{fig:calibration}
+		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
+		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
 \end{figure}
-\begin{figure}[!ht]
+\begin{figure}
 	\centering
-		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
-		\caption {A flowchart of the Deduction Mechanism from the student perspective.}
-		\label{fig:deduction}
+		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
+		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
 \end{figure}
+}
 \section{Discussion}
@@
 Also, by taking the happiness of the students into account, it can be almost guaranteed that these mechanisms are better for the students than automated grading, or any other solutions attempted before.
-Many of the complaints that students give out include something along the lines of the fact that they cannot give feedback on their feedback, a problem in the Coursera system~\cite{theproblemswithpeergradingincoursera}.
+Many of the complaints that students give out include something along the lines of the fact that they cannot give feedback on their feedback, a problem in the Coursera system~\cite{howaccurateispeergrading}.
 This problem is fixed in our mechanism by allowing the students to appeal their grades and to have multiple rounds of grading.
@@
 In current peer grading schemes, it is easy for students to just ``game''the system and fake their way through a course.
-Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{theproblemswithpeergradingincoursera}.
+Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}.
 This allows students to dishonestly grade the work of others, as well as just give whomever they want a better grade than that person actually deserves.

### 2013-09-22 Primes Write up.tex
Fixed most of Tanya's suggestions.

@@
 
-The difficulty of the problem lies in finding an incentive for students to spend time to grade assignments of others who they don't care about.
+The difficulty of the problem lies in finding an incentive for students to spend time to grade assignments of others who they do not care about.
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
@@
 have each paper be graded by two students who both receive bonus points if their grades match.
-This case may work if the students are isolated, but the professor still can't tell the difference between a randomly or sincerely awarded grade.
+This case may work if the students are isolated, but the professor still cannot tell the difference between a randomly or sincerely awarded grade.
 This way, their papers will match those of other clever students, giving them points without grading.
@@
 Because human nature dictates that people will do whatever is in their best interest and may try to outsmart the system, coming up with a strict set of rules to encourage the desired behavior can be quite challenging.
-A mechanism should be made as simple as possible, but the above examples show that a small amount of simplicity must be sacrificed to obtain a system that can't be manipulated.
+A mechanism should be made as simple as possible, but the above examples show that a small amount of simplicity must be sacrificed to obtain a system that cannot be manipulated.
 
@@
   \item Students want to maximize their final happiness, expressed as $H(g)-W$
-  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
-  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
+  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
+  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
 \end{enumerate}
@@
 So, for simplicity, we ignore the ``friendship''effect.
-\subsection{First major objective}
-The first goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment that the professor asks them to.
-If a system has this property, then it is reasonable to assume that students will always choose to grade every assignment the professor asks them to.
+
+\subsection{Objective}
+The goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment they are given to grade.
 Without this property, a system becomes extremely unpredictable.
-So, in other words, no student can deviate from the truthful strategy to improve his happiness.
-In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.
+In other words, no student can deviate from the truthful strategy to improve his or her happiness.
+In math terms, if by acting honestly student $i$ grades $w_i$ papers and gets a grade of $g_i$ there should not be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.
 
@@
 When creating this benchmark, there are 2 things that need to be considered: accuracy and workload.
-Accuracy is important because if we don't care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
+Accuracy is important because if we do not care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
 Secondly, caring about work done.
-If we don't care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.
+If we do not care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.
 
-Also, we need to address why we use maximum for these two things, and not sum.
-Caring about the maximum difference in grades and not the sum.
-Consider these two outcomes: each student's real grade should be 90 but they get a 91 and each student's real grade should be a 90, but all of them get a 90 except for 1 who gets a 0.
-In this case, the first case is clearly better, something that is only captured by a maximum.
-To address caring about the maximum work done, consider these two outcomes: one where a professor grades all $n$ papers, and another where each student grades $2$ papers.
-In this case, the first scenario is far worse, even though the total work performed is less than the second.
-For this reason, we use a maximum.
+In our case, we used the \emph{maximum} deviation and the \emph{maximum} work done.
+The reason why we didn't use the\emph{sum} of the deviations or the \emph{sum} of work done is the following.
+Consider these two cases for the maximum deviation of the student-given grade to the hypothetical professor-given grade.
+\begin{enumerate}[label=\Alph*]
+\item Each of 1000 students should receive a 90, but their peers assigned them a 91. Maximum deviation is 1, sum is 1000.
+\item Each of 1000 students should receive a 90. One person is assigned a 0, while everyone else is assigned a 90. Maximum deviation is 90, sum is 90.
+\end{enumerate}
+Clearly, case A is better than case B. The smaller maximum deviation for case A reflects this.
+For the maximum work done, consider the the following cases:
+\begin{enumerate}[label=\Alph*]
+\item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
+\item Each of 1000 students grades 2 papers. Maximum work is 2, sum is 2000.
+\end{enumerate}
+This time, case B is intuitively better than case A. Again, the smaller maximum deviation agrees.
 
@@
 If the students fail to grade the paper the professor graded correctly, they get a 0.
-Otherwise they get the minimum of an arbitrary number $???$ and the grade their assigned grade.
+Otherwise they get the minimum of an arbitrary number $m$ and the grade their assigned grade.
 \end{definition}
@@
 \begin{proof}[Analysis]
-G is the maximum of \{ some minimum value, the assigned grade \}.
-The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
+Let $G$ be the maximum of \{some minimum value $m$, the assigned grade\}.
+The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$, because the students have a 0.5 chance of getting a 0 and a 0.5 chance of getting $G$.
 
-If they grade both papers, their happiness will be equal to $H(G)-2$Because they spent two units of energy, and are guaranteed to get G.
+If a student grades both papers, his or her happiness will be equal to $H(G)-2$. Because the grader spent two units of energy, and are guaranteed to get $G$.
 
-If they grade neither then the happiness will be $H(0)$ Because they automatically get a 0, but spend no energy.
+If a student grades neither, his or her happiness will be $H(0)$, because he or she automatically get a 0 but spend no energy.
 
-This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(???) > H(0) + 2$.
-The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value high enough.
+This means that if $H(G) - 2 > H(0)$, then a student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(m) > H(0) + 2$.
+The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value $m$ high enough.
 Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
@@
 \end{proof}
-\emph{This process is summarized in figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}
+\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}
 
 \subsubsection{Benchmark and Remaining Issues}
-The means that the value of the objective function in this case is 4, a very low value, because it is exactly the same as if we convinced every student to grade accurately grade 4 papers.
+Computed from the above, the objective function of this mechanism is 4 --- a very low value. A value of 4 is equivalent to if we convinced every student to grade accurately grade 4 papers.
 
-\emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
 
@@
 \subsubsection{Process}
-In the calibration mechanism, we assumed that students couldn't communicate with each other.
+In the calibration mechanism, we assumed that students could not communicate with each other.
 For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
@@
 In this mechanism, we apply the calibration mechanism on a larger scale.
-Every student grades the papers of \emph{k} other students.
-The professor also grades every \emph{kth} paper, these are the calibrated papers.
+Every student grades the papers of $k$ other students.
+The professor also grades every $k$th paper, these are the calibrated papers.
 The same system for assigning grades is used as in the calibration mechanism.
@@
 They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$.
-This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.
+This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.
 
@@
 
-\emph{The benchmark results for The Improved Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for The Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
 
@@
 Students deduct as many points as they want, and write a justification for each of them.
-For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$.
+For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$.
 Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0.
@@
 
-Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
+Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they do not grade, then
+	If they do not grade the paper, they do not use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
 	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
@@
 If the partner gives the paper its true grade:
-	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
+	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
 	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
@@
 \end{proof}
-\emph{This process is summarized in figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
+\emph{This process is summarized in Figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
 
-\emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
 
@@
 \item For all students, $g_i \neq o_i$
-\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
+\item Students all share a common happiness function, $H(g)$, where $g$ represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
 \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
 \item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
-\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
-\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
-\item For a given student in $N$, that student has contact with all other students in $N$.
+\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
+\item For a given student in $N$, that student has contact with all other students in $N$
 \end{enumerate}
@@
 		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
-		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
+		\caption {A flowchart of the Calibration Mechanism (Section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
 \end{figure}
@@
 		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
-		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
+		\caption {A flowchart of the Deduction Mechanism (Section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
 \end{figure}
@@
 \section{Discussion}
-With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game''the way they were meant to, and to efficiently and effectively grade the assignments of these students.
+With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game'' the way they were meant to, and to efficiently and effectively grade the assignments of these students.
 Although our mechanisms are not truly realistic, the significance of them cannot be denied.
@@
 Not only did this research lead to the creation of a good model, but it also led to the creation of a benchmark.
-The creation of a benchmark is important because it allows two or mechanisms to be compared side by side, and it allows theorists to definitively determine which of these mechanisms is superior.
+The creation of a benchmark is important because it allows two mechanisms to be compared side by side, and it allows theorists to definitively determine which of these mechanisms is superior.
 With this, it becomes possible to compare the results of this research to the results of others, and also allows future work to be done by others.
@@
 
-Due to the numerous possibilities the creation of a model and benchmark can lead to for future research, it is clear that they are the most important results gained from this research.
+Due to the numerous possibilities the creation of a model and benchmark can lead to future research, it is clear that they are the most important results gained from this research.
 Without them, nothing else could have been done, and no future mechanisms could be created that would be able to be analyzed in the same way that these were.
@@
 
+As our mechanisms evolve, the benchmark scores yielded by each tends to decrease.
+However, this is not the case with the improved calibration mechanism, which actually provided a higher benchmark score than the previous mechanism.
+This stems from the fact that the assumptions were changed, and the mechanism was not.
+This shows that with a change in assumptions, a new mechanism must be created to address the change, as old mechanisms will often perform badly in new models.
+
+In comparison with more traditional methods of peer grading, our mechanisms peformed extremely well, aside from the improved calibration mechanism.
+\emph{See figure~\ref{fig:comparison} on page~\pageref{fig:comparison} for a graphical representation of this}.
+As can be seen in this figure, the benchmark scores of all traditional methods of grading (peer grading, hand grading by the professor, and automated grading), have higher benchark scores than our mechanisms.
+This means that they are flawed in some way, either in the accuracy of their grades, or the amount of work that one person has to do.
+
+With this comparison, it can be clearly seen that the mechanisms created with this research are more efficient than any currently employed in modern classrooms.
+
 \section{Conclusion}
 In this research, we learned and established the validity of game theory and mathematically based models when solving complex problems involving human nature.
-Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs
+Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs.
 

### 2013-09-22 Primes Write up.tex
Edits

--- 2013-09-21 Primes Write up.tex
@@
 
+With this in mind, we set out to create a series of mechanisms that increase in complexity, as well as creating an ever-changing model.
+We start with a simple model and set of assumptions and gradually build upon this set to increase the realism of the model.
+After every change in assumptions, we create a new mechanism that applies to the new set of assumptions, and works effectively and efficiently.
+By the end of our research, we have contributed a highly realistic and detailed model that other game theorists can build off of to form their own solutions, as well as a set of realistic mechanisms that could be implemented in practice.
 \section{Materials and Methods}
@@
 To re-express the above in mathematics:
-\begin{enumerate}
+\begin{enumerate}[itemsep=0pt, parsep=0pt]
   \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
@@
 \begin{theorem}
-With this mechanism, all students should behave honestly and the mechanism shoul output accurate grades while maintaining a low amount of per-person work.
+With this mechanism, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
 \end{theorem}
 
-\begin{proof}[Analysis]
+\begin{proof}
 G is the maximum of \{ some minimum value, the assigned grade \}.
@@
 \end{theorem}
-\begin{proof}[Analysis]
+\begin{proof}
 In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other.
@@
 Students deduct as many points as they want, and write a justification for each of them.
-For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$.
+For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$.
 Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0.
@@
 \begin{theorem}
-The addition of the contribution score being added or subtraced should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
+The addition of the contribution score being added or subtracted should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
 \end{theorem}
-\begin{proof}[Analysis]
+\begin{proof}
 The graders have two choices, they can either grade the papers, or not grade them.
@@
 
-If they take off any points, the points will surely be refuted by the professor during the regrade.
-So if they take off any points, they will get a 0 on the grading assignment.
-If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.\\
+If they take off any points that shouldn't be taken off, the points will surely be refuted by the professor during the regrade.
+So if they take off any points, they will get a 0 on the grading assignment because of the professor's punishment.
+If the grader gives the paper 100, they might get 0.5 if the other grader also gives it 100.
+If he gives it anything else, the original grader will get 0.
+This is much better than a guaranteed zero, so they will give the paper 100.
+
 If the grader does grade the paper, what score should he give it?
 
-If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
-If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.\\
-If the grader does grade the paper, what score should he or she give it?
+Obviously, if the student takes the effort to grade the paper, they will give the paper its true score, because doing anything else either forfeits a higher contribution score, or guarantees a 0 due to the professor's punishment.
+This means that they are guaranteed at least a contribution score of 0.5, so after grading both of their assigned papers, the graders will get a full contribution score of 1.
 
-If the grader takes off fewer points than the true score of the assignment, he or she is throwing away free points.
-If the grader deducts too aggressively, there is a risk for him or her to get a 0 because the score could be refuted.
-Therefore, assigning the correct score is the best because it guarantees at least a 50.
+Now that we know what the students will do, lets look at what happens when we introduce the grading partner.
 
-Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
-	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
+If the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
+	If they don't grade the paper, they don't use any effort, and their contribution score is 0. So the student's happiness will $H(g) + 4*0 = H(g)$.
+
+If they do grade, they use 1 unit of effort by default, but get the full contribution score of 1. This means that their final happiness is $H(g) + 4*1 - 1 = H(g)+3$.
 
 If the partner gives the paper its true grade:
-	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
-	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
+	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is $H(g) + 4*-1 = H(g)-4$.
 
-Therefore, it is in everyone's best interest to honestly grade the paper.
+If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is $H(g) + 4*0 - 1 = H(g)-1$.
+
+In both of the above cases, the happiness outputs for honestly grading the paper is higher than the happiness output when not grading the paper.
+Our assumptions state that students will do whatever makes them happiest, so they will honestly grade the papers.
 
 \end{proof}
+\noindent
 \emph{This process is summarized in figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
-
+\newline
 \emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
-
+\subsubsection{Benchmark}
+In this model, the most work is being done by the students, who each grade 2 papers.
+In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper.
+This means that no papers will ever reach the professor, so he/she will not have to grade anything.
+Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades.
+This means that the final benchmark is $2+0=2$.
+This is the lowest out of all the mechanisms so far.
 \subsection{Final Assumptions}
-Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inablitity to deal with students who are incompetent graders.
+Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders.
 With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.
@@
 \end{enumerate}
+\newpage
 \section{Illustrations}
@@
 	\centering
-		\includegraphics[width=\textwidth]{Comparison.eps}
+		\includegraphics[width=0.75\textwidth]{Comparison.eps}
 		\caption {A comparison of mechanisms in terms of effectiveness and scalability.\label{fig:comparison}}
@@
 	\centering
-		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
+		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
 		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
@@
 	\centering
-		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
+		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
 		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
@@
 
+As our mechanisms evolve, the benchmark scores yielded by each tends to decrease.
+However, this is not the case with the improved calibration mechanism, which actually provided a higher benchmark score than the previous mechanism.
+This stems from the fact that the assumptions were changed, and the mechanism was not.
+This shows that with a change in assumptions, a new mechanism must be created to address the change, as old mechanisms will often perform badly in new models.
+
+In comparison with more traditional methods of peer grading, our mechanisms peformed extremely well, aside from the improved calibration mechanism.
+\emph{See figure~\ref{fig:comparison} on page~\pageref{fig:comparison} for a graphical representation of this}.
+As can be seen in this figure, the benchmark scores of all traditional methods of grading (peer grading, hand grading by the professor, and automated grading), have higher benchark scores than our mechanisms.
+This means that they are flawed in some way, either in the accuracy of their grades, or the amount of work that one person has to do.
+
+With this comparison, it can be clearly seen that the mechanisms created with this research are more efficient than any currently employed in modern classrooms.
+
 \section{Conclusion}

### 2013-09-22 Primes Write up.tex
Resolved auto-merge artifacts

--- 2013-09-22 Primes Write up.tex
@@
 \begin{theorem}
-With this mechanism, all students should behave honestly and the mechanism shoul output accurate grades while maintaining a low amount of per-person work.
+With this mechanism, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
 \end{theorem}
 
-\begin{proof}[Analysis]
-Let $G$ be the maximum of \{some minimum value $m$, the assigned grade\}.
-The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$, because the students have a 0.5 chance of getting a 0 and a 0.5 chance of getting $G$.
+\begin{proof}
+G is the maximum of \{ some minimum value, the assigned grade \}.
+The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
 
@@
 This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.
-
 Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers.
@@
 Students deduct as many points as they want, and write a justification for each of them.
-For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$.
+For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$.
 Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0.
@@
 
-If they take off any points, the points will surely be refuted by the professor during the regrade.
-So if they take off any points, they will get a 0 on the grading assignment.
-If the grader's give it 100, they might get 50 if the other grader also gives it 100. If he gives it anything else, the original grader will get 0.\\
+If they take off any points that shouldn't be taken off, the points will surely be refuted by the professor during the regrade.
+So if they take off any points, they will get a 0 on the grading assignment because of the professor's punishment.
+If the grader gives the paper 100, they might get 0.5 if the other grader also gives it 100.
+If he gives it anything else, the original grader will get 0.
+This is much better than a guaranteed zero, so they will give the paper 100.
+
 If the grader does grade the paper, what score should he give it?
 
-If the grader randomly takes off any points, the points will surely be refuted by the professor during the regrade, and the grader will get a 0 on the grading assignment.
-If the grader gives it 100, he or she will get a 0 the grading assignment if his or her partner does not give 100. In the case of agreement, both graders get 50 on the grading assignment.\\
-If the grader does grade the paper, what score should he or she give it?
+Obviously, if the student takes the effort to grade the paper, they will give the paper its true score, because doing anything else either forfeits a higher contribution score, or guarantees a 0 due to the professor's punishment.
+This means that they are guaranteed at least a contribution score of 0.5, so after grading both of their assigned papers, the graders will get a full contribution score of 1.
 
-If the grader takes off fewer points than the true score of the assignment, he or she is throwing away free points.
-If the grader deducts too aggressively, there is a risk for him or her to get a 0 because the score could be refuted.
-Therefore, assigning the correct score is the best because it guarantees at least a 50.
+Now that we know what the students will do, lets look at what happens when we introduce the grading partner.
 
-Assuming that the student's partner gives the paper a 100, which is the best thing they could do if they do not grade, then
-	If they do not grade the paper, they do not use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
-	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1
+If the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
+	If they don't grade the paper, they don't use any effort, and their contribution score is 0. So the student's happiness will $H(g) + 4*0 = H(g)$.
+
+If the student grades, he or she uses 1 unit of effort by default, but get the full contribution score of 1. This means that their final happiness is $H(g) + 4\cdot1 - 1 = H(g)+3$.
 
 If the partner gives the paper its true grade:
-	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
-	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
+	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is $H(g) + 4\cdot(-1) = H(g)-4$.
 
-Therefore, it is in everyone's best interest to honestly grade the paper.
+If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is $H(g) + 4\cdot0 - 1 = H(g)-1$.
+
+In both of the above cases, the happiness outputs for honestly grading the paper is higher than the happiness output when not grading the paper.
+Our assumptions state that students will do whatever makes them happiest, so they will honestly grade the papers.
 
 \end{proof}
+\noindent
 \emph{This process is summarized in Figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}
-
+\newline
 \emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
-
+\subsubsection{Benchmark}
+In this model, the most work is being done by the students, who each grade 2 papers.
+In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper.
+This means that no papers will ever reach the professor, so he/she will not have to grade anything.
+Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades.
+This means that the final benchmark is $2+0=2$.
+This is the lowest out of all the mechanisms so far.
 \subsection{Final Assumptions}
-Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inablitity to deal with students who are incompetent graders.
+Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders.
 With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.
@@
 	\centering
-		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
+		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
 		\caption {A flowchart of the Calibration Mechanism (Section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
@@
 	\centering
-		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
+		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
 		\caption {A flowchart of the Deduction Mechanism (Section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}

### 2013-09-22 Primes Write up.tex
Added minor fixes

@@
 \subsection{The Scenario}
-The first step to remedy the professor's problem is to follow the grading of a single assignment.
-The assignment is easy enough to consider independently, and can be generalized to multiple assignments.
+In order to find a solution to the professor’s problem, we consider the case of a single assingment.
+To apply our solution to an entire class, simply apply it to each assignment separately.
 In such a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor.
 These ungraded papers are like the input for a function.
-Each of these papers, $i$ has an objective score $o_i\mid 0<o_i<100$.
+Each of these papers, $i$ has an objective score $o_i,~where~ 0\leq o_i \leq 100$.
 This is the score the professor would give out.
@@
 \subsection{Assumptions}
-To create the models that are used to predict the behavior of the students, we use a set process every each time.
+To create the models that are used to predict the behavior of the students, we use a set process every time.
 To begin with, we create a set of assumptions.
@@
 The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side.
-To begin with, a simple set of assumptions was created:
+To begin with, we create a simple set of assumptions:
 \begin{enumerate}[itemsep=0pt, parsep=0pt]
@@
 Happiness is important because it provides a measure of the combination of the work performed and grade received.
-The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a Coursera course with 150,000 students~\cite{swotanalysisofmoocs}, it is extremely unlikely that any student will ever be able to have any effect on the grade of another student.
-So, for simplicity, we ignore the ``friendship''effect.
+The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness.
+If a student has 100 friends in a class of 150,000, the chance that he will ever have the opportunity to affect the grades of his friends is tiny.
+For simplicity, we ignore this tiny probability and assume it is 0.
 
@@
 Without this property, a system becomes extremely unpredictable.
-In other words, no student can deviate from the truthful strategy to improve his or her happiness.
+In other words, no student can deviate from the desired behavior to improve his or her happiness.
 In math terms, if by acting honestly student $i$ grades $w_i$ papers and gets a grade of $g_i$ there should not be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.
@@
 
-In our case, we used the \emph{maximum} deviation and the \emph{maximum} work done.
-The reason why we didn't use the\emph{sum} of the deviations or the \emph{sum} of work done is the following.
+In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done.
+The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is the following.
 Consider these two cases for the maximum deviation of the student-given grade to the hypothetical professor-given grade.
@@
 
-One advantage of this is that we can now address the fact that the above set of assumptions is rather simple and unrealistic, for instance assuming that every student is a perfect grader.
 %Repeat above corrections%

### 2013-09-22 Primes Write up.tex
Merged everybody's changes.

@@
 Consider these two cases for the maximum deviation of the student-given grade to the hypothetical professor-given grade.
-\begin{enumerate}[label=\Alph*]
+\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
 \item Each of 1000 students should receive a 90, but their peers assigned them a 91. Maximum deviation is 1, sum is 1000.
@@
 For the maximum work done, consider the the following cases:
-\begin{enumerate}[label=\Alph*]
+\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
 \item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
@@
 \begin{proof}
-G is the maximum of \{ some minimum value, the assigned grade \}.
-The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.
+Let $G$ be the maximum of \{some minimum value $m$, the assigned grade\}.
+The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$, because the students have a 0.5 chance of getting a 0 and a 0.5 chance of getting $G$.
 
@@
 \subsubsection{Benchmark and Remaining Issues}
-Computed from the above, the objective function of this mechanism is 4 --- a very low value. A value of 4 is equivalent to if we convinced every student to grade accurately grade 4 papers.
+Computed from the above, the objective function of this mechanism is 4 --- a very low value. A value of 4 is equivalent to if we convinced every student to accurately grade 4 papers.
 
@@
 This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.
+
 Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers.
@@
 To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$.
-(Then the student’s grade is converted from Happiness to an actual score).
+(Then the student's grade is converted from Happiness to an actual score).
 \end{definition}
@@
 
-If they take off any points that shouldn't be taken off, the points will surely be refuted by the professor during the regrade.
+If they take off any points that should not be taken off, the points will surely be refuted by the professor during the regrade.
 So if they take off any points, they will get a 0 on the grading assignment because of the professor's punishment.
@@
 
-If the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
-	If they don't grade the paper, they don't use any effort, and their contribution score is 0. So the student's happiness will $H(g) + 4*0 = H(g)$.
+If the student's partner gives the paper a 100, which is the best thing they could do if they do not grade, then
+	If they do not grade the paper, they do not use any effort, and their contribution score is 0. So the student's happiness will $H(g) + 4*0 = H(g)$.
 
@@
 \section{Discussion}
-With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game'' the way they were meant to, and to efficiently and effectively grade the assignments of these students.
-Although our mechanisms are not truly realistic, the significance of them cannot be denied.
-The mechanisms created by the end of the research came very close to realism, with only one factor missing, and could still be implemented in a classroom environment where all students are capable of grading others assignments efficiently.
+With this research, the goal was to create a mechanism that fulfilled our goal; incentivizing students to play the ``game'' to correctly grade the assignments of other students.
+The mechanism created by the end of the research was realistic enough to be implemented in a classroom environment where all students are capable of grading others assignments efficiently.
 
-The work done in creating these mechanisms further builds upon that which has been done before to try and answer the same question of grading large numbers of papers.
-Much of the previous work done to address this problem involves creating automated mechanisms that simple spit out machine-assigned grades.
-These solutions, as stated previously, are inefficient and often produce unsatisfactory results.
-By creating these mechanisms using game theory, it has been shown that computers do not need to be relied upon to grade papers, opening the way for others to create game theory driven solutions to this problem.
+The work done in this research furthers past solutions of grading large numbers of papers, some of which involve creating automated mechanisms that assign non-human grades.
+These automated solutions, as stated before, often produce unsatisfactory results.
+By creating a grading mechanism using game theory, we have shown that computers do not need to be relied upon to accurately and efficiently grade papers, leading the way for others to create game-theory-driven solutions to this problem.
 
-Also, by taking the happiness of the students into account, it can be almost guaranteed that these mechanisms are better for the students than automated grading, or any other solutions attempted before.
-Many of the complaints that students give out include something along the lines of the fact that they cannot give feedback on their feedback, a problem in the Coursera system~\cite{howaccurateispeergrading}.
-This problem is fixed in our mechanism by allowing the students to appeal their grades and to have multiple rounds of grading.
-Other commonly expressed problems such as the variability of feedback are also addressed by these mechanisms, which prevent this from happening by having a rigid set of justifications required.
-This means that students cannot simply pass on a paper with the word ``good,''they must rather take the time to explain why they took off any points they did, or why they gave the paper a perfect score.
+By taking the happiness of the students into account, it can be almost guaranteed that these mechanisms are better for the students than automated grading, or any other solutions attempted before.
+Many student-given complaints express the lack of feedback the students can provide about their grades.
+This problem, found in systems such as Coursera~\cite{howaccurateispeergrading}, is solved by our mechanisms by allowing the students to appeal their grades and to have multiple rounds of grading.
+Our mechanisms addresses other commonly expressed problems such as inconsistency of feedback by requiring a reason for every deduction made --- students must take the time to explain any deductions, or why they gave the paper a perfect score.
 
@@
 
-In comparison with more traditional methods of peer grading, our mechanisms peformed extremely well, aside from the improved calibration mechanism.
+In comparison with more traditional methods of peer grading, our mechanisms performed extremely well, aside from the improved calibration mechanism.
 \emph{See figure~\ref{fig:comparison} on page~\pageref{fig:comparison} for a graphical representation of this}.
-As can be seen in this figure, the benchmark scores of all traditional methods of grading (peer grading, hand grading by the professor, and automated grading), have higher benchark scores than our mechanisms.
+As can be seen in this figure, the benchmark scores of all traditional methods of grading (peer grading, hand grading by the professor, and automated grading), have higher benchmark scores than our mechanisms.
 This means that they are flawed in some way, either in the accuracy of their grades, or the amount of work that one person has to do.

### 2013-09-22 Primes Write up.tex
Made revisions to a plethora of things.
Primarily, the Calibration Mechanism.

@@
 
-With this in mind, we set out to create a series of mechanisms that increase in complexity, as well as creating an ever-changing model.
+With this in mind, we set out to create a series of mechanisms that increase in complexity, as well as an increasingly-realistic model.
 We start with a simple model and set of assumptions and gradually build upon this set to increase the realism of the model.
@@
 \subsection{The Scenario}
-In order to find a solution to the professor’s problem, we consider the case of a single assingment.
+In order to find a solution to the professor's problem, we consider the case of a single assignment.
 To apply our solution to an entire class, simply apply it to each assignment separately.
@@
 Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced.
-Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desired outcome.
+Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desirable outcome.
 In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
@@
 Accuracy is important because if we do not care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
-Secondly, caring about work done.
-If we do not care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.
+Secondly, ignoring the amount of work done means the professor grade can everything.
+This is bad because it makes the professor extremely unhappy.
 
@@
 The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is the following.
-Consider these two cases for the maximum deviation of the student-given grade to the hypothetical professor-given grade.
+Consider these two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade.
+Note that the grade the student receives at the end is not necessarily that given by their peers.
 \begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
-\item Each of 1000 students should receive a 90, but their peers assigned them a 91. Maximum deviation is 1, sum is 1000.
+\item Each of 1000 students should receive a 90, but the mechanism assigned a 91 to each of them. Maximum deviation is 1, sum is 1000.
 \item Each of 1000 students should receive a 90. One person is assigned a 0, while everyone else is assigned a 90. Maximum deviation is 90, sum is 90.
@@
 \end{enumerate}
-This time, case B is intuitively better than case A. Again, the smaller maximum deviation agrees.
+This time, case B is intuitively better than case A. Again, the benchmark captures our intuition.
 
@@
 
-Now that a simple set of assumptions and a benchmark have been created, it becomes possible to create simple mechanisms, and improve upon them until we get to a final, satisfactory mechanism.
-
-To improve upon our mechanisms, we need to often change our assumptions.
-This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex situations.
+Now that we have created a simple set of assumptions and a benchmark, we can create several simple mechanisms, and improve upon them until we are satisfied with a final mechanism.
+In the improvement process, we gradually refine our assumptions to better represent reality.
+This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex yet more realistic situations.
 
@@
 First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
+One idea is to have the professor choose one paper that he grades.
+He then distributes this paper to every student, along with a second, ungraded paper.
+If the students fail to grade the paper the professor graded correctly, they get a 0.
+If they succeed, they receive their assigned grade.
+This is almost exactly the Calibration Mechanism, except we make a small modification.
+Considering the idea as is, a student whose own grade on the assignment is a 0 has no incentive to grade the paper: Their grade will be a 0 whether or not they grade the paper, so why bother?
+To cope with this, we pick some minimum grade $m > 0$ and promise every student that they will receive a grade of at least $m$ if they grade the assignment correctly.
+By appropriately choosing a value for $m$, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
 \begin{definition}(Calibration Mechanism)
-In this mechanism, the professor chooses one paper to grade, which he gives to every student, along with a second, ungraded paper.
-If the students fail to grade the paper the professor graded correctly, they get a 0.
-Otherwise they get the minimum of an arbitrary number $m$ and the grade their assigned grade.
+First, the professor pre-grades a paper $P$.
+Each student is asked to grade two papers: $P$ and another paper.
+If the student fails to grade $P$, he or she gets a zero.
+Otherwise, the student gets the maximum of some minimum value and his or her assigned grade.
 \end{definition}
 \begin{theorem}
-With this mechanism, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
+If $m>H^{-1}(2)$, it will be in every student's best interest to grade both papers in the Calibration Mechanism.
 \end{theorem}
+\begin{proof}
+Consider the student $i$.
+If all other students behave as desired, student $i$ will be assigned a grade $G=max(m,o_i)$ unless he or she does not grade $P$ correctly.
+The happiness of student $i$ grading one paper is $\frac{H(G)}{2}-1$, because the student has a 50\% chance of getting a 0 and a 50\% chance of getting $G$.
+If student $i$ grades both papers, his or her happiness will be $H(G)-2$ because he or she is guaranteed to receive $G$ by grading both correctly.
+If student $i$ grades neither, his or her happiness will be $0$, because he or she  spends no energy and gets a 0.
+Therefore, if $H(G) > 2$, then student $i$ will grade both papers. So, for the professor to guarantee that the class use effort and obtain the correct grades, $H(m) > 2$.
+Since we chose $m$ to be greater than $H^{-1}(2)$, the previous always holds.
+\end{proof}
+\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}
 
+\subsubsection{Benchmark and Remaining Issues}
+We now show that the Calibration Mechanism achieves a very low value in our benchmark.
+\begin{theorem}
+The Calibration Mechanism achieves a benchmark score of 4.
+\end{theorem}
 \begin{proof}
-Let $G$ be the maximum of \{some minimum value $m$, the assigned grade\}.
-The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$, because the students have a 0.5 chance of getting a 0 and a 0.5 chance of getting $G$.
-
-If a student grades both papers, his or her happiness will be equal to $H(G)-2$. Because the grader spent two units of energy, and are guaranteed to get $G$.
-
-If a student grades neither, his or her happiness will be $H(0)$, because he or she automatically get a 0 but spend no energy.
-
-This means that if $H(G) - 2 > H(0)$, then a student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(m) > H(0) + 2$.
 The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value $m$ high enough.
@@
 \end{proof}
-\emph{This process is summarized in Figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}
-
-\subsubsection{Benchmark and Remaining Issues}
-Computed from the above, the objective function of this mechanism is 4 --- a very low value. A value of 4 is equivalent to if we convinced every student to accurately grade 4 papers.
 
@@
 If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.
-
+%%%%%%%% Go over this section and try to make it similar to the above section. %%%%%%%%
 \subsection{Improved Calibration Mechanism}
 \subsubsection{Process}
-In the calibration mechanism, we assumed that students could not communicate with each other.
-For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
+In the calibration mechanism, we assumed that students couldn't communicate with each other, and therefore couldn't figure out which of the two papers they were asked to grade was calibrated.
+For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.
 \begin{definition}(Improved Calibration Mechanism)
-In this mechanism, we apply the calibration mechanism on a larger scale.
-Every student grades the papers of $k$ other students.
-The professor also grades every $k$th paper, these are the calibrated papers.
+In this mechanism, we apply the Calibration Mechanism on a larger scale.
+Every student is put into a cycle.
+Each student grades the papers of $k$ next students.
+The professor also grades every $kth$ paper in the cycle, which become the calibrated papers.
 The same system for assigning grades is used as in the calibration mechanism.
@@
 Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers.
-As long as the minimum value is high enough, the papers will be accurately graded, as before.
+As long as $m > H^{-1}(k)$, the papers will be accurately graded, as before.
+
 \end{proof}
 \subsubsection{Benchmark and Remaining Issues}
-The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before.
-The huge problem with this is the high amount of work being done.
+The amount of work done by the professor is $\frac{n}{k}$.
+For the students, this number is $k$.
+The maximum grade deviation is also $k$, for $m > H^{-1}(k)$.
+Therefore, the benchmark $max(k, \frac{n}{k}) + k$, a potentially higher value than before.
+The huge problem with this is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$.
+We can see that the benchmark becomes $2\sqrt{n}$.
 
 \emph{The benchmark results for The Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
-
+%%%%%%%% Revise this section to be like the above. %%%%%%%%
 \subsection{The Deduction Mechanism}
@@
 For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$.
-Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0.
-To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$.
+Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives the incorrect grader(s) a 0.
+To compute the final score for a student, the final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$.
 (Then the student's grade is converted from Happiness to an actual score).
@@
 In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper.
-This means that no papers will ever reach the professor, so he/she will not have to grade anything.
+This means that no papers will ever reach the professor, so he or she will not have to grade anything.
 Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades.
@@
 \noindent
+%%%%%%%% Make sure the comparison chart shows 2*sqrt(n) %%%%%%%%
 \begin{figure}[!h]
@@
 }
+%%%%%%%% Go over this section, make edits and revise. %%%%%%%%
 \section{Discussion}

### 2013-09-25 Primes Write up.tex
Re-compiled paper.
Fixed conclusion and a bit of discussion.
Also, fixed typos, double spaces, tabs, and missing periods.

@@
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
-However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e how can the professor tell the difference between an accurately assigned hundred and randomly awarded 100).
+However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e.
+how can the professor tell the difference between an accurately assigned hundred and randomly awarded 100).
 The next step would be to implement simple checking: e.g.
@@
 
-This research opportunity is made interesting by the complexity of human nature as well as its huge practical value.
+This research topic is made interesting by the complexity of human nature as well as its huge practical value.
 This paper will cover the thought process of mechanisms leading up to the final mechanism and its implications.
@@
 
-With this in mind, we set out to create a series of mechanisms that increase in complexity, as well as an increasingly-realistic model.
-We start with a simple model and set of assumptions and gradually build upon this set to increase the realism of the model.
-After every change in assumptions, we create a new mechanism that applies to the new set of assumptions, and works effectively and efficiently.
+We start with a simple model and set of assumptions and gradually build upon this set to achieve an increasingly-realistic model.
+After every change in assumptions, we create a new mechanism that works effectively and efficiently.
 By the end of our research, we have contributed a highly realistic and detailed model that other game theorists can build off of to form their own solutions, as well as a set of realistic mechanisms that could be implemented in practice.
 \section{Materials and Methods}
-\subsection{The Scenario}
+\subsection{Scenario}
 In order to find a solution to the professor's problem, we consider the case of a single assignment.
@@
 	\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness.
+	\item Students can grade others' work accurately (i.e.
+they can find $o_i$) but doing so costs one unit of happiness.
 Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
@@
 In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
+This benchmarking function is known as the \emph{Objective function}, which we will reference in our research.
 
@@
 
-\subsection{The Calibration Mechanism}
+\subsection{Calibration Mechanism}
 \label{sec:calibration}
@@
 
-\emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for the Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}, together with results from other mechanisms.}
 
@@
 \subsubsection{Process}
-In the calibration mechanism, we assumed that students couldn't communicate with each other, and therefore couldn't figure out which of the two papers they were asked to grade was calibrated.
+In the calibration mechanism, we assumed that students could not communicate with each other, and therefore could not figure out which of the two papers they were asked to grade was calibrated.
 For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.
@@
 
-\emph{The benchmark results for The Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for the Improved Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
 %%%%%%%% Revise this section to be like the above. %%%%%%%%
-\subsection{The Deduction Mechanism}
+\subsection{Deduction Mechanism}
 \label{sec:deduction}
@@
 \newline
-\emph{The benchmark results for The Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for the Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
 \subsubsection{Benchmark}
@@
 \subsection{Final Assumptions}
-Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders.
-With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.
+Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view.
+However, the Deduction Mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders.
+To address this, we designed a final set of assumptions that more effectively simulate a realistic world.
 
@@
 Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students.
-In current peer grading schemes, it is easy for students to just ``game''the system and fake their way through a course.
+In current peer grading schemes, it is easy for students to just ``game'' the system and fake their way through a course.
 Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}.
@@
 Not only does this make the system inconsistent, but any student who is lacking something that is in the list of requirements the machine checks for can be unfairly given a poor grade, making them unhappy.
-By solving both of these problems with the mechanisms that were created, it has been demonstrated the peer grading, at least for the moment, is all in all better for education that automated grading.
+By solving both of these problems with the mechanisms that were created, it has been demonstrated the peer grading, at least for the moment, is better for education that automated grading.
 
@@
 
-All in all, with the final mechanism, all of the goals that were set up were accomplished, with only total realism absent from the design.
+With the final mechanism, all of the goals that were set up were accomplished, with only total realism absent from the design.
 With this final mechanism, it has been shown that it is possible to create a mathematically driven and effective design that can solve a problem that needs to be solved.
@@
 This means that with the right mechanism, such as the ones proposed by this research, so, in practice peer grading should be superior to automated grading.
-All in all, this research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.
+This research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.
 
 As our mechanisms evolve, the benchmark scores yielded by each tends to decrease.
-However, this is not the case with the improved calibration mechanism, which actually provided a higher benchmark score than the previous mechanism.
+However, this is not the case with the Improved Calibration Mechanism, which actually provided a higher benchmark score than the previous mechanism.
 This stems from the fact that the assumptions were changed, and the mechanism was not.
@@
 
-In comparison with more traditional methods of peer grading, our mechanisms performed extremely well, aside from the improved calibration mechanism.
-\emph{See figure~\ref{fig:comparison} on page~\pageref{fig:comparison} for a graphical representation of this}.
-As can be seen in this figure, the benchmark scores of all traditional methods of grading (peer grading, hand grading by the professor, and automated grading), have higher benchmark scores than our mechanisms.
-This means that they are flawed in some way, either in the accuracy of their grades, or the amount of work that one person has to do.
+In comparison with more traditional methods of peer grading, our mechanisms performed extremely well, aside from the Improved Calibration Mechanism.
+\emph{See Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} for a graphical representation of this}.
+As can be seen in this figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms.
+This means that traditional methods result in undesirable outcomes, either inaccurate or requiring a disproportionate amount of work.
 
@@
 \section{Conclusion}
-In this research, we learned and established the validity of game theory and mathematically based models when solving complex problems involving human nature.
-Using this to answer the unanswered of how professors should go about grading the astronomically high number of papers submitted by students in the online courses known as MOOCs.
 
-Theoretically, all of our results are perfectly valid, however one must acknowledge that theory is not practice.
-Because of this, it becomes hard to say how valid our results are, since they have not been tested in the real world.
-In the real world, there is always the chance that theory falls apart; this is the main flaw in the validity of our results.
+In this research, several novel game-theory-based mechanisms are proposed to enable a class to grade itself.
+As there are astronomically high numbers of students in the online courses today, our solution is poised to solve the issue of grading such a large volume of assignments created in these course.
+Several solutions to this have been proposed, including the use of automated essay grading or multiple choice.
+However, the usability of automated grading is under heavy debate.
+Multiple choice lacks the flexibility of questions that require open-ended responses.
+To the best of our knowledge, our solution is the first solution of its kind, based on mechanism design and game theory.
 
-Also, the only other flaw, which is minor in comparison, is that the mechanisms do not account for a perfectly realistic world.
-Even though we completed a model which can be built upon, and applies to the real world, the mechanisms designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.
+We began our research by creating a model and a set of assumptions to mathematically express the problem, along with a benchmark to quantitatively measure the effectiveness and the scalability of various mechanisms.
+At first, the assumptions were unrealistic and relatively simple.
+By starting with simple mechanisms and gradually adding more realistic assumptions, we were able to design increasingly realistic mechanisms.
+The three we created were the Calibration, Improved Calibration, and Deduction mechanisms.
+Currently, the Deduction Mechanism performs relatively well in the benchmark, with reasonably realistic assumptions.
 
-Although there are some errors in the validity of our results, all of them were established and created independent of any prior literature.
-One of the main advantages of this research is that it has not been done before; this is what makes it an interesting idea to explore and develop upon.
-Because of this, there is no prior literature that addresses the problem at hand in the same way that we do.
+The benchmark comes in terms of a function that takes into account the happiness the students and the professor, as well as the accuracy of grades of a given mechanism.
+The scalability of a given mechanism can also be assessed by the objective function, as a class size grows.
 
-In the future, one of the experiments that would truly confirm the validity of our results would be to test them in the real world.
-With real world testing in a system where assignments need to be graded, it would quickly become apparent whether the theory behind our mechanisms actually works, and how well it works in the real world.
-This would fix the first of the validity errors that the mechanisms have.
+Although our results are not perfectly valid, all of them were established and created independent of any prior literature.
+The area of study is intriguing and complex, and the methods we developed are creative and innovative; to the best of our knowledge, no prior literature addresses the problem at hand in the same way that we do.
+As human behavior is very complex, a full list of realistic assumptions is hard to create.
+Mechanisms designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.
+If we were to start the work today, we would start with slightly more realistic assumptions to build more realistic mechanisms from the beginning.
+There is always the chance that theory falls apart in reality; this is the main shortcoming of our results.
 
-To address the second of these validity errors, more work would need to be done to make the models realistic.
-If we had more time, this would be the first thing that we would do; creating a mechanism that applies to a more realistic world would ready the theory for real testing, and would also patch the second hole in the validity of the mechanisms.
+There still remains the question of how valid our theories are in practice.
+In the future, one of the experiments that would truly confirm the validity of our results would occur in the reality.
+Any flaws behind our mechanisms would quickly become apparent, through feedback received in classroom or online testing.
+If we had more time, we would build a better, less-harsh mechanism based the Deduction Mechanism and on our final assumptions, and use that to perform tests on.
+After finalization, we would begin some level of real world testing.
+A logical next step is to extend an existing course system or classroom environment, allowing further improvement upon our work.
 
-After finalizing the mechanisms, our preferred next step would be to implement software in an existing course system, and use it to test out our ideas.
-By implementing this, it would allow us to use what already exists and build upon it.
-This means that not much would have to be done to encourage people to use it, since they would already be using whatever we implemented it on.
-Also, this would allow us to receive real data for the theory, and using this we could continue the improvement cycle.
-
-Even though the mechanisms are not truly valid, only one true question remains unanswered.
-This question being the question of what happens when our theory is introduced into the real world.
-As stated previously, to solve this question, we would prefer to create a system of implementation that would allows us to test our mechanisms.
 \newpage

### 2013-09-25 Primes Write up.tex
Minor edits to make more sense

@@
 \section{Introduction}
-Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole.
+Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses) and their importance to education as a whole.
 Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}.
-However, the MOOC's main importance comes from its scalability.
+However, the main importance of MOOCs come from their scalability.
 MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}.
@@
 multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}.
-Even though automated grading for written essays is an active area of research with much recent progress, but the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}.
+Even though automated grading for written essays is an active area of research with much recent progress, the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}.
 On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}.
@@
 There have been many attempts at solving such an important problem~\cite{autograding}~\cite{edxsoftware}.
-However, this work introduces what previous attempts lack: a rigorous mathematical analysis of the system using tools from game theory and mechanism design.
-This work sets a concrete set of constraints that a grading system must satisfy to mitigate students' incentive to cheat, as well as a concrete benchmark to analyze the efficiency of various systems.
-Together, these create a concrete measure for evaluating peer grading systems in terms of efficiency (how much time the professor and students spend grading) and fairness for the students (how accurate their final scores are).
+However, our work introduces what previous attempts lack: a rigorous mathematical analysis of the system using tools from game theory and mechanism design.
+This work sets a concrete set of constraints that a grading system must satisfy to mitigate students' incentive to cheat, as well as a definitive benchmark to analyze the efficiency of various systems.
+Together, these create a measure for evaluating peer grading systems in terms of efficiency (how much time the professor and students spend grading) and fairness for the students (how accurate their final scores are).
 Having this measurement model is a large contribution in itself, because it allows comparison between different systems.
@@
 Mechanisms that do not follow game theoretic constraints may work in the short-term, but they will be exploited if possible in the long term~\cite{boycottfinal}.
-%[Note from Matt and Christos: 1) mention that coming up with a model is itself a big contribution, because now we can compare the quality of two different mechanisms.
-2) Mention that certainly theory is not a perfect predictor of what will happen in practice, but that game theory and mechanism design (and all the assumptions used in this work) have a history of ``calling good mechanisms good and bad mechanisms bad''.
-Also, solutions that do not satisfy game theoretic constraints may work for a while, but in the long run if a system can be exploited, eventually it will be.
-See here for an interesting example of this: http://www.insidehighered.com/news/2013/02/12/students-boycott-final-challenge-professors-grading-policy-and-get]
 
-Game theory allows the creation of a unified system of assumptions that simulate student behavior in a class.
+Game theory allows for the creation of a unified system of assumptions that simulate student behavior in a class.
 The grading system can be viewed as a ``game'' where the set of ``rules'' are known to everyone and the ``players'' --- the students --- ``play'' the game in order to get the best possible result.
-Using the assumptions and rules, game theory can predict how students will behave when they ``play''.
-This way, mechanism efficiency and effectiveness can be proved, allowing the evaluation of different sets of rules.
+Using assumptions and rules, game theory can predict how students will behave when they ``play''.
+This way, mechanism efficiency and effectiveness can be proved, allowing for comparison between different sets of rules.
 
-The difficulty of the problem lies in finding an incentive for students to spend time to grade assignments of others who they do not care about.
+The difficulty of the problem lies in finding an incentive to encourage students to spend time grading the assignments of others.
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
@@
 
-This research topic is made interesting by the complexity of human nature as well as its huge practical value.
+This research topic is also made interesting by the complexity of human nature, along with its huge practical value.
 This paper will cover the thought process of mechanisms leading up to the final mechanism and its implications.
@@
 This is the score the professor would give out.
-Our mechanism then has the students grade the papers in a clever way and output the grades.
+Our mechanism then has the students grade the papers in a clever way, with the grades given out being the functions output.
 We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
@@
 The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side.
-To begin with, we create a simple set of assumptions:
+To begin with, we create this set of assumptions:
 \begin{enumerate}[itemsep=0pt, parsep=0pt]
@@
 \end{enumerate}
-To re-express the above in mathematics:
+To re-express the above in mathematical terms:
 \begin{enumerate}[itemsep=0pt, parsep=0pt]
@@
 
-There are two things that need to be considered: the importance of a student's own happiness and the irrelevance of others' grades.
+There are two things that need to be considered: the importance of a student's own happiness and the irrelevance of the grades of a given student's friends.
 Happiness is important because it provides a measure of the combination of the work performed and grade received.
@@
 In the improvement process, we gradually refine our assumptions to better represent reality.
-This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex yet more realistic situations.
+This means that the original set of assumptions we proposed will change throughout the course of the paper to allow mechanisms to handle more complex and more realistic situations.
 
@@
 The maximum grade deviation is also $k$, for $m > H^{-1}(k)$.
-Therefore, the benchmark $max(k, \frac{n}{k}) + k$, a potentially higher value than before.
+Therefore, the benchmark is $max(k, \frac{n}{k}) + k$, a potentially higher value than before.
 The huge problem with this is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$.
+With a large number of people in a class, this number becomes massive.
 We can see that the benchmark becomes $2\sqrt{n}$.
@@
 
-In this research, several novel game-theory-based mechanisms are proposed to enable a class to grade itself.
+In this research, several novel game-theory based mechanisms are proposed to enable a class to grade itself.
 As there are astronomically high numbers of students in the online courses today, our solution is poised to solve the issue of grading such a large volume of assignments created in these course.

### 2013-09-26 Primes Write up.tex
Added Frans' changes/recommendations

@@
 Even though automated grading for written essays is an active area of research with much recent progress, the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}.
-On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}.
-Although both of these systems are interesting concepts, they are limiting or inaccurate in practice~\cite{howaccurateispeergrading}.
+On the other hand, peer grading can grade any type of question, a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}.
+These limitations render the students unable to effectively evaluate the mastery of the course material.
 
-The problem of grading large numbers of submissions is important to solve.
-Without a solid solution, MOOCs cannot provide efficient feedback for students taking them.
-This renders the students unable to effectively evaluate the mastery of the course material.
-Therefore, it is imperative to create an efficient system that enables students to receive feedback to learn effectively.
-
-There have been many attempts at solving such an important problem~\cite{autograding}~\cite{edxsoftware}.
-However, our work introduces what previous attempts lack: a rigorous mathematical analysis of the system using tools from game theory and mechanism design.
-This work sets a concrete set of constraints that a grading system must satisfy to mitigate students' incentive to cheat, as well as a definitive benchmark to analyze the efficiency of various systems.
+This work proposes several peer grading systems that provide students with an incentive not to hack the system using tools from game theory and mechanism design~\cite{AGTbook}.
+Our work introduces what previous attempts lack: a rigorous mathematical analysis of the system.
+It sets a concrete set of constraints that a grading system must satisfy to mitigate students' incentive to cheat, as well as a definitive benchmark to analyze the efficiency of various systems.
 Together, these create a measure for evaluating peer grading systems in terms of efficiency (how much time the professor and students spend grading) and fairness for the students (how accurate their final scores are).
@@
 Incentivizing students seems simple at first: let the professor give bonus points to students who grade, for example.
-However, this may not return anything useful because a clever student will just take the points and assign a generic grade (i.e.
-how can the professor tell the difference between an accurately assigned hundred and randomly awarded 100).
-The next step would be to implement simple checking: e.g.
-have each paper be graded by two students who both receive bonus points if their grades match.
+However, this choice may not return a useful result because a clever student will just take the points and assign a generic grade.
+The professor cannot tell the difference between an accurately assigned hundred and randomly awarded 100.
+The next step would be to implement simple checking.
+For example, have each paper be graded by two students who both receive bonus points if their grades match.
 This case may work if the students are isolated, but the professor still cannot tell the difference between a randomly or sincerely awarded grade.
@@
 To apply our solution to an entire class, simply apply it to each assignment separately.
-In such a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor.
-These ungraded papers are like the input for a function.
+In a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor.
+These ungraded papers are the input for a function.
 Each of these papers, $i$ has an objective score $o_i,~where~ 0\leq o_i \leq 100$.
@@
 	\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
-	\item Students can grade others' work accurately (i.e.
-they can find $o_i$) but doing so costs one unit of happiness.
+	\item Students can grade others' work accurately (i.e., they can find $o_i$) but doing so costs one unit of happiness.
 Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
 	\item Students want to maximize their final happiness, expressed as $H(g)-W$
-	\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
+	\item Students care only about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e., if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
 	\item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
@@
 
-There are two things that need to be considered: the importance of a student's own happiness and the irrelevance of the grades of a given student's friends.
+Two notes about the importance of a student's happiness and the irrelevance of the grades of a given student's friends.
 Happiness is important because it provides a measure of the combination of the work performed and grade received.
@@
 The goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment they are given to grade.
-Without this property, a system becomes extremely unpredictable.
+Without this property, a system becomes unpredictable.
 In other words, no student can deviate from the desired behavior to improve his or her happiness.
@@
 In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
-This benchmarking function is known as the \emph{Objective function}, which we will reference in our research.
+This benchmarking function is known as the \emph{Objective function}, which we use in our research.
 
-When creating this benchmark, there are 2 things that need to be considered: accuracy and workload.
+When creating this benchmark, there are two metrics that must be considered: accuracy and workload.
 Accuracy is important because if we do not care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism.
@@
 In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done.
-The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is the following.
-Consider these two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade.
+The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is as follows.
+Consider the following two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade.
 Note that the grade the student receives at the end is not necessarily that given by their peers.
+Case 1 is as follows:
 \begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
@@
 \end{enumerate}
-Clearly, case A is better than case B. The smaller maximum deviation for case A reflects this.
-For the maximum work done, consider the the following cases:
+Clearly, outcome A is better than outcome B. The smaller maximum deviation for outcome A reflects this.
+For the maximum work done, consider the the following case:
 \begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
@@
 \end{enumerate}
-This time, case B is intuitively better than case A. Again, the benchmark captures our intuition.
+This time, outcome B is intuitively better than outcome A. Again, the benchmark captures our intuition.
 
@@
 
-Now that we have created a simple set of assumptions and a benchmark, we can create several simple mechanisms, and improve upon them until we are satisfied with a final mechanism.
+Now that we have created a simple set of assumptions and a benchmark, we can create several mechanisms, and improve upon them until we are satisfied with a final mechanism.
 In the improvement process, we gradually refine our assumptions to better represent reality.
@@
 \subsubsection{Process}
-First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
+First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we use as a starting point.
 One idea is to have the professor choose one paper that he grades.
@@
 \subsubsection{Benchmark and Remaining Issues}
-We now show that the Calibration Mechanism achieves a very low value in our benchmark.
+We now show that the Calibration Mechanism achieves a low value in our benchmark.
 \begin{theorem}
@@
 \begin{proof}
-In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other.
+In this scheme, because of the overlapping papers, the students have no better way of determining which papers are calibrated than random guessing, even though they can all communicate with each other.
 As such, there are 3 options for the students.
@@
 Therefore, the benchmark is $max(k, \frac{n}{k}) + k$, a potentially higher value than before.
-The huge problem with this is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$.
+A downside of the Improved Calibration Mechanism is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$.
 With a large number of people in a class, this number becomes massive.
@@
 In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper.
-This means that no papers will ever reach the professor, so he or she will not have to grade anything.
+This means that no papers will ever reach the professor, so he or she will not have to grade any papers.
 Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades.
 This means that the final benchmark is $2+0=2$.
-This is the lowest out of all the mechanisms so far.
+This is the lowest score out of all the mechanisms so far.
 \subsection{Final Assumptions}
-Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view.
+Now we have a model that accounts for a realistic world view.
 However, the Deduction Mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders.
@@
 \end{enumerate}
+\subsection{Comparison}
+Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} shows a comparison between our mechanisms and those currently in use.
+As you can see, our mechanisms performs better than the others, aside from the Improved Calibration Mechanism.
+As can be seen in the figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms.
+This means that traditional methods result in undesirable outcomes, either inaccurate or requiring a disproportionate amount of work.
+
+This comparison clearly shows that the mechanisms we created are more efficient than any currently employed in modern classrooms.
 \newpage
@@
 
-By creating a mechanism that is, in theory, more efficient than both current peer grading systems and automated grading systems, it has been shown that there is still room for improvement in the grading of online courses.
-By showing this, a renewed interest in the field can be created, which could lead to others developing more mechanisms that will improve the general education of students in these courses.
-As the ultimate goal of this research is to accomplish this, the idea that the mechanisms not only accomplish this, but also open the road for others to do so is a marked success.
-
-With the final mechanism, all of the goals that were set up were accomplished, with only total realism absent from the design.
-With this final mechanism, it has been shown that it is possible to create a mathematically driven and effective design that can solve a problem that needs to be solved.
-Not only is this something that has not been done before, but it opens the way for others to build upon this work, something that could eventually lead to the creation of a perfect solution.
-
 However important the creation of these mechanisms is, arguably more important to the future development of further solutions is the creation of a realistic and robust model.
@@
 
-Due to the numerous possibilities the creation of a model and benchmark can lead to future research, it is clear that they are the most important results gained from this research.
-Without them, nothing else could have been done, and no future mechanisms could be created that would be able to be analyzed in the same way that these were.
-Due to the importance of future research in this field, it was imperative that this research led to more solutions in the future, so that the problem that was identified would be quickly and efficiently solved.
-
-Although the models presented by this research are not completely realistic, they do show that there is much room for improvement in the area of grading online courses, and that it is possible to take a strictly mathematical approach at designing a mechanism, and then implementing it using computer science.
-By showing that this is possible, a huge amount of potential for future research has been opened, primarily due to the creation of a benchmark and model.
-With these tools, other game theorists can create their own mechanisms, and compare them to those of others around the world.
-
 Aside from improving previous research done in this field, this research also supports the idea that many others have proposed: that peer grading is more efficient than automated grading.
@@
 For this reason, systems such as Coursera have yet to adopt this, and instead default to peer grading.
-As many people suspected, and as this research confirms, peer grading can indeed be more efficient than automated grading when implemented correctly, simply because the A.I.
-of current machines cannot handle the many different ways a student can answer an open ended question.
+As many people suspected, and as this research confirms, peer grading can indeed be more efficient than automated grading when implemented correctly, simply because the artificial intelligence present in current machines cannot handle the many different ways a student can answer an open ended question.
 
@@
 This shows that with a change in assumptions, a new mechanism must be created to address the change, as old mechanisms will often perform badly in new models.
-
-In comparison with more traditional methods of peer grading, our mechanisms performed extremely well, aside from the Improved Calibration Mechanism.
-\emph{See Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} for a graphical representation of this}.
-As can be seen in this figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms.
-This means that traditional methods result in undesirable outcomes, either inaccurate or requiring a disproportionate amount of work.
-
-With this comparison, it can be clearly seen that the mechanisms created with this research are more efficient than any currently employed in modern classrooms.
 
@@
 After finalization, we would begin some level of real world testing.
-A logical next step is to extend an existing course system or classroom environment, allowing further improvement upon our work.
+A logical next step is to extend an existing course system or classroom environment to test our ideas.
 

### 2013-09-26 Primes Write up.tex
Revised Discussion

@@
 Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} shows a comparison between our mechanisms and those currently in use.
-As you can see, our mechanisms performs better than the others, aside from the Improved Calibration Mechanism.
+As shown, our mechanisms performs better than the others, aside from the Improved Calibration Mechanism.
 As can be seen in the figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms.
@@
 
-Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students.
-In current peer grading schemes, it is easy for students to just ``game'' the system and fake their way through a course.
-Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}.
-This allows students to dishonestly grade the work of others, as well as just give whomever they want a better grade than that person actually deserves.
-In our mechanisms, however, these problems are solved by removing anonymity and adding incentives to make students behave honestly, no matter who they are grading.
+Traditional peer-grading schemes are prone to student manipulation: one of the issues our approach mitigates.
+Because such systems make grade feedback anonymous, students can easily get away with dishonestly or inadequately grading the work of others for their own benefit.
+Anonymity not encourage students to be honest; it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}.
+The removal of anonymity and the application of incentives in our methods encourage positive student behavior.
 
-Aside from fixing many problems that students have with other peer grading systems, our mechanisms also address the unhappiness and inconsistency caused by the grading given out by machines.
-One key problem that machines have is that they always look at the same thing in a paper, meaning that they can be easily ``gamed''and fooled into thinking something is better than it acutely is~\cite{robogradingproblems}.
-Not only does this make the system inconsistent, but any student who is lacking something that is in the list of requirements the machine checks for can be unfairly given a poor grade, making them unhappy.
-By solving both of these problems with the mechanisms that were created, it has been demonstrated the peer grading, at least for the moment, is better for education that automated grading.
+Machine grading systems are known to cause unhappiness and inconsistency: one of the problems our approach addresses.
+Because machines always look for the same things in each paper, students who know the criteria can fool the system~\cite{robogradingproblems}, yielding inconsistent grades.
+Conversely, the machine may fail to recognize alternative wordings or conceptual definitions, leading to inaccurate grades and unhappy students.
+The mechanisms we have created solves both these issues by using humans instead of machines.
 
-Not only do the mechanisms developed in this research improve upon the efficiency of automated grading systems, but they also help to remove the dominance that automated grading has placed on grading large courses.
-By providing a system that fixes many of the problems with current automated grading systems, these mechanisms help to show that automated grading is not the only way to solve the problem of grading online courses.
-Because automated grading, at the moment, is not as efficient and robust as it needs to be to prevent students from creating unfair situations, this is something that is necessary to show because automated grading is simply not good enough with today's technology.
+Not only do the mechanisms developed in this research improve upon the efficiency of traditional automated and peer grading systems, but the mechanisms also fix many problems inherent in such methods.
+These mechanisms shed light on the alternatives to automated grading, which are more efficient and lack issues inherent in computational grading.
+At the moment, automated grading is not as efficient and robust as it needs to be to prevent students from creating unfair situations.
 
-However important the creation of these mechanisms is, arguably more important to the future development of further solutions is the creation of a realistic and robust model.
-Without a model, many of the mechanisms mentioned would have been impossible to create, and would certainly not work as well as they do.
+The importance of a realistic and robust model --- as well as effective mechanisms --- cannot be overstated.
 The creation of a model is essential in game theory as it provides the outline for how the ``players''of a given game will act under any set of circumstances.
+Many of the mechanisms mentioned would be impossible to create without a model.
+A well-defined model can easily be re-used and extended by others.
 As such, by creating a good model, this research has undergone the trouble of providing a way for anyone to predict how students will behave.
-
-Not only did this research lead to the creation of a good model, but it also led to the creation of a benchmark.
-The creation of a benchmark is important because it allows two mechanisms to be compared side by side, and it allows theorists to definitively determine which of these mechanisms is superior.
-With this, it becomes possible to compare the results of this research to the results of others, and also allows future work to be done by others.
-Not only does a benchmark allow the research done here to be compared to that of others, but it allows two totally independent mechanisms not derived from this research to be compared, which could lead to a universal system of evaluating peer grading systems.
-
-Both of these are major contributions towards further developments in the field of research this problem takes place in, primarily game theory.
-By doing so, grading mechanisms across online courses will constantly be able to evolve and improve with contributions from anyone.
-By creating the benchmark and model, all mechanisms will undergo a uniform set of evaluations that will allow online course systems to determine which system is the best out of any proposals.
-By doing so, this research has opened up a road for many game theorists to develop and analyze new ideas that will lead to improvements in student happiness and results from online courses.
 

### 2013-09-26 Abstract.tex
Create Abstract.tex

\documentclass[12pt, Arial]{article}
\title{Executive Summary}
\author{How to Teach a Class to Grade Itself Using Game Theory}
\begin{document}
\maketitle
This research project focuses on the development of a novel and efficient peer grading system for online courses by Coursera or EDx. In such courses, the amount of students can be enormous. To grade the number of assignments produced, multiple choice tests and automated grading systems have been employed, but these run into limitations when grading open-ended responses such as essays. The underlying complexity of peer grading arises from the nature of human behavior. Our approach to this problem utilizes game theory and mechanism design --- a first of its kind to our knowledge. Our research proposes three mechanisms, each with more realism than the previous. To compare mechanisms, we defined a benchmark based on the accuracy of grades and workload of student and professor. Using this benchmark, the final mechanism we created surpasses both traditional peer grading and automated grading methods.  Our work facilitates and standardizes future work for peer grading and mechanism development, ultimately improving the quality of online education.
\end{document}

### 2013-09-26 Real Abstract.tex
Create Real Abstract.tex
Oops. The previous Abstract.tex was really the exec. summary.

\documentclass[12pt, Arial]{article}
\title{Abstract}
\author{How to Teach a Class to Grade Itself Using Game Theory}
\begin{document}
\maketitle
An efficient peer grading mechanism is proposed for grading the multitude of assignments in online courses. This novel approach is based on game theory and mechanism design. A set of assumptions and a mathematical model is ratified to simulate the dominant strategy behavior of students in a given mechanism. A benchmark function accounting for grade accuracy and workload is established to quantitatively compare effectiveness and scalability of various mechanisms. After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration and Deduction. The Deduction mechanism performs relatively well in the benchmark, outperforming traditional automated and peer grading systems. The mathematical model and benchmark opens the way for future derivative works to be performed and compared.
\end{document}

### 2013-09-26 Abstract.tex
Updated and compiled Abstract + ES

@@
 \documentclass[12pt, Arial]{article}
-\title{Executive Summary}
+\title{Abstract}
 \author{How to Teach a Class to Grade Itself Using Game Theory}
+\date{}
 \begin{document}
 \maketitle
-This research project focuses on the development of a novel and efficient peer grading system for online courses by Coursera or EDx.
-In such courses, the amount of students can be enormous.
-To grade the number of assignments produced, multiple choice tests and automated grading systems have been employed, but these run into limitations when grading open-ended responses such as essays.
-The underlying complexity of peer grading arises from the nature of human behavior.
-Our approach to this problem utilizes game theory and mechanism design --- a first of its kind to our knowledge.
-Our research proposes three mechanisms, each with more realism than the previous.
-To compare mechanisms, we defined a benchmark based on the accuracy of grades and workload of student and professor.
-Using this benchmark, the final mechanism we created surpasses both traditional peer grading and automated grading methods.
-Our work facilitates and standardizes future work for peer grading and mechanism development, ultimately improving the quality of online education.
+An efficient peer grading mechanism is proposed for grading the multitude of assignments in online courses.
+This novel approach is based on game theory and mechanism design.
+A set of assumptions and a mathematical model is ratified to simulate the dominant strategy behavior of students in a given mechanism.
+A benchmark function accounting for grade accuracy and workload is established to quantitatively compare effectiveness and scalability of various mechanisms.
+After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration and Deduction.
+The Deduction mechanism performs relatively well in the benchmark, outperforming traditional automated and peer grading systems.
+The mathematical model and benchmark opens the way for future derivative works to be performed and compared.
 \end{document}

### 2013-09-26 Executive Summary.tex
Updated and compiled Abstract + ES

\documentclass[12pt, Arial]{article}
\title{Executive Summary}
\author{How to Teach a Class to Grade Itself Using Game Theory}
\date{}
\begin{document}
\maketitle
This research project focuses on the development of a novel and efficient peer grading system for online courses by Coursera or EDx. In such courses, the amount of students can be enormous. To grade the number of assignments produced, multiple choice tests and automated grading systems have been employed, but these run into limitations when grading open-ended responses such as essays. The underlying complexity of peer grading arises from the nature of human behavior. Our approach to this problem utilizes game theory and mechanism design --- a first of its kind to our knowledge. Our research proposes three mechanisms, each with more realism than the previous. To compare mechanisms, we defined a benchmark based on the accuracy of grades and workload of student and professor. Using this benchmark, the final mechanism we created surpasses both traditional peer grading and automated grading methods.  Our work facilitates and standardizes future work for peer grading and mechanism development, ultimately improving the quality of online education.
\end{document}

### 2013-09-26 Primes Write up.tex
Final Changes

@@
 However, the main importance of MOOCs come from their scalability.
-MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}.
+MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: by the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}.
 The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.
@@
 Professors are simply unable to grade hundreds of thousands of submissions.
-Currently, two types of solutions are used to remedy the problem: automated grading and peer grading.
+Currently, two types of solutions are used to remedy the problem: automated grading and peer grading~\cite{edxsoftware}.
 Automated grading relies on machines to grade assignments.
@@
 However, this choice may not return a useful result because a clever student will just take the points and assign a generic grade.
-The professor cannot tell the difference between an accurately assigned hundred and randomly awarded 100.
+The professor cannot tell the difference between an accurately assigned 100 and randomly awarded 100.
 The next step would be to implement simple checking.
 For example, have each paper be graded by two students who both receive bonus points if their grades match.
-This case may work if the students are isolated, but the professor still cannot tell the difference between a randomly or sincerely awarded grade.
-This way, their papers will match those of other clever students, giving them points without grading.
+This may work at first, but clever students will learn over time to coordinate, assign everyone the same grade without doing any work, and pick up the bonus points (again, the professor cannot tell the difference between a randomly or sincerely assigned grade).
 These examples show that properly incentivizing graders can be a difficult task.
@@
 These ungraded papers are the input for a function.
-Each of these papers, $i$ has an objective score $o_i,~where~ 0\leq o_i \leq 100$.
+Each of these papers, $i$ has an objective score $o_i$ where $0\leq o_i \leq 100$.
 This is the score the professor would give out.
@@
 \subsection{Assumptions}
-To create the models that are used to predict the behavior of the students, we use a set process every time.
+To create the models that we use to predict the behavior of the students, we use a set process every time.
 To begin with, we create a set of assumptions.
@@
 This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model.
-The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side.
+The same set of assumptions can be used for multiple mechanisms, which will allow us to evaluate different mechanisms side by side.
 To begin with, we create this set of assumptions:
@@
 	\item Students want to maximize their final happiness, expressed as $H(g)-W$
-	\item Students care only about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e., if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
+	\item Students care only about the expectation of their final happiness, which, put in game theoretical terms, makes them risk neutral (i.e., if $H(x)=10$ and $H(y)=5$, then getting $x$ and $y$ each with $50$ percent chance, gives a happiness of $7.5$).
 	\item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It does not depend on the score of others
@@
 
+Do these mathematical assumptions perfectly capture human behavior?
+Of course not.
+But these assumptions are certainly a meaningful simplification of student behavior, and one should expect mechanisms that are provably good under these assumptions to be pretty good in practice as well.
 \subsection{Objective}
@@
 A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development.
-Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced.
+Mechanisms should be compared in terms of the amount of work done by a person as well as the accuracy of the grades produced.
 Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desirable outcome.
-In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.
-This benchmarking function is known as the \emph{Objective function}, which we use in our research.
+In mathematical terms, we want to minimize the function $\max_{i \ge 1} \{|H(g_i)-H(o_i)|\} + \max_{i \ge 0} \{w_i\}$ in the worst possible case.
+We call our benchmarking function the \emph{Objective function}, which we use in our research.
 
@@
 In our case, we use the \emph{maximum} deviation and the \emph{maximum} work done.
-The reason why we do not use the\emph{sum} of the deviations or the \emph{sum} of work done is as follows.
+The reason why we do not use the \emph{sum} of the deviations or the \emph{sum} of work done is as follows.
 Consider the following two cases for the maximum deviation of the grade assigned by the mechanism to the hypothetical professor-given grade.
@@
 Case 1 is as follows:
-\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
+\begin{enumerate}[label=\Alph*]
 	\item Each of 1000 students should receive a 90, but the mechanism assigned a 91 to each of them. Maximum deviation is 1, sum is 1000.
@@
 For the maximum work done, consider the the following case:
-\begin{enumerate}[label=\Alph*, itemsep=0pt, parsep=0pt]
+\begin{enumerate}[label=\Alph*]
 	\item The professor grades 1000 papers. Maximum work is 1000, sum is 1000.
@@
 Then, game theory is used to mathematically predict student behavior to benchmark such a system.
-Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months.
+Starting from the simplest and most obvious approaches, we created, tested, and refined upon various mechanisms in an iterative process that spanned several months.
 The end result is fairly complete, although there are still questions to be answered in future work.
@@
 \subsubsection{Process}
-First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we use as a starting point.
+First, we design a mechanism that does extremely well in a model defined by our simple assumptions, which we use as a starting point.
 One idea is to have the professor choose one paper that he grades.
@@
 To cope with this, we pick some minimum grade $m > 0$ and promise every student that they will receive a grade of at least $m$ if they grade the assignment correctly.
-By appropriately choosing a value for $m$, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.
+By appropriately choosing a value for $m$, all students should behave honestly and the mechanism should output accurate grades while maintaining a low amount of per-person work.\\
 \begin{definition}(Calibration Mechanism)
@@
 If the student fails to grade $P$, he or she gets a zero.
-Otherwise, the student gets the maximum of some minimum value and his or her assigned grade.
+Otherwise, the student gets the maximum of $m$ and his or her assigned grade.
 \end{definition}
+\medskip
 \begin{theorem}
-If $m>H^{-1}(2)$, it will be in every student's best interest to grade both papers in the Calibration Mechanism.
+If $m \geq H^{-1}(2)$, it will be in every student's best interest to grade both papers in the Calibration Mechanism.
 \end{theorem}
@@
 \subsubsection{Benchmark and Remaining Issues}
-We now show that the Calibration Mechanism achieves a low value in our benchmark.
+We now show that the Calibration Mechanism achieves a low value in our benchmark.\\
 \begin{theorem}
@@
 Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
-So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
+So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2. This means that the sum is $2+2=4$
 \end{proof}
@@
 In the calibration mechanism, we assumed that students could not communicate with each other, and therefore could not figure out which of the two papers they were asked to grade was calibrated.
-For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.
+For this mechanism, we relax this assumption and instead provide a mechanism that works even if each student can communicate with all other students.\\
 \begin{definition}(Improved Calibration Mechanism)
@@
 \end{definition}
+\medskip
 \begin{theorem}
-In this mechanism, students will return accurate grades, even though they can communicate with each other.
+In this mechanism, students will return accurate grades as long as $m \geq H^{-1}(k)$, even though they can communicate with each other.
 \end{theorem}
@@
 As such, there are 3 options for the students.
-They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$.
+They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(G) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$.
 This means that it is always worse to grade $i$, because happiness from grading $i$ is equal to $i$ times happiness for grading 0 plus $i-k$ times happiness for grading $k$.
@@
 Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers.
-As long as $m > H^{-1}(k)$, the papers will be accurately graded, as before.
+As long as $m \geq H^{-1}(k)$, the papers will be accurately graded, as before.
 
@@
 \subsubsection{Benchmark and Remaining Issues}
+We now show that the Improved Calibration Mechanism receives a higher benchmark than the calibration mechanism.\\
+\begin{theorem}
+The Improved Calibration Mechanism achieves a benchmark score of $2\sqrt{n}$.
+\end{theorem}
 The amount of work done by the professor is $\frac{n}{k}$.
 For the students, this number is $k$.
-The maximum grade deviation is also $k$, for $m > H^{-1}(k)$.
-Therefore, the benchmark is $max(k, \frac{n}{k}) + k$, a potentially higher value than before.
+The maximum grade deviation is also $k$, for $m \geq H^{-1}(k)$.
+Therefore, the benchmark is $\max\{k, \frac{n}{k}\} + k$, a potentially higher value than before.
 A downside of the Improved Calibration Mechanism is the high amount of work being done, choosing the optimal value for $k$, which is $\sqrt{n}$.
@@
 For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, student $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and $j$ receives $\frac{x_j}{x_i + x_j}$.
+If $x_i = x_j = 0$ both contribution scores are $\frac{1}{2}$.
 Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives the incorrect grader(s) a 0.
-To compute the final score for a student, the final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$.
+To compute the final score for a student, the final grade on the assignment is calculated as follows: 2 points times their contribution score are added to $H(g)$.
 (Then the student's grade is converted from Happiness to an actual score).
 \end{definition}
+\medskip
 \begin{theorem}
-The addition of the contribution score being added or subtracted should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
+The addition of the contribution score being added encourages graders to honestly grade papers.
 \end{theorem}
@@
 If the student's partner gives the paper a 100, which is the best thing they could do if they do not grade, then
-	If they do not grade the paper, they do not use any effort, and their contribution score is 0. So the student's happiness will $H(g) + 4*0 = H(g)$.
+	if the student does not grade the paper, they do not use any effort, and their contribution score is $\frac{1}{2}$. So the student's happiness will $H(g) + 2\cdot0.5 = H(g)+1$.
 
-If the student grades, he or she uses 1 unit of effort by default, but get the full contribution score of 1. This means that their final happiness is $H(g) + 4\cdot1 - 1 = H(g)+3$.
+If the student grades, he or she uses 1 unit of effort by default, but will get the full contribution score of 1. This means that their final happiness is $H(g) + 2\cdot1 - 1 = H(g)+1$.
 
 If the partner gives the paper its true grade:
-	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is $H(g) + 4\cdot(-1) = H(g)-4$.
+	If the grader does not grade the assignment, they will give it a 100 and so the grader's contribution score is 0. So their happiness is $H(g) + 2\cdot0 = H(g)$.
 
-If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is $H(g) + 4\cdot0 - 1 = H(g)-1$.
+If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is $H(g) + 2\cdot0.5 - 1 = H(g)$.
 
-In both of the above cases, the happiness outputs for honestly grading the paper is higher than the happiness output when not grading the paper.
-Our assumptions state that students will do whatever makes them happiest, so they will honestly grade the papers.
+In both of the above cases, the happiness output for honestly grading the paper is equal to the happiness output when not grading the paper.
+However, if we increase the 2 present in each equation by an infinitely small amount, the equalities become strict, and as our assumptions state that students will do whatever makes them happiest, so they will honestly grade the papers.
+For our purposes, because this new coefficient is greater than 2 by an infinitely small amount, we simply refer to it as 2.
 
@@
 \newline
-\emph{The benchmark results for the Calibration Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
+\emph{The benchmark results for the Deduction Mechanism can be seen in Figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}
 \subsubsection{Benchmark}
-In this model, the most work is being done by the students, who each grade 2 papers.
-In this mechanism, the professor will not perform any work, because students will adhere to the dominant strategy behavior, and honestly grade the paper.
-This means that no papers will ever reach the professor, so he or she will not have to grade any papers.
-Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 0, since every student will output accurate grades.
-This means that the final benchmark is $2+0=2$.
-This is the lowest score out of all the mechanisms so far.
+We now show that the Deduction Mechanism receives the lowest benchmark out of our three mechanisms.\\
+\begin{theorem}
+The Deduction Mechanism achieves a benchmark score of $4$.
+\end{theorem}
+In this mechanism, the most work is being done by the students, who each grade 2 papers, while the professor will not perform any work, because students will adhere to the dominant strategy behavior, honestly grading the papers.
+This means that no papers will ever reach the professor, so he or she will not have to grade any papers, making the most work done by any one person $2$.
+Also, because every student will follow dominant strategy behavior, the maximum deviation from the objective score will be 2, since every student will output accurate grades, but also get a bonus 2 points thanks to the reward.
+This means that the final benchmark is $2+2=4$.
 \subsection{Final Assumptions}
 Now we have a model that accounts for a realistic world view.
-However, the Deduction Mechanism still has some unrealistic parts, primarily the inability to deal with students who are incompetent graders.
+However, the Deduction Mechanism still has some unrealistic parts.
 To address this, we designed a final set of assumptions that more effectively simulate a realistic world.
@@
 \begin{enumerate}[itemsep=0pt, parsep=0pt]
-	\item When grading, $w_i=0 \oplus w_i=1$
+	\item When grading, either $w_i=0$ or $w_i=1$
 	\item For all students, $g_i \neq o_i$
@@
 	\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
-	\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
+	\item Students only care about the expectation of their final happiness, which, put in game theoretical terms, makes them risk neutral
 	\item For a given student in $N$, that student has contact with all other students in $N$
@@
 This problem, found in systems such as Coursera~\cite{howaccurateispeergrading}, is solved by our mechanisms by allowing the students to appeal their grades and to have multiple rounds of grading.
-Our mechanisms addresses other commonly expressed problems such as inconsistency of feedback by requiring a reason for every deduction made --- students must take the time to explain any deductions, or why they gave the paper a perfect score.
+Our mechanisms address other commonly expressed problems such as inconsistency of feedback by requiring a reason for every deduction made --- students must take the time to explain any deductions, or why they gave the paper a perfect score.
 
@@
 
-Human judgment has always been superior to that of a machine, and this research continues to support that idea.
-As powerful as automated grading can be in practice, when it comes to theory, peer grading is simply more efficient.
-This means that with the right mechanism, such as the ones proposed by this research, so, in practice peer grading should be superior to automated grading.
-This research has opened doors for game theorists to make improvements to current grading schemes, and also provides mechanisms that are a distinct improvement over current peer and automated grading systems.
-
 As our mechanisms evolve, the benchmark scores yielded by each tends to decrease.
@@
 We began our research by creating a model and a set of assumptions to mathematically express the problem, along with a benchmark to quantitatively measure the effectiveness and the scalability of various mechanisms.
-At first, the assumptions were unrealistic and relatively simple.
+At first, the assumptions were relatively simple.
 By starting with simple mechanisms and gradually adding more realistic assumptions, we were able to design increasingly realistic mechanisms.
@@
 
-Although our results are not perfectly valid, all of them were established and created independent of any prior literature.
 The area of study is intriguing and complex, and the methods we developed are creative and innovative; to the best of our knowledge, no prior literature addresses the problem at hand in the same way that we do.
-As human behavior is very complex, a full list of realistic assumptions is hard to create.
-Mechanisms designed around this model do not address the real world, since they lack the capacity to account for students who are incapable of grading well.
-If we were to start the work today, we would start with slightly more realistic assumptions to build more realistic mechanisms from the beginning.
-There is always the chance that theory falls apart in reality; this is the main shortcoming of our results.
+As human behavior is complex, a full list of realistic assumptions is hard to create.
 
@@
 Any flaws behind our mechanisms would quickly become apparent, through feedback received in classroom or online testing.
-If we had more time, we would build a better, less-harsh mechanism based the Deduction Mechanism and on our final assumptions, and use that to perform tests on.
 After finalization, we would begin some level of real world testing.

### 2014-05-14 Abstract.tex
Updated abstract, minor changes to Trifold

@@
 A benchmark function accounting for grade accuracy and workload is established to quantitatively compare effectiveness and scalability of various mechanisms.
-After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration and Deduction.
+After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration, and Deduction.
+The Calibration mechanism performs as predicted by game theory when tested in an online crowdsourced experiment.
 The Deduction mechanism performs relatively well in the benchmark, outperforming traditional automated and peer grading systems.

### 2014-12-30 Paper.tex
First nice draft

\documentclass{sigchi}

% Use this command to override the default ACM copyright statement (e.g. for preprints). 
% Consult the conference website for the camera-ready copyright statement.

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\toappear{Pending copyright...}

% Arabic page numbers for submission. 
% Remove this line to eliminate page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphicx} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{epstopdf}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={SIGCHI Conference Proceedings Format},
pdfauthor={LaTeX},
pdfkeywords={MOOC, game theory, mechanism design, peer grading, learning at scale},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{Game Theory based Peer Grading Mechanisms for MOOCs}

\numberofauthors{5}
\author{
  \alignauthor William Wu\\
    \affaddr{Acton Boxborough Regional High School}\\
    \affaddr{36 Charter Rd Acton, MA 01720, USA}\\
    \email{willy.vvu@gmail.com}
  \alignauthor Nicolaas Kaashoek\\
    \affaddr{Lexington High School}\\
    \affaddr{251 Waltham Street, Lexington, MA 02421, USA}\\
    \email{nick.kaashoek@gmail.com}
}

\maketitle

\begin{abstract}
An efficient peer grading mechanism is proposed for grading the multitude of assignments in online courses. This novel approach is based on game theory and mechanism design. A set of assumptions and a mathematical model is ratified to simulate the dominant strategy behavior of students in a given mechanism. A benchmark function accounting for grade accuracy and workload is established to quantitatively compare effectiveness and scalability of various mechanisms. After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration, and Deduction. The Calibration mechanism performs as predicted by game theory when tested in an online crowdsourced experiment. The Deduction mechanism performs relatively well in the benchmark, outperforming traditional automated and peer grading systems. The mathematical model and benchmark opens the way for future derivative works to be performed and compared.
\end{abstract}

\keywords{
	MOOC; game theory; mechanism design; peer grading; learning at scale;
}

\category{K.3.m.}{Computers and Education}{Miscellaneous}

\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses) and their importance to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canMOOCsreducecc}. However, the main importance of MOOCs come from their scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofMOOCs}: by the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofMOOCs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are simply unable to grade hundreds of thousands of submissions. Currently, two types of solutions are used to remedy the problem: automated grading and peer grading~\cite{edxsoftware}. Automated grading relies on machines to grade assignments. Machines can only check certain types of answers (i.e. multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongMOOCs}. Even though automated grading for written essays is an active area of research with much recent progress, the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}. Students who know the machine's grading criteria can fool the system~\cite{robogradingproblems}, yielding inconsistent grades.  On the other hand, peer grading can grade any type of question, a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofMOOCs}. Additionally, lack of feedback from peer grading is an area of complaint in systems such as Coursera~\cite{howaccurateispeergrading}. These limitations render the students unable to effectively evaluate the mastery of the course material.

We propose several peer grading mechanisms based on game theory and our student model - a set of assumptions we believe students abide by. We also create a benchmark to compare between our and existing mechanisms. Although a theoretical model cannot predict exactly what will happen in practice, game theory and mechanism design have a history of generally determining mechanisms that work in practice from ones that do not~\cite{AGTbook}. Mechanisms that do not follow game theoretic constraints may work in the short-term, but they will be exploited if possible in the long term~\cite{boycottfinal}.

\section{Model and Assumptions}
Our student model consists of assumptions we believed students abide by, as follows:
\begin{enumerate}
  \item Let H be a function of a student's grade, returning a student's happiness, such that H(0)=0. \newline \textit{Happiness is an arbitrary numerical unit.}
  \item Students want to maximize their happiness.
  \item Grading an assignment costs 1 happiness.
  \item Happiness is not affected by external factors, such as the grades of peers.
  \item Students can communicate with their peers.
  \item Students are not perfect graders.
  \item There is no such thing as partial-grading.
  \item Students can report their level of uncertainty when they grade. Let this factor be equal to U.
  \item More effort spent in grading lowers uncertainty.
  \item When a student assigns a grade G, the chance of the grade being N off from the actual grade is proportional to U.
\end{enumerate}

\section{Benchmark}

To compare mechanisms, we created a numerical benchmark (objective function) where a lower score is better. The score is computed by adding the most work done by any person to the highest possible error in grading. Mathematically:

$\max_{i \ge 1} \{|H(g_i)-H(o_i)|\} + \max_{i \ge 0} \{w_i\}$

\subsection{Mechanisms}

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Calibration-Flowchart.eps}
\caption{A flowchart of the Calibration Mechanism from the student perspective.}
\label{fig:calibration}
\end{figure}

The Calibration mechanism is described visually in Figure~\ref{fig:calibration}. It achieves a low benchmark score of 4, of a 2 in max work done and 2 in max error in grade.
The Calibration mechanism can break when students communicate to reveal the calibrated assignment to circumvent grading. The Improved Calibration mechanism mitigates this issue by introducing multiple calibrated papers at the expense of more work, raising the objective score.

We tested and verified the Calibration mechanism through an anonymous crowdsourced experiment. In this case, ``grading'' involved counting two sets of objects. Initially unknown to the participant, one set is ``calibrated'' and will be used to reward the participant based on the accuracy of the grading.

The Calibration mechanism rewards students for accurately grading the Calibrated set in order to reduce the grading error for the uncalibrated set, as shown in Figure~\ref{fig:reward-error}. This is also evident in Figure~\ref{fig:error-calibration}, where less error in grading the Calibrated set correlates to a lower maximum grading error. An accurate grade for the uncalibrated set is the goal for the Calibration mechanism, and the data suggests that the mechanism works in practice.

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Reward-Error-Graph.eps}
\caption{Uncalibrated Error vs Reward}
\label{fig:reward-error}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Error-Calibration-Graph.eps}
\caption{Max error vs Calibrated error}
\label{fig:error-calibration}
\end{figure}

\subsection{Deduction Mechanism}

The Deduction mechanism (Figure~\ref{fig:deduction}) achieves a very low benchmark score of 2, consisting of a 2 in max work done and a 0 in max error in grade. Incapable graders will raise the benchmark score, as they issue refutations that add work to the professor.

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Deduction-Flowchart.eps}
\caption{A flowchart of the Deduction Mechanism from the student perspective.}
\label{fig:deduction}
\end{figure}

\section{Results}
The comparison of existing solutions and those proposed in this work can be seen in Figure~\ref{fig:comparison}. Each mechanism will be explained below.

Traditional Professor Grading involves one professor grading all assignments. In a class of 1000 students, this method is extremely inefficient.

In Traditional Peer Grading, each student grades another's assignment without any supervision. However, as in this mechanism, the objective score is high due to the potential error caused by lack of motivation to grade properly.

% TODO: Add references to computer grading
Although without requiring effort from either professor or student, Traditional Automated Grading of open-ended responses are still under heavy research. Current solutions are quite preliminary, though can arrive at a grade within approximately 25 percent~\cite{automatedsystemssuck}.

The Calibration Mechanism requires one calibrated paper from the professor and two papers graded by each student. The objective score is raised to 4 instead of 2 because students are incentivized by increasing their grade, thus sacrificing accuracy.

The Improved Calibration Mechanism requires each student to grade a subset of the other student's assignments, and the teacher to grade another subset. This mechanism addresses the flaw in the Calibration Mechanism that occurs when students can communicate, at the expense of more work. Thus, leading to poor scalability.

The Deduction Mechanism rewards graders for grading more harshly than their peers, and relies on a voting system to reject grades that are below the expected grade to be reviewed by the professor. In the dominant strategy behavior of the system, no grades should be rejected, leading to no work for the professor. Again, incentive given to the students comes at the cost of accuracy, raising the objective score by two points.

Overall, our Calibration and Deduction mechanisms vastly outperform existing solutions with the exception of Improved Calibration.

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Comparison-Graph.eps}
\caption{A comparison of mechanisms in terms of effectiveness and scalability.}
\label{fig:comparison}
\end{figure}

% TODO: Accessibility

% TODO: Prep for Blind Review by removing authors

\section{Conclusion}
An efficient and accurate solution is needed to grade the large number of assignments in MOOCs.

We began by creating a student model - a set of assumptions that approximate the realistic behavior of students. We then developed various grading mechanisms based on our student model and mechanism design. These mechanisms would incentivize students to grade accurately and efficiently as proven by game theory.

We tested our Calibration mechanism using a croudsourced experiment, finding that it could work in practice. A mechanism based on a more realistic model would achieve better results.

Our model can easily be reused and improved upon by future researchers who wish to develop more efficient solutions. Efficiency is measured in terms of the benchmark we created, a numerical score encompassing both the accuracy of grades and the effort spent by any one person. To the best of our knowledge, this is the first game-

\section{Future Work}
As we consider how to generate accurate grades from incompetent graders, our model will require more realistic assumptions, which in turn may create more complex mechanisms.
Eventually, we would like to see new mechanisms based off of our model or our existing mechanisms implemented in MOOCs such as EdX or Coursera.

\section{Acknowledgments}
We would like to thank MIT and the MIT PRIMES program for providing the research opportunity as well as our parents and mentors for their support.

\subsection{Additional Authors}
Mentors \newline
\textbf{Matt Weinberg} smweinberg@csail.mit.edu \newline
\textbf{Christos Tzamos} ctzamos@gmail.com

Professor \newline
\textbf{Costis Daskalakis} costis@csail.mit.edu

% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
\balance

\bibliographystyle{acm-sigchi}
\bibliography{bibliography}
\end{document}

### 2014-12-30 Paper.tex
Small Changes
Made some small changes to the addresses and the acknowledgements
section
More small changes to acknowledgements

@@
 
-\numberofauthors{5}
+\numberofauthors{2}
 \author{
@@
     \affaddr{Acton Boxborough Regional High School}\\
-    \affaddr{36 Charter Rd Acton, MA 01720, USA}\\
+    \affaddr{36 Charter Rd\\ Acton, MA 01720, USA}\\
     \email{willy.vvu@gmail.com}
@@
     \affaddr{Lexington High School}\\
-    \affaddr{251 Waltham Street, Lexington, MA 02421, USA}\\
+    \affaddr{251 Waltham Street\\ Lexington, MA 02421, USA}\\
     \email{nick.kaashoek@gmail.com}
@@
 Mentors \newline
-\textbf{Matt Weinberg} smweinberg@csail.mit.edu \newline
-\textbf{Christos Tzamos} ctzamos@gmail.com
+\textbf{Matthew~Weinberg}~(\href{mailto:smweinberg@csail.mit.edu}{smweinberg@csail.mit.edu})\newline
+\textbf{Christos~Tzamos}~(\href{mailto:ctzamos@gmail.com}{ctzamos@gmail.com})
 
-Professor \newline
-\textbf{Costis Daskalakis} costis@csail.mit.edu
+Advisor \newline
+Professor \textbf{Costis~Daskalakis}~(\href{mailto:costis@csail.mit.edu}{costis@csail.mit.edu})
 

### 2015-01-07 Paper.tex
Quick addition of title to metadata

@@
 \hypersetup{
-pdftitle={SIGCHI Conference Proceedings Format},
+pdftitle={Game Theory based Peer Grading Mechanisms for MOOCs},
 pdfauthor={LaTeX},

### 2015-01-07 Paper.tex
Nearly final edits
The pdf still needs generation.

@@
 After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration, and Deduction.
-The Calibration mechanism performs as predicted by game theory when tested in an online crowdsourced experiment.
-The Deduction mechanism performs relatively well in the benchmark, outperforming traditional automated and peer grading systems.
+The Calibration mechanism performs as predicted by game theory when tested in an online crowdsourced experiment, but fails when students are assumed to communicate.
+The Improved Calibration mechanism addresses this assumption, but at the cost of more effort spent grading.
+The Deduction mechanism performs relatively well in the benchmark, outperforming the Calibration, Improved Calibration, traditional automated, and traditional peer grading systems.
 The mathematical model and benchmark opens the way for future derivative works to be performed and compared.
@@
 \keywords{
-	MOOC; game theory; mechanism design; peer grading; learning at scale;
+	Massive Open Online Courses; MOOC; game theory; mechanism design; peer grading; learning at scale;
 }
@@
 \section{Model and Assumptions}
+\label{sec:modelandassumptions}
 Our student model consists of assumptions we believed students abide by, as follows:
 \begin{enumerate}
-  \item Let H be a function of a student's grade, returning a student's happiness, such that H(0)=0. \newline \textit{Happiness is an arbitrary numerical unit.}
+  \item Let H be a function of a student's grade, returning a student's happiness, such that a grade of zero yields zero happiness ($H(0)=0$).
+\newline \textit{Happiness is an arbitrary numerical unit.}
   \item Students want to maximize their happiness.
-  \item Grading an assignment costs 1 happiness.
+  \item Grading an assignment costs 1 (one) happiness.
   \item Happiness is not affected by external factors, such as the grades of peers.
@@
 To compare mechanisms, we created a numerical benchmark (objective function) where a lower score is better.
-The score is computed by adding the most work done by any person to the highest possible error in grading.
+The score is computed by adding the highest possible error in student grading to the most work done by any person.
 Mathematically:
 
-$\max_{i \ge 1} \{|H(g_i)-H(o_i)|\} + \max_{i \ge 0} \{w_i\}$
+$\max_{i \ge 1} \{|H(g_i)-H(o_i)|\} + \max_{i \ge 1} \{w_i\}$
 
+Where $w_i$ is the work done, or number of assignments graded, by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the grade that would have been given by the professor on the $i$th assignment.
+$H$ is the happiness function defined in section~\ref{sec:modelandassumptions}.
+
+Where 
 \subsection{Mechanisms}
@@
 
-The Calibration mechanism is described visually in Figure~\ref{fig:calibration}. It achieves a low benchmark score of 4, of a 2 in max work done and 2 in max error in grade.
+The Calibration mechanism is described visually in Figure~\ref{fig:calibration}. It achieves a low benchmark score of 4, consisting of a 2 in max work done and 2 in max error in grade.
 The Calibration mechanism can break when students communicate to reveal the calibrated assignment to circumvent grading.
@@
 
-The Deduction mechanism (Figure~\ref{fig:deduction}) achieves a very low benchmark score of 2, consisting of a 2 in max work done and a 0 in max error in grade.
+The Deduction mechanism (Figure~\ref{fig:deduction}) achieves a very low benchmark score of 2, with 2 in max work done and a 0 in max error in grade.
 Incapable graders will raise the benchmark score, as they issue refutations that add work to the professor.
@@
 
-Traditional Professor Grading involves one professor grading all assignments. In a class of 1000 students, this method is extremely inefficient.
+Traditional Professor Grading involves one professor grading all assignments. In an online class of 1000 students, this method is extremely inefficient.
 

### 2015-01-08 Paper.tex
More small fixes, and copyright

@@
 
-\toappear{Pending copyright...}
+\toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is  granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for components of this work owned by others than ACM must be honored.
+Abstracting with credit is permitted.
+To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
+Request permissions from permissions@acm.org.
+\\
+{\emph{L@S'15}}, March 14-15, 2015, Vancouver, Canada. \\
+Copyright \copyright~2015 ACM ISBN/15/03...\$15.00. \\
+DOI string from ACM form confirmation}
 
@@
 
-Where $w_i$ is the work done, or number of assignments graded, by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the grade that would have been given by the professor on the $i$th assignment.
+Where $w_i$ is the work done or number of assignments graded by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the grade that would have been given by the professor on the $i$th assignment.
 $H$ is the happiness function defined in section~\ref{sec:modelandassumptions}.

### 2015-01-08 Paper.tex
Added content around transitional areas

@@
 
+With a student model in place, it is now possible to simulate student behavior with game theory, in order to eventually determine the effectiveness of various mechanisms when exposed to students.
+However, effectiveness needs to be quantified as well.
+This is addressed by the creation of a numerical benchmark.
+
 \section{Benchmark}
@@
 
-Where $w_i$ is the work done or number of assignments graded by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the grade that would have been given by the professor on the $i$th assignment.
-$H$ is the happiness function defined in section~\ref{sec:modelandassumptions}.
+where $w_i$ is the work done or number of assignments graded by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the accurate grade that would have been given by the professor on the $i$th assignment.
+$H$ is the happiness function defined in the \textit{Models and Assumptions}~section.
 
-Where 
-\subsection{Mechanisms}
+Creating a benchmark now allows various mechanisms to be brainstormed with mechanism design and subsequently tested.
+\section{Mechanisms}
+\subsection{Calibration Mechanism}
 
@@
 The Calibration mechanism is described visually in Figure~\ref{fig:calibration}. It achieves a low benchmark score of 4, consisting of a 2 in max work done and 2 in max error in grade.
-The Calibration mechanism can break when students communicate to reveal the calibrated assignment to circumvent grading.
-The Improved Calibration mechanism mitigates this issue by introducing multiple calibrated papers at the expense of more work, raising the objective score.
 
@@
 
-The Calibration mechanism rewards students for accurately grading the Calibrated set in order to reduce the grading error for the uncalibrated set, as shown in Figure~\ref{fig:reward-error}.
-This is also evident in Figure~\ref{fig:error-calibration}, where less error in grading the Calibrated set correlates to a lower maximum grading error.
-An accurate grade for the uncalibrated set is the goal for the Calibration mechanism, and the data suggests that the mechanism works in practice.
+We added a reward system to the Calibration mechanism to incentivize participants to grade correctly.
+This reward, awarded for accurately grading the Calibrated set, is synonymous to the punishment administered by the professor upon improperly grading the Calibrated set.
+In Figure~\ref{fig:error-calibration}, where the maximum error made in grading both calibrated and uncalibrated sets is plotted against the error made only on the calibrated set.
+The conclusion that can be drawn is that the grader's performance on the Calibrated set seems to be a general indication of the grader's performance overall.
+Another correlation is evident in Figure~\ref{fig:reward-error}, where grading error is plotted against relative magnitude of reward.
+This shows that a higher reward correlates to lower error.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.9\columnwidth]{Error-Calibration-Graph.eps}
+\caption{Max error vs Calibrated error}
+\label{fig:error-calibration}
+\end{figure}
 
@@
 
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.9\columnwidth]{Error-Calibration-Graph.eps}
-\caption{Max error vs Calibrated error}
-\label{fig:error-calibration}
-\end{figure}
+Putting two parts together, a grader's overall error can be estimated from performance on the Calibrated set.
+By rewarding graders based low errors on the Calibrated set, more accurate grades for the uncalibrated set are likely to be attained.
+Accuracy of grades on the uncalibrated set is one of the goals for the Calibration mechanism, and the data suggests that the mechanism works in practice.
+
+\subsection{Improved Calibration Mechanism}
+Originally designed with the assumption that students cannot communicate, the Calibration mechanism quickly breaks when student conspire to reveal the calibrated assignment to circumvent grading.
+The Improved Calibration mechanism mitigates this issue by introducing multiple calibrated papers at the expense of more work, raising the objective score.
+However, since the work created by this mechanism does not scale well with class size, a better mechanism was developed: the Deduction mechanism.
 

### 2015-01-09 Paper.tex
Added mention of our experiment and other
Small changes to enhance clarity/grammar

@@
 A benchmark function accounting for grade accuracy and workload is established to quantitatively compare effectiveness and scalability of various mechanisms.
-After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration, and Deduction.
+After multiple iterations of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration, and Deduction.
 The Calibration mechanism performs as predicted by game theory when tested in an online crowdsourced experiment, but fails when students are assumed to communicate.
@@
   \item Students are not perfect graders.
-  \item There is no such thing as partial-grading.
+  \item There is no such thing as partial-grading. That is to say, students either grade or do not grade. There is no middle ground.
   \item Students can report their level of uncertainty when they grade. Let this factor be equal to U.
@@
 This shows that a higher reward correlates to lower error.
+The data for both of these figures were obtained through a crowdsourced experiment which simulated the calibration mechanism.
 

### 2015-01-09 Paper.tex
Just about final. Submitting it soon.

@@
 Initially unknown to the participant, one set is ``calibrated'' and will be used to reward the participant based on the accuracy of the grading.
-
 We added a reward system to the Calibration mechanism to incentivize participants to grade correctly.
 This reward, awarded for accurately grading the Calibrated set, is synonymous to the punishment administered by the professor upon improperly grading the Calibrated set.
-In Figure~\ref{fig:error-calibration}, where the maximum error made in grading both calibrated and uncalibrated sets is plotted against the error made only on the calibrated set.
-The conclusion that can be drawn is that the grader's performance on the Calibrated set seems to be a general indication of the grader's performance overall.
+
+The results of this experiment can be seen in Figure~\ref{fig:error-calibration}, where the maximum error made in grading both calibrated and uncalibrated sets is plotted against the error made only on the calibrated set.
+The grader's performance on the Calibrated set is shown to be a general indication of the grader's performance overall.
 Another correlation is evident in Figure~\ref{fig:reward-error}, where grading error is plotted against relative magnitude of reward.
 This shows that a higher reward correlates to lower error.
-The data for both of these figures were obtained through a crowdsourced experiment which simulated the calibration mechanism.
+Together, these verify that the Calibration mechanism indeed works.
 
@@
 Efficiency is measured in terms of the benchmark we created, a numerical score encompassing both the accuracy of grades and the effort spent by any one person.
-To the best of our knowledge, this is the first game-
+To the best of our knowledge, this is the first game-theory-based peer-grading system.
 
@@
 We would like to thank MIT and the MIT PRIMES program for providing the research opportunity as well as our parents and mentors for their support.
+Of course, none of this is possible without the original idea proposed by our advisor.
 

### 2015-02-02 CHIext-template/sample.tex
Finally in the right format.

\documentclass{chi-ext}
% Please be sure that you have the dependencies (i.e., additional LaTeX packages) to compile this example.
% See http://personales.upv.es/luileito/chiext/

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
 \copyrightinfo{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
 {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
 Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
 DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\title{CHI \LaTeX\ Ext. Abstracts Template}

\numberofauthors{5}
% Notice how author names are alternately typesetted to appear ordered in 2-column format;
% i.e., the first 4 autors on the first column and the other 4 auhors on the second column.
% Actually, it's up to you to strictly adhere to this author notation.
\author{
  \alignauthor{
  	\textbf{First Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author1@anotherco.com}
  }\alignauthor{
  	\textbf{Fourth Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author5@anotherco.com}
  }
  \vfil
  \alignauthor{
  	\textbf{Second Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author2@anotherco.com}
  }\alignauthor{
  	\textbf{Fifth Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author6@anotherco.com}
  }
  \vfil
  \alignauthor{
  	\textbf{Third Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author3@anotherco.com}
  }
}

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{CHI LaTeX Extended Abstracts Template}
\def\plainauthor{Luis A. Leiva}
\def\plainkeywords{Guides, instructions, author's kit, conference publications}
\def\plaingeneralterms{Documentation, Standardization}

\hypersetup{
  % Your metadata go here
  pdftitle={\plaintitle},
  pdfauthor={\plainauthor},  
  pdfkeywords={\plainkeywords},
  pdfsubject={\plaingeneralterms},
  % Quick access to color overriding:
  %citecolor=black,
  %linkcolor=black,
  %menucolor=black,
  %urlcolor=black,
}

\usepackage{graphicx}   % for EPS use the graphics package instead
\usepackage{balance}    % useful for balancing the last columns
\usepackage{bibspacing} % save vertical space in references

\begin{document}

\maketitle

\begin{abstract}
In this sample we describe the formatting requirements for various SIGCHI related submissions 
and offer recommendations on writing for the worldwide SIGCHI readership. 
%Do not change the page size or page settings.
Please review this document even if you have submitted to SIGCHI conferences before, 
some format details have changed relative to previous years.
\end{abstract}

\keywords{\plainkeywords}
\textcolor{red}{Optional section to be included in your final version.}

\category{H.5.m}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}. 
%See \cite{ACMCCS} 
See: \url{http://www.acm.org/about/class/1998/} 
for help using the ACM Classification system.
\textcolor{red}{Optional section to be included in your final version, but strongly encouraged.}

% =============================================================================
\section{Introduction}
% =============================================================================
This format is to be used for submissions that are published in the conference extended abstracts.  
We wish to give this volume a consistent, high-quality appearance. 
We therefore ask that authors follow some simple guidelines. 
In essence, you should format your paper exactly like this document. 
The easiest way to do this is simply to download a template from the conference website and replace the content with your own material.

% =============================================================================
\section{Copyright}
% =============================================================================
For publications in the CHI Extended Abstracts, copyright remains with the author.  
The publication is not considered an archival publication; however, it does go into the ACM Digital Library. 
Because you retain copyright, as the author you are free to use this material as you like, including submitting a paper based on this work to other conferences or journals.  
Authors grant unrestricted permission for ACM to publish the accepted submission in the CHI Extended Abstracts without additional consideration or remuneration.

% =============================================================================
\section{Text formatting}
% =============================================================================
Please use an 8.5-point Verdana font, or other sans serifs font as close as possible in appearance to Verdana in which these guidelines have been set. 
Arial 9-point font is a reasonable substitute for Verdana as it has a similar x-height. 
Please use serif or non-proportional fonts only for special purposes, such as distinguishing source code text.
Additionally, here is an example of footnoted text.\footnote{Use footnotes sparingly, if at all.}
As stated in the footnote, footnotes should rarely be used.

\subsection{Language, style, and content}
% -----------------------------------------------------------------------------
The written and spoken language of SIGCHI is English. 
Spelling and punctuation may use any dialect of English (e.g., British, Canadian, US, etc.) provided this is done consistently. 
Hyphenation is optional. 
To ensure suitability for an international audience, please pay attention to the following:

\begin{itemize}\compresslist
\item 	
Write in a straightforward style. 
Use simple sentence structure. 
Try to avoid long sentences and complex sentence structures. 
Use semicolons carefully.
\item 	
Use common and basic vocabulary (e.g., use the word ``unusual" rather than the word ``arcane").
\item 	
Briefly define or explain all technical terms. 
The terminology common to your practice/discipline may be different in other design practices/disciplines.
\item 	
Spell out all acronyms the first time they are used in your text. 
For example, ``World Wide Web (WWW)".
\item 	
Explain local references (e.g., not everyone knows all city names in a particular country).
\item 	
Explain ``insider" comments. 
Ensure that your whole audience understands any reference whose meaning you do not describe (e.g., do not assume that everyone has used a Macintosh or a particular application).
\item 	
Explain colloquial language and puns. 
Understanding phrases like ``red herring" requires a cultural knowledge of English. 
Humor and irony are difficult to translate.
\item 	
Use unambiguous forms for culturally localized concepts, such as times, dates, currencies and numbers (e.g., ``1-5-97" or ``5/1/97" may mean 5 January or 1 May, and ``seven o'clock" may mean 7:00 am or 19:00).
\item 	
Be careful with the use of gender-specific pronouns (he, she) and other gender-specific words (chairman, manpower, man-months). 
Use inclusive language (e.g., she or he, they, chair, staff, staff-hours, person-years) that is gender-neutral. 
If necessary, you may be able to use ``he" and ``she" in alternating sentences, so that the two genders occur equally often~\cite{Schwartz95}. 
\end{itemize}

% =============================================================================
\section{Figures}
% =============================================================================
The examples on this and following pages should help you get a feel for how screen-shots and other figures should be placed in the template. 
Be sure to make images large enough so the important details are legible and clear.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{sample.jpg}
  \caption{Insert a caption below each figure.}
  \label{fig:sample}
\end{figure}
\marginpar{
\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{Figure2.png}
  \caption{One good use of the narrow margin column: callouts that annotate a figure, either with text or a more detailed image.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}
}

Your document may use color figures, which are included in the page limit; the figures must be usable when printed in black and white.
You can use the \LaTeX's \texttt{marginpar} command to insert figures in the (left) margin side of the document (see \autoref{fig:marginparsample}).

% =============================================================================
\section{References and Citations}
% =============================================================================
Use a numbered list of references at the end of the article, ordered alphabetically by first author, and referenced by numbers in brackets \cite{Anderson92,Klemmer02,Mather00,Zellweger01}
For papers from conference proceedings, include the title of the paper and an abbreviated name of the conference (e.g., for Interact 2003 proceedings, use Proc. Interact 2003). 
Do not include the location of the conference or the exact date; do include the page numbers if available. 
See the examples of citations at the end of this document.

Your references should be published materials accessible to the public.  
Internal technical reports may be cited only if they are easily accessible (i.e., you provide the address for obtaining the report within your citation) and may be obtained by any reader for a nominal fee.  
Proprietary information may not be cited. 
Private communications should be acknowledged in the main text, not referenced  (e.g., [Robertson, personal communication]).

% =============================================================================
\section{Accessibility}
% =============================================================================
The Executive Council of SIGCHI has committed to making SIGCHI conferences more inclusive for researchers, practitioners, and educators with disabilities. As a part of this goal, the all authors are asked to work on improving the accessibility of their submissions. Specifically, we encourage authors to carry out the following five steps:
\begin{enumerate}
	\item Add alternative text to all figures
	\item Mark table headings
	\item Add tags to the PDF
	\item Verify the default language
	\item Set the tab order to ``Use Document Structure''
\end{enumerate}
Unfortunately good tools do not yet exist to create tagged PDF files from Latex. LaTeX users will need to carry out all of the above steps in the PDF directly using Adobe Acrobat, after the PDF has been generated.

For more information and links to instructions and resources, please see:
{\url{http://chi2014.acm.org/authors/guide-to-an-accessible-submission}}.

% =============================================================================
\section{Producing and testing PDF files}
% =============================================================================
We recommend that you produce a PDF version of your submission well before the final deadline. 
Besides making sure that you are able to produce a PDF, you will need to check that (a) the length of the file remains within the submission category's page limit, (b) the PDF file size is 4 megabytes or less, and (c) the file can be read and printed using Adobe Acrobat Reader. 
Test your PDF file by viewing or printing it with the same software we will use when we receive it, Adobe Acrobat Reader Version 7. 
This is widely available at no cost from~\cite{Acrobat7}.  
Note that most reviewers will use a North American/European version of Acrobat reader, which cannot handle documents containing non-North American or non-European fonts (e.g. Asian fonts).  
Please therefore do not use Asian fonts, and verify this by testing with a North American/European Acrobat reader (obtainable as above). Something as minor as including a space or punctuation character in a two-byte font can render a file unreadable.

% =============================================================================
\section{Dummy text}
% =============================================================================
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ut eros semper lectus vehicula elementum. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam quis mi sapien. Suspendisse potenti. Mauris ultrices euismod velit sed dictum. Nullam auctor, nulla tincidunt dapibus suscipit, velit leo convallis metus, vel commodo libero erat in dolor. In laoreet porttitor ligula, porta blandit lectus consequat quis.

Nam ut eros dui. Mauris volutpat elit metus, euismod pellentesque purus. In hac habitasse platea dictumst. Nullam consectetur lacinia interdum. Sed nec blandit nisi. Proin in nulla purus, sit amet iaculis tortor. Ut dapibus pellentesque nulla in interdum. Nunc at velit felis. Curabitur euismod neque eu orci varius in pharetra sem interdum. Morbi in mauris ac risus iaculis dapibus id in magna. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.

Aliquam consectetur quam sed odio varius vitae rhoncus urna fermentum. Phasellus viverra diam non justo porttitor varius. Integer ultrices accumsan lectus eget mollis. Nulla et leo sit amet nunc ornare rutrum sit amet ac dui. Cras vehicula accumsan purus nec fermentum. Mauris viverra condimentum metus, ut posuere quam laoreet nec. Phasellus massa tellus, ullamcorper nec porta sed, aliquet vitae nulla. Phasellus non tortor mauris. Cras ullamcorper egestas erat, vel rutrum elit viverra a. Donec in nisl ut est facilisis blandit. Quisque congue accumsan risus, ut venenatis magna vulputate vel. Nam commodo sapien vel mauris adipiscing nec dictum quam congue. Phasellus tempor vestibulum nisl quis blandit. Nullam condimentum auctor nibh, quis elementum libero tristique.

\section{Acknowledgements}
We thank all DUX 2003 publications support and staff who wrote this document originally and allowed us to modify it for this conference.
This template was based on Manas Tungare's \texttt{chi.cls}, and rewritten by Luis A. Leiva.

\section{References format}
References must be the same font size as other body text.
% REFERENCES FORMAT
% References must be the same font size as other body text.

\balance
\bibliographystyle{acm-sigchi}
\bibliography{sample}

\end{document}

### 2015-02-02 Paper.tex
Finally in the right format.

@@
-\documentclass{sigchi}
-
-% Use this command to override the default ACM copyright statement (e.g. for preprints). 
-% Consult the conference website for the camera-ready copyright statement.
+\documentclass{chi-ext}
+% Please be sure that you have the dependencies (i.e., additional LaTeX packages) to compile this example.
+% See http://personales.upv.es/luileito/chiext/
 
 %% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
-% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+% \copyrightinfo{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
 Copyrights for components of this work owned by others than ACM must be honored.
@@
 %% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
+\copyrightinfo{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for third-party components of this work must be honored.
+For all other uses, contact the Owner/Author.
+\\
+Copyright is held by the owner/author(s). \\
+{\emph{L@S 2015}}, Mar 14-18, 2015, Vancouver, BC, Canada \\
+ACM 978-1-4503-3411-2/15/03. \\
+http://dx.doi.org/10.1145/2724660.2728676}
 
-\toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is  granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
-Copyrights for components of this work owned by others than ACM must be honored.
-Abstracting with credit is permitted.
-To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
-Request permissions from permissions@acm.org.
-\\
-{\emph{L@S'15}}, March 14-15, 2015, Vancouver, Canada. \\
-Copyright \copyright~2015 ACM ISBN/15/03...\$15.00. \\
-DOI string from ACM form confirmation}
+\title{Game Theory Based Peer Grading Mechanisms For MOOCs}
 
-% Arabic page numbers for submission. 
-% Remove this line to eliminate page numbers for the camera ready copy
-% \pagenumbering{arabic}
+\numberofauthors{5}
+% Notice how author names are alternately typesetted to appear ordered in 2-column format;
+% i.e., the first 4 autors on the first column and the other 4 auhors on the second column.
+% Actually, it's up to you to strictly adhere to this author notation.
+\author{
+  \alignauthor{
+    \textbf{Constantinos Daskalakis}\\
+    \affaddr{Massachusetts Institute of Technology}\\
+    \affaddr{77 Massachusetts Avenu}\\
+    \affaddr{Cambridge, MA 02139}\\
+    \email{costis@csail.mit.edu}
+  }\alignauthor{
+    \textbf{Nicolaas Kaashoek}\\
+    \affaddr{Lexington High School}\\
+    \affaddr{251 Waltham Street}\\
+    \affaddr{Lexington, MA 02421, USA}\\
+    \email{nick.kaashoek@gmail.com}
+  }
+  \vfil
+  \alignauthor{
+    \textbf{Christos Tzamos}\\
+    \affaddr{Massachusetts Institute of Technology}\\
+    \affaddr{77 Massachusetts Avenu}\\
+    \affaddr{Cambridge, MA 02139}\\
+    \email{ctzamos@gmail.com}
+  }\alignauthor{
+    \textbf{Matthew Weinberg}\\
+    \affaddr{Massachusetts Institute of Technology}\\
+    \affaddr{77 Massachusetts Avenu}\\
+    \affaddr{Cambridge, MA 02139}\\
+    \email{smweinberg@csail.mit.edu}
+  }
+  \vfil
+  \alignauthor{
+    \textbf{William Wu}\\
+    \affaddr{Acton Boxborough Regional High School}\\
+    \affaddr{36 Charter Rd}\\
+    \affaddr{Acton, MA 01720, USA}\\
+    \email{willy.vvu@gmail.com}
+  }
+}
 
-% Load basic packages
-\usepackage{balance}  % to better equalize the last page
-\usepackage{graphicx} % for EPS, load graphicx instead
-\usepackage{times}    % comment if you want LaTeX's default font
-\usepackage{url}      % llt: nicely formatted URLs
+% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
+\def\plaintitle{Game Theory based Peer Grading Mechanisms for MOOCs}
+\def\plainauthor{William Wu}
+\def\plainkeywords{MOOC, game theory, mechanism design, peer grading, learning at scale}
+\def\plaingeneralterms{Game Theory, Mechanism Design, Peer Grading}
+
+\hypersetup{
+  % Your metadata go here
+  pdftitle={\plaintitle},
+  pdfauthor={\plainauthor},  
+  pdfkeywords={\plainkeywords},
+  pdfsubject={\plaingeneralterms},
+  % Quick access to color overriding:
+  %citecolor=black,
+  %linkcolor=black,
+  %menucolor=black,
+  %urlcolor=black,
+}
+
+\usepackage{graphicx}   % for EPS use the graphics package instead
+\usepackage{balance}    % useful for balancing the last columns
+\usepackage{bibspacing} % save vertical space in references
+
 \usepackage{epstopdf}
 
-% llt: Define a global style for URLs, rather that the default one
-\makeatletter
-\def\url@leostyle{%
-  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
-\makeatother
-\urlstyle{leo}
-
-% To make various LaTeX processors do the right thing with page size.
-\def\pprw{8.5in}
-\def\pprh{11in}
-\special{papersize=\pprw,\pprh}
-\setlength{\paperwidth}{\pprw}
-\setlength{\paperheight}{\pprh}
-\setlength{\pdfpagewidth}{\pprw}
-\setlength{\pdfpageheight}{\pprh}
-
-% Make sure hyperref comes last of your loaded packages, 
-% to give it a fighting chance of not being over-written, 
-% since its job is to redefine many LaTeX commands.
-\usepackage[pdftex]{hyperref}
-\hypersetup{
-pdftitle={Game Theory based Peer Grading Mechanisms for MOOCs},
-pdfauthor={LaTeX},
-pdfkeywords={MOOC, game theory, mechanism design, peer grading, learning at scale},
-bookmarksnumbered,
-pdfstartview={FitH},
-colorlinks,
-citecolor=black,
-filecolor=black,
-linkcolor=black,
-urlcolor=black,
-breaklinks=true,
-}
-
-% create a shortcut to typeset table headings
-\newcommand\tabhead[1]{\small\textbf{#1}}
-
-% End of preamble. Here it comes the document.
 \begin{document}
-
-\title{Game Theory based Peer Grading Mechanisms for MOOCs}
-
-\numberofauthors{2}
-\author{
-  \alignauthor William Wu\\
-    \affaddr{Acton Boxborough Regional High School}\\
-    \affaddr{36 Charter Rd\\ Acton, MA 01720, USA}\\
-    \email{willy.vvu@gmail.com}
-  \alignauthor Nicolaas Kaashoek\\
-    \affaddr{Lexington High School}\\
-    \affaddr{251 Waltham Street\\ Lexington, MA 02421, USA}\\
-    \email{nick.kaashoek@gmail.com}
-}
 
@@
 
-\keywords{
-	Massive Open Online Courses; MOOC; game theory; mechanism design; peer grading; learning at scale;
-}
+\keywords{Massive Open Online Courses; MOOC; game theory; mechanism design; peer grading; learning at scale;}
 
-\category{K.3.m.}{Computers and Education}{Miscellaneous}
+\category{H.5.m}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}. 
+%See \cite{ACMCCS} 
+See: \url{http://www.acm.org/about/class/1998/} 
+for help using the ACM Classification system.
 
@@
 
-\begin{figure}[!h]
+\begin{figure}
   \centering
-\includegraphics[width=0.9\columnwidth]{Calibration-Flowchart.eps}
+  \includegraphics[width=\linewidth]{Calibration-Flowchart.eps}
   \caption{A flowchart of the Calibration Mechanism from the student perspective.}
@@
 
-\begin{figure}[!h]
+\begin{figure}
   \centering
-\includegraphics[width=0.9\columnwidth]{Error-Calibration-Graph.eps}
+  \includegraphics[width=\linewidth]{Error-Calibration-Graph.eps}
   \caption{Max error vs Calibrated error}
@@
 
-\begin{figure}[!h]
+\begin{figure}
   \centering
-\includegraphics[width=0.9\columnwidth]{Reward-Error-Graph.eps}
+  \includegraphics[width=\linewidth]{Reward-Error-Graph.eps}
   \caption{Uncalibrated Error vs Reward}
@@
 
-\begin{figure}[!h]
+\begin{figure}
   \centering
-\includegraphics[width=0.9\columnwidth]{Deduction-Flowchart.eps}
+  \includegraphics[width=\linewidth]{Deduction-Flowchart.eps}
   \caption{A flowchart of the Deduction Mechanism from the student perspective.}
@@
 
-\begin{figure}[!h]
+\begin{figure}
   \centering
-\includegraphics[width=0.9\columnwidth]{Comparison-Graph.eps}
+  \includegraphics[width=\linewidth]{Comparison-Graph.eps}
   \caption{A comparison of mechanisms in terms of effectiveness and scalability.}
@@
 
-\subsection{Additional Authors}
-Mentors \newline
-\textbf{Matthew~Weinberg}~(\href{mailto:smweinberg@csail.mit.edu}{smweinberg@csail.mit.edu})\newline
-\textbf{Christos~Tzamos}~(\href{mailto:ctzamos@gmail.com}{ctzamos@gmail.com})
-
-Advisor \newline
-Professor \textbf{Costis~Daskalakis}~(\href{mailto:costis@csail.mit.edu}{costis@csail.mit.edu})
-
-% Note that in a perfect world balance wants to be in the first
-% column of the last page.
-%
-% If balance doesn't work for you, you can remove that and
-% hard-code a column break into the bbl file right before you
-% submit:
-%
-% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
-% in-an-ieee-paper-if-using-bibtex
-%
-% Or, just remove \balance and give up on balancing the last page.
-%
 \balance
-
 \bibliographystyle{acm-sigchi}
 \bibliography{bibliography}
+
 \end{document}

### 2015-02-05 Paper.tex
Nearly final! Day of submission.

@@
   \alignauthor{
+    \textbf{William Wu}\\
+    \affaddr{Acton Boxborough Regional High School}\\
+    \affaddr{36 Charter Rd}\\
+    \affaddr{Acton, MA 01720, USA}\\
+    \email{willy.vvu@gmail.com}
+  }\alignauthor{
+    \textbf{Christos Tzamos}\\
+    \affaddr{Massachusetts Institute of Technology}\\
+    \affaddr{77 Massachusetts Avenue}\\
+    \affaddr{Cambridge, MA 02139}\\
+    \email{ctzamos@gmail.com}
+  }
+  \vfil
+  \alignauthor{
     \textbf{Constantinos Daskalakis}\\
     \affaddr{Massachusetts Institute of Technology}\\
-    \affaddr{77 Massachusetts Avenu}\\
+    \affaddr{77 Massachusetts Avenue}\\
     \affaddr{Cambridge, MA 02139}\\
@@
   }\alignauthor{
+    \textbf{Matthew Weinberg}\\
+    \affaddr{Massachusetts Institute of Technology}\\
+    \affaddr{77 Massachusetts Avenue}\\
+    \affaddr{Cambridge, MA 02139}\\
+    \email{smweinberg@csail.mit.edu}
+  }
+  \vfil
+  \alignauthor{
     \textbf{Nicolaas Kaashoek}\\
@@
     \email{nick.kaashoek@gmail.com}
-  }
-  \vfil
-  \alignauthor{
-    \textbf{Christos Tzamos}\\
-    \affaddr{Massachusetts Institute of Technology}\\
-    \affaddr{77 Massachusetts Avenu}\\
-    \affaddr{Cambridge, MA 02139}\\
-    \email{ctzamos@gmail.com}
-  }\alignauthor{
-    \textbf{Matthew Weinberg}\\
-    \affaddr{Massachusetts Institute of Technology}\\
-    \affaddr{77 Massachusetts Avenu}\\
-    \affaddr{Cambridge, MA 02139}\\
-    \email{smweinberg@csail.mit.edu}
-  }
-  \vfil
-  \alignauthor{
-    \textbf{William Wu}\\
-    \affaddr{Acton Boxborough Regional High School}\\
-    \affaddr{36 Charter Rd}\\
-    \affaddr{Acton, MA 01720, USA}\\
-    \email{willy.vvu@gmail.com}
   }
@@
 We tested and verified the Calibration mechanism through an anonymous crowdsourced experiment.
-In this case, ``grading'' involved counting two sets of objects.
+We wrote a program that presented participants with two sets of randomly generated orange and blue colored objects.
+Each set represented an assignment, and ``grading'' an assignment involved counting the number of orange objects in each set.
+After observing the set for a randomly chosen amount of time, participants were asked to input the number of orange objects they thought they saw in each set.
 Initially unknown to the participant, one set is ``calibrated'' and will be used to reward the participant based on the accuracy of the grading.
-We added a reward system to the Calibration mechanism to incentivize participants to grade correctly.
 This reward, awarded for accurately grading the Calibrated set, is synonymous to the punishment administered by the professor upon improperly grading the Calibrated set.
@@
 An efficient and accurate solution is needed to grade the large number of assignments in MOOCs.
-
-We began by creating a student model - a set of assumptions that approximate the realistic behavior of students.
-We then developed various grading mechanisms based on our student model and mechanism design.
-These mechanisms would incentivize students to grade accurately and efficiently as proven by game theory.
-
-We tested our Calibration mechanism using a croudsourced experiment, finding that it could work in practice. A mechanism based on a more realistic model would achieve better results.
-
-Our model can easily be reused and improved upon by future researchers who wish to develop more efficient solutions.
-Efficiency is measured in terms of the benchmark we created, a numerical score encompassing both the accuracy of grades and the effort spent by any one person.
-To the best of our knowledge, this is the first game-theory-based peer-grading system.
+In this paper, a student model was first created - a set of assumptions that approximate the realistic behavior of students.
+Based on this model, various grading mechanisms were developed: Calibration, Improved Calibration, and Deduction.
+These mechanisms incentivize students to grade accurately and efficiently as proven by game theory.
+The Calibration mechanism was tested with a croudsourced experiment, showing that it could work in practice.
+The student model can easily be reused and improved upon by future researchers who wish to develop more efficient solutions to more realistic scenarios.
+Mechanism efficiency can be measured in terms of benchmark defined in this paper.
+The benchmark is a numerical score encompassing both the accuracy of grades and the effort spent by any one person.
+The inclusion of effort spent by any one person in the benchmark enables the grading system scalability to be taken into account.
+To the best of our knowledge, these are the first game-theory-based peer-grading mechanisms.
 
@@
 We would like to thank MIT and the MIT PRIMES program for providing the research opportunity as well as our parents and mentors for their support.
-Of course, none of this is possible without the original idea proposed by our advisor.
+Of course, none of this is possible without the original idea proposed by our advisor, Constantinos Daskalakis.
 

### 2015-02-05 Paper.tex
Final! Submission very soon.

@@
 After multiple iterations of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration, and Deduction.
-The Calibration mechanism performs as predicted by game theory when tested in an online crowdsourced experiment, but fails when students are assumed to communicate.
+The Calibration mechanism performs as predicted by game theory when tested in an online crowd-sourced experiment, but fails when students are assumed to communicate.
 The Improved Calibration mechanism addresses this assumption, but at the cost of more effort spent grading.
@@
 
-\category{H.5.m}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}. 
-%See \cite{ACMCCS} 
+\category{K.3.m.}{Computers and Education}{Miscellaneous}. \\
 See: \url{http://www.acm.org/about/class/1998/} 
@@
 Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canMOOCsreducecc}.
-However, the main importance of MOOCs come from their scalability.
-MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofMOOCs}: by the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofMOOCs}.
-The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.
+The main importance of MOOCs is their ability to educate massive numbers of students worldwide~\cite{makingsenseofMOOCs}: by the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofMOOCs}.
+This leads to high student-professor ratios, reaching 150,000:1 in some courses.
 
-High student-professor ratios lead to problems for professors.
-Professors are simply unable to grade hundreds of thousands of submissions.
+High student-professor ratios lead to problems for professors, who are simply unable to grade hundreds of thousands of submissions.
 Currently, two types of solutions are used to remedy the problem: automated grading and peer grading~\cite{edxsoftware}.
-Automated grading relies on machines to grade assignments.
-Machines can only check certain types of answers (i.e.
+Automated grading relies on machines, which can only check certain types of answers (i.e.
 multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongMOOCs}.
@@
 Students who know the machine's grading criteria can fool the system~\cite{robogradingproblems}, yielding inconsistent grades.
-On the other hand, peer grading can grade any type of question, a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofMOOCs}.
+On the other hand, peer grading can grade any type of question.
+However, such systems can easily be ``hacked'' by the students~\cite{makingsenseofMOOCs}.
 Additionally, lack of feedback from peer grading is an area of complaint in systems such as Coursera~\cite{howaccurateispeergrading}.
-These limitations render the students unable to effectively evaluate the mastery of the course material.
+These limitations render the students unable to effectively evaluate mastery of course material.
 
@@
 \begin{enumerate}
-  \item Let H be a function of a student's grade, returning a student's happiness, such that a grade of zero yields zero happiness ($H(0)=0$).
-\newline \textit{Happiness is an arbitrary numerical unit.}
+\item Let H be a function of a student's grade, returning a student's happiness, such that a grade of zero yields zero happiness ($H(0)=0$). \newline \textit{Happiness is an arbitrary numerical unit.}
 \item Students want to maximize their happiness.
@@
 \item Students are not perfect graders.
-  \item There is no such thing as partial-grading. That is to say, students either grade or do not grade. There is no middle ground.
-  \item Students can report their level of uncertainty when they grade. Let this factor be equal to U.
+\item There is no such thing as partial-grading. Students either grade or do not grade.
+\item Students can report their level of uncertainty (U) when they grade.
 \item More effort spent in grading lowers uncertainty.
-  \item When a student assigns a grade G, the chance of the grade being N off from the actual grade is proportional to U.
+\item The chance of a student-assigned grade G being N off from the actual grade is proportional to U.
 \end{enumerate}
 
-With a student model in place, it is now possible to simulate student behavior with game theory, in order to eventually determine the effectiveness of various mechanisms when exposed to students.
-However, effectiveness needs to be quantified as well.
-This is addressed by the creation of a numerical benchmark.
+With a student model in place, it is now possible to simulate student behavior with game theory.
 
 \section{Benchmark}
-
-To compare mechanisms, we created a numerical benchmark (objective function) where a lower score is better.
+In order to eventually determine the effectiveness of various mechanisms, as well as to compare mechanisms, we created a numerical benchmark (objective function) where a lower score is better.
 The score is computed by adding the highest possible error in student grading to the most work done by any person.
@@
 
-where $w_i$ is the work done or number of assignments graded by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the accurate grade that would have been given by the professor on the $i$th assignment.
+where $w_i$ is the work done (assignments graded) by the $i$th person, $g_i$ is the grade given by student grader on the $i$th assignment, and $o_i$ is the accurate ``objective'' grade that would have been given by the professor on the $i$th assignment.
 $H$ is the happiness function defined in the \textit{Models and Assumptions}~section.
 
-Creating a benchmark now allows various mechanisms to be brainstormed with mechanism design and subsequently tested.
 \section{Mechanisms}
 \subsection{Calibration Mechanism}
+
+The Calibration mechanism, described visually in Figure~\ref{fig:calibration},achieves a low benchmark score of 4, consisting of a 2 in max work done and 2 in max error in grade.
 
@@
 
-The Calibration mechanism is described visually in Figure~\ref{fig:calibration}. It achieves a low benchmark score of 4, consisting of a 2 in max work done and 2 in max error in grade.
-
-We tested and verified the Calibration mechanism through an anonymous crowdsourced experiment.
+We tested and verified the Calibration mechanism through an anonymous crowd-sourced experiment.
 We wrote a program that presented participants with two sets of randomly generated orange and blue colored objects.
@@
 This reward, awarded for accurately grading the Calibrated set, is synonymous to the punishment administered by the professor upon improperly grading the Calibrated set.
-
-The results of this experiment can be seen in Figure~\ref{fig:error-calibration}, where the maximum error made in grading both calibrated and uncalibrated sets is plotted against the error made only on the calibrated set.
-The grader's performance on the Calibrated set is shown to be a general indication of the grader's performance overall.
-Another correlation is evident in Figure~\ref{fig:reward-error}, where grading error is plotted against relative magnitude of reward.
-This shows that a higher reward correlates to lower error.
-Together, these verify that the Calibration mechanism indeed works.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{Error-Calibration-Graph.eps}
-  \caption{Max error vs Calibrated error}
-  \label{fig:error-calibration}
-\end{figure}
 
@@
 
-Putting two parts together, a grader's overall error can be estimated from performance on the Calibrated set.
-By rewarding graders based low errors on the Calibrated set, more accurate grades for the uncalibrated set are likely to be attained.
-Accuracy of grades on the uncalibrated set is one of the goals for the Calibration mechanism, and the data suggests that the mechanism works in practice.
+The results of this experiment can be seen in Figure~\ref{fig:reward-error}, where grading error is plotted against relative magnitude of reward.
+This shows that a higher reward correlates to lower error.
+As the reward is administered based on the grader's performance on the Calibrated set, the correlation implies that the graders who perform well on the Calibrated set also perform well on the non-calibrated set.
+This verifies that the Calibration mechanism indeed works.
 
@@
 The Improved Calibration mechanism mitigates this issue by introducing multiple calibrated papers at the expense of more work, raising the objective score.
-However, since the work created by this mechanism does not scale well with class size, a better mechanism was developed: the Deduction mechanism.
+However, since the work created by this mechanism does not scale well with class size, the Deduction mechanism was developed.
 
@@
 \section{Conclusion}
-An efficient and accurate solution is needed to grade the large number of assignments in MOOCs.
 In this paper, a student model was first created - a set of assumptions that approximate the realistic behavior of students.
@@
 These mechanisms incentivize students to grade accurately and efficiently as proven by game theory.
-The Calibration mechanism was tested with a croudsourced experiment, showing that it could work in practice.
+The Calibration mechanism was tested with a crowd-sourced experiment, showing that it could work in practice.
 The student model can easily be reused and improved upon by future researchers who wish to develop more efficient solutions to more realistic scenarios.
@@
 \section{Future Work}
-As we consider how to generate accurate grades from incompetent graders, our model will require more realistic assumptions, which in turn may create more complex mechanisms.
-Eventually, we would like to see new mechanisms based off of our model or our existing mechanisms implemented in MOOCs such as EdX or Coursera.
+The further improvement and development of mechanisms may involve adding more realistic assumptions to the student model, which in turn may require more complex mechanisms.
+For example, a more complex mechanism may be required to generate accurate grades from incompetent graders.
+Of course, more testing and validation of mechanisms with crowd-sourced experiments is necessary.
+Eventually, new mechanisms based off the student model or existing mechanisms could be implemented in commercial MOOCs such as EdX or Coursera.
 
 \section{Acknowledgments}
-We would like to thank MIT and the MIT PRIMES program for providing the research opportunity as well as our parents and mentors for their support.
+We would like to thank MIT and the MIT PRIMES program for providing the research opportunity, as well as our parents for their support.
 Of course, none of this is possible without the original idea proposed by our advisor, Constantinos Daskalakis.
